### 2021-09-06 README.Rmd
first commit :rocket:

---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# conmat

<!-- badges: start -->
<!-- badges: end -->

The goal of conmat is to provide methods for producing contact matrices.

## Installation

You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("njtierney/conmat")
```

### 2021-09-06 R/add_rotated_ages.R

@@ -1,0 +1,26 @@
+# apply a 45 degree rotation to age contact pairs, to model trends along the
+# diagonal, and perpendicularly across the diagonal
+#' @title FUNCTION_TITLE
+#' @description FUNCTION_DESCRIPTION
+#' @param contact_data PARAM_DESCRIPTION
+#' @return OUTPUT_DESCRIPTION
+#' @details DETAILS
+#' @examples 
+#' \dontrun{
+#' if(interactive()){
+#'  #EXAMPLE1
+#'  }
+#' }
+#' @seealso 
+#'  \code{\link[dplyr]{mutate}}
+#' @rdname add_rotated_ages
+#' @export 
+#' @importFrom dplyr mutate
+add_rotated_ages <- function(contact_data) {
+  theta <- pi / 4
+  contact_data %>%
+    dplyr::mutate(
+      along_diagonal = age_from * cos(theta) + age_to * cos(theta),
+      across_diagonal = age_from * cos(theta) - age_to * sin(theta)
+    )
+}

### 2021-09-06 R/aggregate_predicted_contacts.R

@@ -1,0 +1,77 @@
+# aggregate predicted contacts from complete 1y resolution to a stated resolution
+# must pass in the population to do approppriate weighting of 'from' age groups
+#' @title FUNCTION_TITLE
+#' @description FUNCTION_DESCRIPTION
+#' @param predicted_contacts_1y PARAM_DESCRIPTION
+#' @param population PARAM_DESCRIPTION
+#' @param age_breaks PARAM_DESCRIPTION, Default: c(seq(0, 75, by = 5), Inf)
+#' @return OUTPUT_DESCRIPTION
+#' @details DETAILS
+#' @examples 
+#' \dontrun{
+#' if(interactive()){
+#'  #EXAMPLE1
+#'  }
+#' }
+#' @seealso 
+#'  \code{\link[dplyr]{mutate}},\code{\link[dplyr]{filter}},\code{\link[dplyr]{group_by}},\code{\link[dplyr]{summarise}}
+#'  \code{\link[stats]{weighted.mean}}
+#' @rdname aggregate_predicted_contacts
+#' @export 
+#' @importFrom dplyr mutate filter group_by summarise
+#' @importFrom stats weighted.mean
+aggregate_predicted_contacts <- function(
+  predicted_contacts_1y,
+  population,
+  age_breaks = c(
+    seq(0, 75, by = 5),
+    Inf
+  )
+) {
+  
+  # get function for 1y age populations in this country
+  age_population_function <- get_age_population_function(population)
+  
+  # aggregate contacts within age breaks
+  predicted_contacts_1y %>%
+    dplyr::mutate(
+      age_group_to = cut(
+        pmax(0.1, age_to),
+        age_breaks
+      )
+    ) %>%
+    dplyr::filter(
+      !is.na(age_group_to)
+    ) %>%
+    # sum the number of contacts to the 'to' age groups, for each integer
+    # participant age
+    dplyr::group_by(
+      age_from,
+      age_group_to
+    ) %>%
+    dplyr::summarise(
+      contacts = sum(contacts),
+      .groups = "drop"
+    ) %>%
+    # *average* the total contacts within the 'from' contacts, weighted by the
+    # population distribution (to get contacts for the population-average ember of
+    # that age group)
+    dplyr::mutate(
+      pop_age_from = age_population_function(age_from),
+      age_group_from = cut(
+        pmax(0.1, age_from),
+        age_breaks
+      )
+    ) %>%
[…]

### 2021-09-06 R/estimate_setting_contacts.R

@@ -1,0 +1,52 @@
+# given a named list of contact datasets (with names giving the setting, and
+# assumed to together make up the full set of contacts for individuals in the
+# survey), a representative population distribution for the survey, and a set of
+# age breaks at which to aggregate contacts, return a set of predicted contact
+# matrices for each setting, and for all combined.
+#' @title FUNCTION_TITLE
+#' @description FUNCTION_DESCRIPTION
+#' @param contact_data_list PARAM_DESCRIPTION
+#' @param survey_population PARAM_DESCRIPTION
+#' @param prediction_population PARAM_DESCRIPTION, Default: survey_population
+#' @param age_breaks PARAM_DESCRIPTION
+#' @return OUTPUT_DESCRIPTION
+#' @details DETAILS
+#' @examples 
+#' \dontrun{
+#' if(interactive()){
+#'  #EXAMPLE1
+#'  }
+#' }
+#' @rdname estimate_setting_contacts
+#' @export 
+estimate_setting_contacts <- function(
+  contact_data_list,
+  survey_population,
+  prediction_population = survey_population,
+  age_breaks
+) {
+  
+  setting_models <- lapply(
+    X = contact_data_list,
+    FUN = fit_single_contact_model,
+    population = survey_population
+  )
+  
+  setting_predictions <- lapply(
+    X = setting_models, 
+    FUN = predict_contacts,
+    population = prediction_population,
+    age_breaks = age_breaks
+  )
+  
+  setting_matrices <- lapply(
+    X = setting_predictions,
+    FUN = predictions_to_matrix
+  )
+  
+  combination <- Reduce("+", setting_matrices)
+  setting_matrices$all <- combination
+  
+  setting_matrices
+  
+}

### 2021-09-06 R/fit_single_contact_model.R

@@ -1,0 +1,48 @@
+# fit a single GAM contact model to a dataset
+#' @title FUNCTION_TITLE
+#' @description FUNCTION_DESCRIPTION
+#' @param contact_data PARAM_DESCRIPTION
+#' @param population PARAM_DESCRIPTION
+#' @return OUTPUT_DESCRIPTION
+#' @details DETAILS
+#' @examples 
+#' \dontrun{
+#' if(interactive()){
+#'  #EXAMPLE1
+#'  }
+#' }
+#' @seealso 
+#'  \code{\link[mgcv]{bam}}
+#'  \code{\link[stats]{offset}},\code{\link[stats]{c("Poisson", "family")}}
+#' @rdname fit_single_contact_model
+#' @export 
+#' @importFrom mgcv bam
+#' @importFrom stats offset poisson
+fit_single_contact_model <- function(contact_data, population) {
+  
+  # contact model for all locations together
+  contact_data %>%
+    add_modelling_features(
+      population = population
+    ) %>%
+    mgcv::bam(
+      contacts ~
+        # multiplicative offset for population in the 'to' age group, to account for
+        # opportunity to contact
+        stats::offset(log(pop_age_to)) +
+        # deviation of contact age distribution from population age distribution
+        s(age_to) +
+        # number of contacts by age
+        s(age_from) +
+        # intergenerational contact patterns
+        s(abs(age_from - age_to)) +
+        # probabilities of both attending (any) school/work
+        school_probability +
+        work_probability,
+      family = stats::poisson,
+      # add number of participants as a multilpicative offset here rather than in
+      # the formula, so it is not needed for prediction,
+      offset = log(participants),
+      data = .
+    )
+}

### 2021-09-06 R/get_age_population_function.R

@@ -1,0 +1,51 @@
+# return an interpolating function to get populations in 1y age increments from
+# chunkier distributions produced by socialmixr::wpp_age() (must contain `lower.age.limit` and `population`)
+#' @title FUNCTION_TITLE
+#' @description FUNCTION_DESCRIPTION
+#' @param population PARAM_DESCRIPTION
+#' @return OUTPUT_DESCRIPTION
+#' @details DETAILS
+#' @examples 
+#' \dontrun{
+#' if(interactive()){
+#'  #EXAMPLE1
+#'  }
+#' }
+#' @seealso 
+#'  \code{\link[dplyr]{arrange}}
+#'  \code{\link[stats]{splinefun}}
+#' @rdname get_age_population_function
+#' @export 
+#' @importFrom dplyr arrange
+#' @importFrom stats splinefun spline
+get_age_population_function <- function(population) {
+  
+  population <- population %>%
+    dplyr::arrange(lower.age.limit)
+  
+  # compute the widths of age bins
+  bin_widths <- diff(population$lower.age.limit)
+  final_bin_width <- bin_widths[length(bin_widths)]
+  bin_widths <- c(bin_widths, final_bin_width)
+  
+  # range of ages (assume the final bin width is that same as the previous one,
+  # since we cannot extrapolate the infinite upper bound without known the upper
+  # age limit)
+  min_age <- min(population$lower.age.limit)
+  max_age <- max(population$lower.age.limit) + final_bin_width
+  
+  # interpolator to 1y age groups up to 100
+  spline <- stats::splinefun(
+    x = population$lower.age.limit,
+    y = population$population / bin_widths, 
+  )
+  
+  # wrap this up in a function to handle values outside this range
+  function(age) {
+    population <- stats::spline(age)
+    invalid <- age < min(age) | age > max_age
+    population[invalid] <- 0
+    pmax(population, 0)
+  }
+  
+}

### 2021-09-06 R/get_polymod_contact_data.R

@@ -1,0 +1,120 @@
+# format polymod data and filter contacts to certain settings
+#' @title FUNCTION_TITLE
+#' @description FUNCTION_DESCRIPTION
+#' @param setting PARAM_DESCRIPTION, Default: c("all", "home", "work", "school", "other")
+#' @param ages PARAM_DESCRIPTION, Default: 0:100
+#' @param contact_age_imputation PARAM_DESCRIPTION, Default: c("sample", "mean", "remove_participant")
+#' @return OUTPUT_DESCRIPTION
+#' @details DETAILS
+#' @examples 
+#' \dontrun{
+#' if(interactive()){
+#'  #EXAMPLE1
+#'  }
+#' }
+#' @seealso 
+#'  \code{\link[dplyr]{mutate-joins}},\code{\link[dplyr]{mutate}},\code{\link[dplyr]{context}},\code{\link[dplyr]{case_when}},\code{\link[dplyr]{group_by}},\code{\link[dplyr]{filter}},\code{\link[dplyr]{select}},\code{\link[dplyr]{summarise}},\code{\link[dplyr]{n_distinct}}
+#'  \code{\link[stats]{Uniform}}
+#'  \code{\link[tidyr]{complete}},\code{\link[tidyr]{expand}}
+#' @rdname get_polymod_contact_data
+#' @export 
+#' @importFrom dplyr left_join mutate n case_when group_by ungroup filter select summarise n_distinct
+#' @importFrom stats runif
+#' @importFrom tidyr complete nesting
+get_polymod_contact_data <- function(
+  setting = c("all", "home", "work", "school", "other"),
+  ages = 0:100,
+  contact_age_imputation = c("sample", "mean", "remove_participant")
+) {
+  
+  setting <- match.arg(setting)
+  contact_age_imputation <- match.arg(contact_age_imputation)
+  
+  contact_data <- polymod$participants %>%
+    dplyr::left_join(
+      polymod$contacts,
+      by = "part_id"
+    )
+  
+  # impute contact ages according to the required method
+  contact_data_imputed <- contact_data %>%
+    dplyr::mutate(
+      cnt_age_sampled = floor(
+        # suppress warnings about NAs in runif
+        suppressWarnings(
+          stats::runif(
+            n = dplyr::n(),
+            min = cnt_age_est_min,
+            max = cnt_age_est_max + 1
+          )
+        )
+      ),
+      cnt_age_mean = floor(
[…]

### 2021-09-06 R/get_polymod_population.R

@@ -1,0 +1,53 @@
+# return the polymod-average population age distribution in 5y
+# increments (weight country population distributions by number of participants)
+# note that we don't want to weight by survey age distributions for this, since
+# the total number of *participants* represents the sampling
+#' @title FUNCTION_TITLE
+#' @description FUNCTION_DESCRIPTION
+
+#' @return OUTPUT_DESCRIPTION
+#' @details DETAILS
+#' @examples 
+#' \dontrun{
+#' if(interactive()){
+#'  #EXAMPLE1
+#'  }
+#' }
+#' @seealso 
+#'  \code{\link[dplyr]{filter}},\code{\link[dplyr]{group_by}},\code{\link[dplyr]{summarise}},\code{\link[dplyr]{context}},\code{\link[dplyr]{mutate-joins}}
+#'  \code{\link[socialmixr]{wpp_age}}
+#'  \code{\link[stats]{weighted.mean}}
+#' @rdname get_polymod_population
+#' @export 
+#' @importFrom dplyr filter group_by summarise n left_join
+#' @importFrom socialmixr wpp_age
+#' @importFrom stats weighted.mean
+get_polymod_population <- function() {
+  
+  polymod$participants %>%
+    dplyr::filter(
+      !is.na(year)
+    ) %>%
+    dplyr::group_by(
+      country,
+      year
+    ) %>%
+    dplyr::summarise(
+      participants = dplyr::n(),
+      .groups = "drop"
+    ) %>%
+    dplyr::left_join(
+      socialmixr::wpp_age(),
+      by = c("country", "year")
+    ) %>%
+    dplyr::filter(
+      !is.na(lower.age.limit)
+    ) %>%
+    dplyr::group_by(
+      lower.age.limit
+    ) %>%
+    dplyr::summarise(
+      population = stats::weighted.mean(population, participants)
+    )
+  
+}

### 2021-09-06 R/get_polymod_setting_data.R

@@ -1,0 +1,21 @@
+#' @title FUNCTION_TITLE
+#' @description FUNCTION_DESCRIPTION
+
+#' @return OUTPUT_DESCRIPTION
+#' @details DETAILS
+#' @examples 
+#' \dontrun{
+#' if(interactive()){
+#'  #EXAMPLE1
+#'  }
+#' }
+#' @rdname get_polymod_setting_data
+#' @export 
+get_polymod_setting_data <- function() {
+  list(
+    home = get_polymod_contact_data("home"),
+    work = get_polymod_contact_data("work"),
+    school = get_polymod_contact_data("school"),
+    other = get_polymod_contact_data("other")
+  )
+}

### 2021-09-06 R/matrix_to_predictions.R

@@ -1,0 +1,39 @@
+# convert a contact matrix as output by these functions (or socialmixr) into a
+# long-form tibble
+#' @title FUNCTION_TITLE
+#' @description FUNCTION_DESCRIPTION
+#' @param contact_matrix PARAM_DESCRIPTION
+#' @return OUTPUT_DESCRIPTION
+#' @details DETAILS
+#' @examples 
+#' \dontrun{
+#' if(interactive()){
+#'  #EXAMPLE1
+#'  }
+#' }
+#' @seealso 
+#'  \code{\link[tibble]{as_tibble}}
+#'  \code{\link[tidyr]{pivot_longer}}
+#'  \code{\link[dplyr]{mutate}},\code{\link[dplyr]{across}},\code{\link[dplyr]{reexports}}
+#' @rdname matrix_to_predictions
+#' @export 
+#' @importFrom tibble as_tibble
+#' @importFrom tidyr pivot_longer
+#' @importFrom dplyr mutate across starts_with
+matrix_to_predictions <- function(contact_matrix) {
+  contact_matrix %>%
+    tibble::as_tibble(
+      rownames = "age_group_from"
+    ) %>%
+    tidyr::pivot_longer(
+      cols = -c(age_group_from),
+      names_to = "age_group_to",
+      values_to = "contacts"
+    ) %>%
+    dplyr::mutate(
+      dplyr::across(
+        dplyr::starts_with("age_group"),
+        ~factor(.x, levels = unique(.x))
+      )
+    )
+}

### 2021-09-06 R/predict_contacts.R

@@ -1,0 +1,51 @@
+# predict number of contacts in all combinations of the age groups specified by
+# age_breaks, given a model and a population distribution of the time/place to
+# predict to
+#' @title FUNCTION_TITLE
+#' @description FUNCTION_DESCRIPTION
+#' @param model PARAM_DESCRIPTION
+#' @param population PARAM_DESCRIPTION
+#' @param age_breaks PARAM_DESCRIPTION, Default: c(seq(0, 75, by = 5), Inf)
+#' @return OUTPUT_DESCRIPTION
+#' @details DETAILS
+#' @examples 
+#' \dontrun{
+#' if(interactive()){
+#'  #EXAMPLE1
+#'  }
+#' }
+#' @seealso 
+#'  \code{\link[dplyr]{arrange}}
+#' @rdname predict_contacts
+#' @export 
+#' @importFrom dplyr arrange
+predict_contacts <- function (
+  model,
+  population,
+  age_breaks = c(seq(0, 75, by = 5), Inf)
+) {
+  
+  population <- population %>%
+    dplyr::arrange(lower.age.limit)
+  
+  age_min_integration <- min(population$lower.age.limit)
+  bin_widths <- diff(population$lower.age.limit)
+  final_bin_width <- bin_widths[length(bin_widths)]
+  age_max_integration <- max(population$lower.age.limit) + final_bin_width
+  
+  pred_1y <- predict_contacts_1y(
+    model = model,
+    population = population,
+    age_min = age_min_integration,
+    age_max = age_max_integration
+  )
+  
+  pred_groups <- aggregate_predicted_contacts(
+    predicted_contacts_1y = pred_1y,
+    population = population,
+    age_breaks = age_breaks
+  )
+  
+  pred_groups
+  
+}

### 2021-09-06 R/predict_contacts_1y.R

@@ -1,0 +1,57 @@
+# predict contacts to a given population at full 1y resolution 
+#' @title FUNCTION_TITLE
+#' @description FUNCTION_DESCRIPTION
+#' @param model PARAM_DESCRIPTION
+#' @param population PARAM_DESCRIPTION
+#' @param age_min PARAM_DESCRIPTION, Default: 0
+#' @param age_max PARAM_DESCRIPTION, Default: 100
+#' @return OUTPUT_DESCRIPTION
+#' @details DETAILS
+#' @examples 
+#' \dontrun{
+#' if(interactive()){
+#'  #EXAMPLE1
+#'  }
+#' }
+#' @seealso 
+#'  \code{\link[tidyr]{expand_grid}}
+#'  \code{\link[dplyr]{mutate}},\code{\link[dplyr]{select}}
+#' @rdname predict_contacts_1y
+#' @export 
+#' @importFrom tidyr expand_grid
+#' @importFrom dplyr mutate select
+predict_contacts_1y <- function(model, population, age_min = 0, age_max = 100) {
+  
+  all_ages <- age_min:age_max
+  
+  # predict contacts to all integer years, adjusting for the population in a given place
+  tidyr::expand_grid(
+    age_from = all_ages,
+    age_to = all_ages,
+  ) %>%
+    # add on prediction features, setting the population to predict to
+    add_modelling_features(
+      population = population
+    ) %>%
+    dplyr::mutate(
+      # prediction
+      contacts = predict(
+        model,
+        newdata = .,
+        type = "response"
+      ),
+      # uncertainty
+      se_contacts = predict(
+        model,
+        newdata = .,
+        type = "response",
+        se.fit = TRUE
+      )$se.fit
+    ) %>%
+    dplyr::select(
+      age_from,
+      age_to,
+      contacts,
+      se_contacts
+    ) 
+}

### 2021-09-06 R/predictions_to_matrix.R

@@ -1,0 +1,29 @@
+#' @title FUNCTION_TITLE
+#' @description FUNCTION_DESCRIPTION
+#' @param contact_predictions PARAM_DESCRIPTION
+#' @return OUTPUT_DESCRIPTION
+#' @details DETAILS
+#' @examples 
+#' \dontrun{
+#' if(interactive()){
+#'  #EXAMPLE1
+#'  }
+#' }
+#' @seealso 
+#'  \code{\link[tidyr]{pivot_wider}}
+#'  \code{\link[tibble]{rownames}}
+#' @rdname predictions_to_matrix
+#' @export 
+#' @importFrom tidyr pivot_wider
+#' @importFrom tibble column_to_rownames
+predictions_to_matrix <- function(contact_predictions) {
+  contact_predictions %>%
+    tidyr::pivot_wider(
+      names_from = age_group_to,
+      values_from = contacts
+    ) %>%
+    tibble::column_to_rownames(
+      "age_group_from"
+    ) %>%
+    as.matrix()
+}

### 2021-09-06 data-raw/clean-population-by-age-2020.R

@@ -1,0 +1,50 @@
+library(readxl)
+library(tidyverse)
+library(here)
+library(janitor)
+# data downloaded from https://www.abs.gov.au/statistics/people/population/regional-population-age-and-sex/2020/32350DS0003_2020.xls
+file_path <- here("data-raw/32350DS0003_2020.xls")
+names_1 <- file_path %>%
+  read_excel(
+    sheet = "Table 3",
+    skip = 8,
+    n_max = 1
+  ) %>%
+  names()
+names_2 <- file_path %>%
+  read_excel(
+    sheet = "Table 3",
+    skip = 7,
+    n_max = 1
+  ) %>%
+  names()
+
+names <- c(names_1[1:4], names_2[-(1:4)])
+
+abs_pop_age_lga_2020 <- file_path %>%
+  read_excel(
+    sheet = "Table 3",
+    skip = 10,
+    col_names = names
+  ) %>%
+  select(
+    -`S/T code`,
+    -`Total persons`
+  ) %>%
+  rename(
+    `85+` = `85 and over`,
+    state = `S/T name`,
+    LGA_NAME19 = `LGA name`,
+    LGA_CODE19 = `LGA code`
+  ) %>%
+  pivot_longer(
+    cols = -c(state, LGA_NAME19, LGA_CODE19),
+    names_to = "age",
+    values_to = "population"
+  ) %>%
+  # death to em-dashes
+  mutate(age = str_replace(age, "–", "-")) %>% 
+  clean_names() %>% 
+  mutate(year = 2020, .before = state)
+
+use_data(abs_pop_age_lga_2020)

### 2021-09-06 data-raw/read-household.R

@@ -1,0 +1,13 @@
+library(readr)
+household <- read_csv(here("data-raw/ABS_C16_T23_LGA_06092021160753604.csv"))
+
+View(household)
+
+household
+
+# multiply the number of households by the number people in a household
+# e.g., 6000 households of size 1 - there are 6000 people who live alone
+# do this for each group for one through to 7
+
+# for 8 or more - take Total population, and subtract the sum of the other
+# 1-7 groups (from LGA data)

### 2021-09-06 inst/clean-code.R

@@ -1,0 +1,83 @@
+sinew::pretty_namespace(
+  con = "gist.R",
+  force = list(
+    dplyr = c("arrange",
+              "group_by",
+              "filter",
+              "mutate",
+              "select",
+              "starts_with",
+              "across",
+              "bind_rows",
+              "case_when",
+              "group_by",
+              "left_join",
+              "n",
+              "n_distinct",
+              "summarise",
+              "ungroup"),
+    tibble = c("as_tibble",
+               "column_to_rownames"),
+    ggplot2 = c("ggplot", 
+                "aes",
+                "coord_fixed",
+                "element_blank",
+                "element_text",
+                "facet_wrap",
+                "geom_tile",
+                "ggsave",
+                "ggtitle",
+                "scale_fill_distiller",
+                "theme",
+                "theme_minimal"),
+    tidyr = c("complete", 
+              "nesting",
+              "expand_grid",
+              "pivot_longer",
+              "pivot_wider"),
+    stats = c("weighted.mean", 
+              "offset",
+              "runif",
+              "spline",
+              "splinefun"),
+    patchwork = c("plot_annotation",
+                 "plot_layout"),
+    socialmixr = c("contact_matrix",
+                   "wpp_age")
+  ),
+  ignore = list(
+    conmat = c("get_polymod_population",
+               "get_age_population_function",
+               "add_population_age_to",
+               "add_school_work_participation",
+               "add_rotated_ages",
+               "add_modelling_features",
+               "predict_contacts_1y",
+               "aggregate_predicted_contacts",
+               "matrix_to_predictions",
+               "estimate_setting_contacts",
+               "get_polymod_contact_data",
+               "plot_matrix",
+               "fit_single_contact_model",
+               "predict_contacts",
+               "predictions_to_matrix"),
+    brms = "s",
+    base = c("c", 
+             "length", 
+             "predict", 
+             "unique", 
+             "suppressWarnings")
+  ),
+  overwrite = TRUE
+)
+
+sinew::untangle(
+  file = "gist.R",
+  dir.out = "R/",
+  keep.body = TRUE
+)
+
+sinew::makeOxyFile(
+  input = "R/",
+  overwrite = TRUE
+)

### 2021-09-06 R/get_polymod_contact_data.R
add polymod data and update the spline issue and make vignette work

@@ -32,7 +32,7 @@ get_polymod_contact_data <- function(
   
   contact_data <- polymod$participants %>%
     dplyr::left_join(
-      polymod$contacts,
+      socialmixr::polymod$contacts,
       by = "part_id"
     )
   

### 2021-09-06 R/get_polymod_population.R

@@ -24,7 +24,7 @@
 #' @importFrom stats weighted.mean
 get_polymod_population <- function() {
   
-  polymod$participants %>%
+  socialmixr::polymod$participants %>%
     dplyr::filter(
       !is.na(year)
     ) %>%

### 2021-09-06 R/polymod-data.R

@@ -1,0 +1,6 @@
+#' Polymod data
+#' 
+#' Imported from `socialmixr`
+#' @name polymod
+#' @export
+"polymod"

### 2021-09-06 README.Rmd
use github actions and setup pkgdown

@@
 <!-- badges: start -->
+[![Codecov test coverage](https://codecov.io/gh/njtierney/conmat/branch/master/graph/badge.svg)](https://codecov.io/gh/njtierney/conmat?branch=master)
+[![R-CMD-check](https://github.com/njtierney/conmat/workflows/R-CMD-check/badge.svg)](https://github.com/njtierney/conmat/actions)
 <!-- badges: end -->

### 2021-09-06 R/conmat-package.R
add package metadata doc file and pipe, fix missing comma

@@ -1,0 +1,47 @@
+#' @keywords internal
+#' @importFrom stats predict
+"_PACKAGE"
+
+# The following block is used by usethis to automatically manage
+# roxygen namespace tags. Modify with care!
+## usethis namespace: start
+## usethis namespace: end
+NULL
+
+
+if (getRversion() >= "2.15.1") utils::globalVariables(c("."))
+globalVariables(
+  c(
+    "age_from",
+    "age_group_from",
+    "age_group_to",
+    "age_to",
+    "cnt_age",
+    "cnt_age_est_max",
+    "cnt_age_est_min",
+    "cnt_home",
+    "cnt_leisure",
+    "cnt_otherplace",
+    "cnt_school",
+    "cnt_transport",
+    "cnt_work",
+    "contacted",
+    "contacts",
+    "country",
+    "lower.age.limit",
+    "missing_any_contact_age",
+    "missing_any_contact_setting",
+    "part_age",
+    "part_id",
+    "participants",
+    "pop_age_from",
+    "population",
+    "predict",
+    "school_fraction_age_from",
+    "school_fraction_age_to",
+    "se_contacts",
+    "work_fraction_age_from",
+    "work_fraction_age_to",
+    "year"
+  )
+)

### 2021-09-06 README.Rmd
add some figures to the readme

@@
 ``` r
-# install.packages("devtools")
-devtools::install_github("njtierney/conmat")
+# install.packages("remotes")
+remotes::install_github("njtierney/conmat")
 ```
+
+## Example
+
+```{r}
+library(conmat)
+# build synthetic age-structured contact matrices with GAMs
+# analysis of polymod data
+
+# set age breaks
+age_breaks_5y <- c(seq(0, 75, by = 5), Inf)
+age_breaks_1y <- c(seq(0, 100, by = 1), Inf)
+
+# fit a single overall contact model to polymod
+m_all <- fit_single_contact_model(
+  contact_data = get_polymod_contact_data("all"),
+  population = get_polymod_population()
+)
+
+m_all
+```
+
+```{r}
+# predict contacts at 1y and 5y resolutions for inspection
+synthetic_all_5y <- predict_contacts(
+  model = m_all, 
+  population = get_polymod_population(),
+  age_breaks = age_breaks_5y
+) %>%
+  predictions_to_matrix()
+
+synthetic_all_5y
+```
+
+```{r}
+# predict contacts at 1y and 5y resolutions for inspection
+synthetic_all_5y <- predict_contacts(
+  model = m_all, 
+  population = get_polymod_population(),
+  age_breaks = age_breaks_5y
+) %>%
+  predictions_to_matrix()
+
+synthetic_all_5y
+
+library(ggplot2)
+plot_matrix(synthetic_all_5y) +
+  ggtitle("synthetic all at once")
+```

### 2021-09-07 README.Rmd
add code of conduct

@@
 
-```{r}
+```{r matrix-plot}
 # predict contacts at 1y and 5y resolutions for inspection
@@
 ```
+
+## Code of Conduct
+
+Please note that the conmat project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/0/CODE_OF_CONDUCT.html).
+By contributing to this project, you agree to abide by its terms.

### 2021-09-08 README.Rmd
add cleaned up education state data

@@
 
-```{r}
+```{r example}
 library(conmat)
@@
 
-```{r}
+```{r syn-all-5y}
 # predict contacts at 1y and 5y resolutions for inspection
@@
 ```{r matrix-plot}
+set.seed(2021-09-08)
 # predict contacts at 1y and 5y resolutions for inspection
@@
 
+## Data sources
+
+This package provides data for use in calculating contact matrices.
+
+These data are still being cleaned and processed, but their current forms are shown below:
+
+### abs_education_state
+
+```{r abs-education-state}
+abs_education_state
+```
+
+### abs_education_state_2020
+
+```{r abs-education-state-2020}
+abs_education_state_2020
+```
+
+### abs_employ_age_lga
+
+```{r abs-employ-age-lga}
+abs_employ_age_lga
+```
+
+### abs_household_lga
+
+```{r abs-household-lga}
+abs_household_lga
+```
+
+### abs_pop_age_lga_2016
+
+```{r abs-pop-age-lga-2016}
+abs_pop_age_lga_2016
+```
+
+### abs_pop_age_lga_2020
+
+```{r abs-pop-age-lga-2020}
+abs_pop_age_lga_2020
+```
+
+### abs_state_age
+
+```{r abs-state-age}
+abs_state_age
+```
+
 ## Code of Conduct

### 2021-09-08 data-raw/clean-education.R

@@ -78,6 +78,8 @@ abs_education_state <- abs_education_state_raw %>%
   arrange(age) %>%
   ungroup()
 
+use_data(abs_education_state, overwrite = TRUE)
+
 abs_education_state_2020 <- abs_education_state %>%
   filter(year == 2020) %>%
   mutate(state = toupper(state)) %>%
@@ -90,11 +92,6 @@ abs_education_state_2020 <- abs_education_state %>%
     age = 0:100,
     fill = list(value = 0)
   )
-
-abs_state_age %>%
-  pull(age_group) %>%
-  unique() %>%
-  parse_number()
 
 abs_state_age_lookup <- abs_state_age %>%
   mutate(
@@ -131,8 +128,6 @@ abs_education_state_2020_interp
 abs_education_state_2020_interp$population[[2]]
 
 abs_education_state_2020_interp
-
-use_data(abs_education_state_2020)
 
 abs_education_state_raw_table_notes <- read_excel(
   here("data-raw/Table 42b Number of Full-time and Part-time Students, 2006-2020.xlsx"),

### 2021-09-09 R/data_abs_employ_age_lga.R
update pkgdown, add NEWS, fix missing :: and remove period from DESCRIPTION title

@@ -11,7 +11,7 @@
 #'   \item{age_group}{age groups are as follows: 15-19, 20-24, 25-34, 35-44, 45-54, 55-64, 
 #'     65-74, 75-84, 85+, total}
 #'   \item{total_employed}{total  number of people employed}
-#'   \item{total_unemploted}{total number of people unemployed}
+#'   \item{total_unemployed}{total number of people unemployed}
 #'   \item{total_labour_force}{total number of people in the labour force}
 #'   \item{total}{sum of these totals...or thereabouts??}
 #' }

### 2021-09-09 R/unabbreviate_states.R

@@ -8,7 +8,7 @@
 #' @examples
 #' abbreviate_states("VIC")
 unabbreviate_states <- function(state_names) {
-  case_when(
+  dplyr::case_when(
     state_names %in% c("Australian Capital Territory", "ACT") ~ "Australian Capital Territory",
     state_names %in% c("New South Wales", "NSW") ~ "New South Wales",
     state_names %in% c("Northern Territory", "NT") ~ "Northern Territory",

### 2021-09-09 R/add_modelling_features.R
minor doco changes

@@ -9,6 +9,7 @@
 #'   # EXAMPLE1
 #' }
 #' }
+#' @note internal
 #' @export
 add_modelling_features <- function(contact_data, ...) {
   contact_data %>%

### 2021-09-09 README.Rmd
added example of conmat use to README for Sydney

@@
 
+```{r get-syd}
+library(conmat)
+sydney_age_pop <- abs_age_lga("Sydney (C)")
+sydney_age_pop
+```
+
+```{r sydney-synth-5, cache = TRUE}
+synthetic_settings_5y_sydney <- extrapolate_polymod(
+  population = sydney_age_pop,
+  age_breaks = c(seq(0, 85, by = 5), Inf)
+)
+synthetic_settings_5y_sydney
+```
+
+```{r sydney-synth-5-plot}
+# this code is erroring for the moment - something to do with rendering a large plot I think.
+# plot_setting_matrices(
+#   synthetic_settings_5y_sydney,
+#   title = "Setting-specific synthetic contact matrices (Sydney 2020 projected)"
+# )
+```
+
+```{r plot-matrix-differents}
+plot_matrix(synthetic_settings_5y_sydney$home)
+plot_matrix(synthetic_settings_5y_sydney$work)
+plot_matrix(synthetic_settings_5y_sydney$school)
+plot_matrix(synthetic_settings_5y_sydney$other)
+plot_matrix(synthetic_settings_5y_sydney$all)
+```
+
 ```{r example}
-library(conmat)
 # build synthetic age-structured contact matrices with GAMs

### 2021-09-23 README.Rmd
update README
fix duplicate title param

@@
 
-You can install the development version from [GitHub](https://github.com/) with:
+You can install the development version with:
+
+```r
+install.packages("conmat", repos = "https://njtierney.r-universe.dev")
+```
+
+Or alternatively you can use `remotes` (although I recommend using the above code)
 
@@
 
+We can extract out the ABS age population data using `abs_age_lga` like so:
+
 ```{r get-syd}
@@
 ```
+
+Note that you need to use the exact LGA name - you can look up LGA names in the data set `abs_lga_lookup`:
+
+```{r abs-lga-lookup}
+abs_lga_lookup
+```
+
+We can then extrapolate this data from polymod and plot a matrix, below:
 

### 2021-09-24 README.Rmd

@@
 
+## Speeding up computation with `future`
+
+`conmat` now supports parallelisation, which is useful in a couple of contexts with the model fitting, here is an example:
+
+```{r load-future}
+library(future)
+plan(multisession, workers = 4)
+```
+
+We set the future plan, saying multisession, with 4 workers.
+
+Then we run the code as normal:
+
+```{r show-off-furrr}
+polymod_setting_data <- get_polymod_setting_data()
+polymod_population <- get_polymod_population()
+
+contact_model <- fit_setting_contacts(
+  contact_data_list = polymod_setting_data,
+  survey_population = polymod_population
+)
+
+contact_model_pred <- predict_setting_contacts(
+  population = polymod_population,
+  contact_model = contact_model,
+  age_breaks = c(seq(0, 75, by = 5), Inf)
+)
+```
+
+Notably this is about 3 times faster than without using that plan.
+
 ## Data sources

### 2021-09-24 README.Rmd
update README instructions
update README with new workflow and figures

@@
 
-We can then extrapolate this data from polymod and plot a matrix, below:
+First we want to fit the model to the polymod data
 
-```{r sydney-synth-5, cache = TRUE}
-synthetic_settings_5y_sydney <- extrapolate_polymod(
+```{r fit-polymod}
+set.seed(2021-09-24)
+polymod_contact_data <- get_polymod_setting_data()
+polymod_survey_data <- get_polymod_population()
+
+setting_models <- fit_setting_contacts(
+  contact_data_list = polymod_contact_data,
+  population = polymod_survey_data
+  )
+```
+
+Then we take this model and extrapolate to the sydney data:
+
+```{r sydney-synth-5}
+set.seed(2021-09-24)
+synthetic_settings_5y_sydney <- predict_setting_contacts(
   population = sydney_age_pop,
+  contact_model = setting_models,
   age_breaks = c(seq(0, 85, by = 5), Inf)
   )
+
 synthetic_settings_5y_sydney
@@
 ```{r plot-matrix-differents}
+set.seed(2021-09-24)
 plot_matrix(synthetic_settings_5y_sydney$home)
@@
   contact_data_list = polymod_setting_data,
-  survey_population = polymod_population
+  population = polymod_population
 )

### 2021-09-29 README.Rmd
change out sydney for Fairfield in the README

@@
 library(conmat)
-sydney_age_pop <- abs_age_lga("Sydney (C)")
-sydney_age_pop
+fairfield_age_pop <- abs_age_lga("Fairfield (C)")
+fairfield_age_pop
 ```
@@
 
-Then we take this model and extrapolate to the sydney data:
+Then we take this model and extrapolate to the fairfield data:
 
-```{r sydney-synth-5}
+```{r fairfield-synth-5}
 set.seed(2021-09-24)
-synthetic_settings_5y_sydney <- predict_setting_contacts(
-  population = sydney_age_pop,
+synthetic_settings_5y_fairfield <- predict_setting_contacts(
+  population = fairfield_age_pop,
   contact_model = setting_models,
@@
   )
-
-synthetic_settings_5y_sydney
 ```
 
-```{r sydney-synth-5-plot}
+```{r fairfield-synth-5-plot}
 # this code is erroring for the moment - something to do with rendering a large plot I think.
-# plot_setting_matrices(
-#   synthetic_settings_5y_sydney,
-#   title = "Setting-specific synthetic contact matrices (Sydney 2020 projected)"
-# )
+plot_setting_matrices(
+  synthetic_settings_5y_fairfield,
+  title = "Setting-specific synthetic contact matrices (fairfield 2020 projected)"
+)
 ```
@@
 set.seed(2021-09-24)
-plot_matrix(synthetic_settings_5y_sydney$home)
-plot_matrix(synthetic_settings_5y_sydney$work)
-plot_matrix(synthetic_settings_5y_sydney$school)
-plot_matrix(synthetic_settings_5y_sydney$other)
-plot_matrix(synthetic_settings_5y_sydney$all)
+plot_matrix(synthetic_settings_5y_fairfield$home)
+plot_matrix(synthetic_settings_5y_fairfield$work)
+plot_matrix(synthetic_settings_5y_fairfield$school)
+plot_matrix(synthetic_settings_5y_fairfield$other)
+plot_matrix(synthetic_settings_5y_fairfield$all)
 ```

### 2021-10-04 README.Rmd
add CSV file of transmission probabilities and update README with data and plot example

@@
 
+### eyre_transmission_probabilities
+
+```{r eyre-transmission-probabilities}
+eyre_transmission_probabilities
+
+library(ggplot2)
+library(stringr)
+library(dplyr)
+eyre_transmission_probabilities %>%
+   group_by(
+     setting,
+     case_age_5y,
+     contact_age_5y
+   ) %>%
+   summarise(
+     across(
+       probability,
+       mean
+     ),
+     .groups = "drop"
+   ) %>%
+   rename(
+     case_age = case_age_5y,
+     contact_age = contact_age_5y
+   ) %>%
+   mutate(
+     across(
+       ends_with("age"),
+       ~ factor(.x,
+                levels = str_sort(
+                  unique(.x),
+                  numeric = TRUE
+                )
+       )
+     )
+   ) %>%
+   ggplot(
+     aes(
+       x = case_age,
+       y = contact_age,
+       fill = probability
+     )
+   ) +
+   facet_wrap(~setting) +
+   geom_tile() +
+   scale_fill_viridis_c() +
+   coord_fixed() +
+   theme_minimal() +
+   theme(
+     axis.text = element_text(angle = 45, hjust = 1)
+   )
+
+```
+
 ### abs_education_state

### 2021-12-15 README.Rmd
disclamer documentation on contact matrices structure

@@
 ```
+
+## Disclaimer
+
+The contact matrices created using the package are transposed compared to the contact matrices discussed by [Prem](https://journals.plos.org/ploscompbiol/article?id=10.1371/journal.pcbi.1005697#pcbi.1005697.ref023) and [Mossong](https://journals.plos.org/plosmedicine/article?id=10.1371/journal.pmed.0050074).
 

### 2021-12-15 README.Rmd
edits on disclaimer reference link

--- 2021-10-04 README.Rmd
@@
 ```
+
+## Disclaimer
+
+The contact matrices created using the package are in transposed format when compared to the contact matrices discussed by [Prem](https://journals.plos.org/ploscompbiol/article?id=10.1371/journal.pcbi.1005697) and [Mossong](https://journals.plos.org/plosmedicine/article?id=10.1371/journal.pmed.0050074).
 

### 2022-03-21 README.Rmd
Note on contact matrices structure

--- 2021-10-04 README.Rmd
@@
 ```
+
+## Note
+
+The contact matrices created using this package are transposed when compared to the contact matrices discussed by [Prem](https://journals.plos.org/ploscompbiol/article?id=10.1371/journal.pcbi.1005697) and [Mossong](https://journals.plos.org/plosmedicine/article?id=10.1371/journal.pmed.0050074).
+That is, the rows are "age group to", and the columns are "age group from".
 

### 2022-08-04 R/predict_contacts_1y.R
some more minor changes

@@ -13,6 +13,7 @@
 #' }
 #' @export
 predict_contacts_1y <- function(model, population, age_min = 0, age_max = 100) {
+  
   all_ages <- age_min:age_max
 
   # predict contacts to all integer years, adjusting for the population in a given place

### 2022-08-16 R/generate-ngm.R
merge conflict resolved

@@ -66,9 +66,11 @@ generate_ngm <- function(state_name = NULL,
   setting_rel_ngms$all <- Reduce("+", setting_rel_ngms)
   
   # scale to a required R_target
+  # the eigenvalue is the R
   R_raw <- Re(eigen(setting_rel_ngms$all)$values[1])
   scaling <- R_target / R_raw
   
+  # could be lapply
   setting_ngms <- mapply("*",
                          setting_rel_ngms,
                          scaling,

### 2022-08-24 R/unabbreviate_states.R
begin implementing the code documentation tidyup, refactoring some names and also moving internal functions into utils

@@ -3,10 +3,12 @@
 #' @param state_names vector of state names in short form
 #'
 #' @return Longer state names
-#' @export
+#' @seealso [abbreviate_states()]
 #'
 #' @examples
-#' abbreviate_states("VIC")
+#' unabbreviate_states("VIC")
+#' unabbreviate_states(c("VIC", "QLD"))
+#' @export
 unabbreviate_states <- function(state_names) {
   dplyr::case_when(
     state_names %in% c("Australian Capital Territory", "ACT") ~ "Australian Capital Territory",

### 2022-08-24 R/utils.R

@@ -1,0 +1,74 @@
+#' Prepare age population data
+#' 
+#' Internally used function within [age_population()] to separate age groups 
+#'   into its lower & upper limit and then filter the data passed to the desired 
+#'   year and location.
+#'
+#' @param data data.frame
+#' @param location_col bare unquoted variable referring to location column
+#' @param location location name to filter to. If not specified gives all locations.
+#' @param age_col bare unquoted variable referring to age column
+#' @param year_col bare unquoted variable referring to year column
+#' @param year year to filter to. If not specified, gives all years.
+#' 
+#' @keywords internal
+#'
+#' @return data frame with lower.age.limit and upper.age.limit and optionally
+#'   filtered down to specific location or year.
+clean_age_population_year <- function(data,
+                                           location_col = NULL,
+                                           location = NULL,
+                                           age_col,
+                                           year_col = NULL,
+                                           year = NULL) {
+  
+  # separate age group into "lower.age.limit" & "upper.age.limit" 
+  age_population_year_df <- separate_age_group(data, {{ age_col }})
+  
+  # filter year only
+  
+  if (!is.null(year)) {
+    age_population_year_df <- age_population_year_df %>%
+      dplyr::filter({{ year_col }} %in% {{ year }})
+  }
+  
+  # filter year & location
+  if (!is.null(location)) {
+    age_population_location_df <- age_population_year_df %>%
+      dplyr::filter({{ location_col }} %in% {{ location }})
+    
+    return(age_population_location_df)
+  } else {
+    return(age_population_year_df) 
+    # return the whole data frame or the df with only year filter 
+    # if year variable is present
+  }
+}
+
+#' Separate age groups
+#' 
+#' An internal function used within [clean_age_population_year()] to
+#'   separate age groups in a data set into two variables, `lower.age.limit`, 
+#'   and `upper.age.limit`
+#'
+#' @param data data frame
+#' @param age_col bare unquoted column referring to age column
+#' @keywords internal
+#' @return data frame with two extra columns, `lower.age.limit` and 
+#'   `upper.age.limit`
+separate_age_group <- function(data, age_col) {
+  result <- data %>%
+    tidyr::separate(
+      {{ age_col }},
+      c("lower.age.limit", "upper.age.limit"),
+      "[[:punct:]]",
+      extra = "merge"
+    ) %>%
+    dplyr::mutate(
[…]

### 2022-08-26 R/data_abs_state_age.R
documentation and code makeover

@@ -1,6 +1,7 @@
 #' ABS state population data for 2020
 #'
-#' A dataset containing Australian Bureau of Statistics state level population data for 2020
+#' Dataset containing Australian Bureau of Statistics state level population 
+#'   data for 2020
 #'
 #' @format A data frame with 168 rows and 3 variables:
 #' \describe{

### 2022-08-26 R/get_polymod_contact_data.R

@@ -13,11 +13,21 @@
 #' }
 #' }
 #' @export
-get_polymod_contact_data <- function(setting = c("all", "home", "work", "school", "other"),
-                                     countries = c("Belgium", "Finland", "Germany", "Italy", "Luxembourg", "Netherlands", 
-                                                 "Poland", "United Kingdom"),
-                                     ages = 0:100,
-                                     contact_age_imputation = c("sample", "mean", "remove_participant")) {
+get_polymod_contact_data <- function(
+  setting = c("all", "home", "work", "school", "other"),
+  countries = c(
+    "Belgium",
+    "Finland",
+    "Germany",
+    "Italy",
+    "Luxembourg",
+    "Netherlands",
+    "Poland",
+    "United Kingdom"
+  ),
+  ages = 0:100,
+  contact_age_imputation = c("sample", "mean", "remove_participant")
+) {
   setting <- match.arg(setting)
   contact_age_imputation <- match.arg(contact_age_imputation)
 

### 2022-08-30 R/get_polymod_contact_data.R
further documentation adjustments

@@ -1,17 +1,41 @@
-#' Format polymod data and filter contacts to certain settings
+#' @title Format POLYMOD data and filter contacts to certain settings
+#' 
+#' @description Provides contact and participant POLYMOD data from selected
+#'   countries. It impute missing contact ages via one of three methods: 
+#'   1) imputing contact ages from a random uniform distribution from the range
+#'   of ages. 2) using the average of the ages, 3) removal of those 
+#'   participants. The contact  settings are then classified as "home", 
+#'   "school", "work" and "others", where "others" include locations such as
+#'   leisure, transport or other places. The participants with missing contact 
+#'   ages or settings are removed, and the number of contacts per participant 
+#'   and contact age from ages 0-100 are obtained for various countries and
+#'   settings.
 #'
-#' @param setting Default: c("all", "home", "work", "school", "other")
-#' @param countries countries to extract data from
-#' @param ages Default: 0:100
-#' @param contact_age_imputation Default: c("sample", "mean", "remove_participant")
-#' @return OUTPUT_DESCRIPTION
-#' @details DETAILS
+#' @param setting Which setting to extract data from. Default is all settings.
+#'    Options are: "all", "home", "work", "school", and "other".
+#' @param countries countries to extract data from. Default is all countries 
+#'   from this list: "Belgium", "Finland", "Germany", "Italy", "Luxembourg",
+#'   "Netherlands", "Poland", and "United Kingdom".
+#' @param ages Which ages to return. Default is ages 0 to 100.
+#' @param contact_age_imputation How to handle age when it is missing. Choose 
+#'   one of three methods: 1) "sample", which imputes contact ages from a 
+#'   random uniform distribution from the range of ages. 2) "mean", use the
+#'   average of the ages, 3) "remove_participant" removal of those 
+#'   participants. Default is "sample".
+#' @return A data.frame with columns: "setting" (all, work, home, etc. as
+#'   specified in "setting" argument); "age_from" - the age of the participant; 
+#'   "age_to" - the age of the person the participant had contact with; 
+#'   "contacts" the number of contacts that person had; "participants" the
+#'   number of participants in that row.
 #' @examples
-#' \dontrun{
-#' if (interactive()) {
-#'   # EXAMPLE1
-#' }
-#' }
+#' get_polymod_contact_data()
+#' get_polymod_contact_data(setting = "home")
[…]

### 2022-08-30 R/fit_single_contact_model.R
document `fit_single_contact_model`

@@ -1,15 +1,81 @@
-#' fit a single GAM contact model to a dataset
-#'
-#' @param contact_data PARAM_DESCRIPTION
-#' @param population PARAM_DESCRIPTION
-#' @return OUTPUT_DESCRIPTION
-#' @details DETAILS
+#' @title Fit a single GAM contact model to a dataset
+#' 
+#' @description This is the workhorse of the `conmat` package, and is typically
+#'   used inside [fit_setting_contacts()]. It predicts the contact rate between 
+#'   all age bands (the contact rate between ages 0 and 1, 0 and 2, 0 and 3, 
+#'   and so on), for a specified setting, with specific terms being added for 
+#'   given settings. See "details" for further information.
+#'   
+#' @details The model fit is a Generalised Additive Model (GAM). To help 
+#'   account for assortativity with age, where people of similar ages have 
+#'   more contact with each other, we include predictors `age_from`, and 
+#'   `age_to`. To account for intergenerational contact patterns, where 
+#'   parents and grandparents will interact with their children and grand 
+#'   children, we include a term that is the absolute difference of age_from 
+#'   and age_to. We also include the interaction of intergenerational contact 
+#'   patterns with contacts from one age with the term that is the absolute 
+#'   difference of age_from and age_to, and age_from. These terms are fit with 
+#'   a smoothing function. Specifically, the relevant code looks like this:
+#'   
+#'   ``` r
+#'   s(age_to) + 
+#'     s(age_from) + 
+#'     s(abs(age_from - age_to)) + 
+#'     s(abs(age_from - age_to), age_from)
+#'   ```
+#'   
+#'   We also include predictors for the probability of attending school, and 
+#'   attending work. These are computed as the probability that a person goes 
+#'   to the same school/work, proportional to the increase in contacts due to
+#'   attendance. These terms are calculated from estimated proportion of 
+#'   people in age groups attending school and work. See 
+#'   [add_modelling_features()] for more details.
+#'   
+#'   Finally, we include two offset terms so that we estimate the contact rate, 
+#'   that is the contacts per capita, instead of the number of contacts. These
+#'   offset terms are `log(contactable_population)`, and 
+#'   `log(contactable_population_school)` when the model is fit to a school 
+#'   setting. The contactable population is estimated as the interpolated 
[…]

### 2022-08-31 R/aggregate_predicted_contacts.R
update prediction documentation

@@ -1,18 +1,42 @@
-#' aggregate predicted contacts from complete 1y resolution
-#'
-#' aggregate predicted contacts from complete 1y resolution to a stated
-#' resolution must pass in the population to do appropriate weighting of
-#' 'from' age groups
-#' @param predicted_contacts_1y contacts in 1 year breaks
-#' @param population population
-#' @param age_breaks Default: c(seq(0, 75, by = 5), Inf)
-#' @return data frame
+#' @title Aggregate predicted contacts to specified age breaks
+#' 
+#' @description Aggregates contacts rate from, say, a 1 year level into 
+#'   provided age  breaks, weighting the contact rate by the specified age
+#'   population. For example, if you specify breaks as c(0, 5, 10, 15, Inf), 
+#'   it will return age groups as 0-5, 5-10, 10-15, and 15+ (Inf). Used 
+#'   internally within [predict_contacts()], although can be used by users.
+#'   
+#' @param predicted_contacts_1y contacts in 1 year breaks (could technically 
+#'   by in other year breaks). Data must contain columns, `age_from`, `age_to`,
+#'   `contacts`, and `se_contacts`, which is the same output as 
+#'   [predict_contacts_1y()] - see examples below.
+#' @param population population with columns `lower.age.limit`, and 
+#'   `population`. See examples below.
+#' @param age_breaks vector of ages. Default: c(seq(0, 75, by = 5), Inf)
+#' @return data frame with columns, `age_group_from`, `age_group_to`, and
+#'  `contacts`, which is the aggregated model.
 #' @examples
-#' \dontrun{
-#' if (interactive()) {
-#'   # EXAMPLE1
-#' }
-#' }
+#'  fairfield_abs_data <- abs_age_lga("Fairfield (C)")
+#'  
+#'  fairfield_abs_data
+#'  
+#'  # We can predict the contact rate for Fairfield from the existing contact 
+#'  # data, say, between the age groups of 0-15 in 5 year bins for school:
+#'    
+#' fairfield_contacts_1 <- predict_contacts_1y(
+#'   model = polymod_setting_models$home,
+#'   population = fairfield_abs_data,
+#'   age_min = 0,
+#'   age_max = 15
+#' )
+#'  
+#'  fairfield_contacts_1
+#'  
+#' aggregated_fairfield <- aggregate_predicted_contacts(
+#'   predicted_contacts_1y = fairfield_contacts_1,
+#'   population = fairfield_abs_data,
[…]

### 2022-08-31 R/predict_contacts_1y.R

@@ -1,16 +1,46 @@
-#' predict contacts to a given population at full 1y resolution
+#' @title Predict contact rate to a given population at full 1y resolution
 #'
-#' @param model PARAM_DESCRIPTION
-#' @param population PARAM_DESCRIPTION
-#' @param age_min PARAM_DESCRIPTION, Default: 0
-#' @param age_max PARAM_DESCRIPTION, Default: 100
-#' @return OUTPUT_DESCRIPTION
+#' @description Provides a predicted rate of contacts for contact ages.
+#'   Take an already fitted model of contact rate and predict the
+#'   estimated contact rate, and standard error, for all combinations of the 
+#'   provided ages in 1 year increments. So if the minimum age is 5, and the 
+#'   maximum age is 10, it will provide the estimated contact rate for all age 
+#'   combinations: 5 and 5, 5 and 6 ... 5 and 10, and so on. This function is 
+#'   used internally within [predict_contacts()], and thus 
+#'   [predict_setting_contacts()] as well, although it can be used by itself.
+#'   See examples for more details, and details for more information.
+#'  
+#' @details Prediction features are added using [add_modelling_features()]. 
+#'   These features include the population distribution of contact ages, 
+#'   fraction of population in each age group that attend school/work as well 
+#'   as the offset according to the settings on all combinations of the
+#'   participant & contact ages.
+#'   
+#' @param model A single fitted model of contact rate (e.g.,
+#'    [fit_single_contact_model()]) 
+#' @param population a dataframe of age population information, with columns 
+#'    indicating some lower age limit, and population, (e.g., 
+#'    [get_polymod_population()])
+#' @param age_min Age range minimum value. Default: 0
+#' @param age_max Age range maximum value, Default: 100
+#' @return Data frame with four columns: `age_from`, `age_to`, `contacts`, and
+#'   `se_contacts`. This contains the participant & contact ages from the 
+#'   minimum and maximum ages provided along with the predicted rate of 
+#'   contacts and standard error around the prediction.
 #' @examples
-#' \dontrun{
-#' if (interactive()) {
-#'   # EXAMPLE1
-#' }
-#' }
+#' 
+#' fairfield_abs_data <- abs_age_lga("Fairfield (C)")
+#' 
+#' fairfield_abs_data
+#' 
+#' # predict the contact rates in 1 year blocks to Fairfield data
+#' 
[…]

### 2022-09-01 README.Rmd
tidy up README and split out some parts into vignettes

@@
 
-The goal of conmat is to provide methods for producing contact matrices.
+The goal of conmat is to make it easy to generate synthetic contact matrices for a given age population.
+
+**What is a contact matrix?**
+
+Contact matrices describe the degree of contact between individuals of given age groups.
+These matrices are commonly used to model how diseases such as COVID-19 spread in a population through social contact.
+
+**Why do we need _synthetic_ contact matrices?**
+
+Contact matrices are produced from empirical data resulting from a contact survey, which requires individuals to diary the amount and manner of contact a person has in a day.
+
+However, these surveys are highly time-consuming and expensive to run, meaning that only a handful of these empirical datasets exist globally.
+
+We can use statistical methods to create _synthetic contact matrices_, which are new contact matrices that have been generalised to new countries based on existing surveys.
+
+**Why do we need `conmat`?**
+
+Existing methods only provide outputs of the contact matrices for each country, or at best, for urban and rural areas for a given country.
+
+We need methods that allow for flexibly creating synthetic contact matrices for a specified age population, as the age population distribution of many countries (e.g., Australia), are quite heterogeneous, and assuming it is homogeneous would result in inaccurate representation of community infection in many regions.
 
@@
 
-Or alternatively you can use `remotes` (although I recommend using the above code)
+Or alternatively you can use `remotes`
 
@@
 
-## Note
-
-The contact matrices created using this package are transposed when compared to the contact matrices discussed by [Prem](https://journals.plos.org/ploscompbiol/article?id=10.1371/journal.pcbi.1005697) and [Mossong](https://journals.plos.org/plosmedicine/article?id=10.1371/journal.pmed.0050074).
-That is, the rows are "age group to", and the columns are "age group from".
-
 ## Example
 
-We can extract out the ABS age population data using `abs_age_lga` like so:
+First we want to fit the model to the POLYMOD data, which contains various survey and population data.
 
-```{r get-syd}
+```{r get-polymod}
 library(conmat)
-fairfield_age_pop <- abs_age_lga("Fairfield (C)")
-fairfield_age_pop
+polymod_contact_data <- get_polymod_setting_data()
+polymod_survey_data <- get_polymod_population()
 ```
 
-Note that you need to use the exact LGA name - you can look up LGA names in the data set `abs_lga_lookup`:
+The contact data is a list of the contacts for each of the settings, "home", "work", "school", and "other". It contains a dataframe for each of these.
 
-```{r abs-lga-lookup}
-abs_lga_lookup
+```{r show-polymod-str}
+str(polymod_contact_data)
 ```
 
-First we want to fit the model to the polymod data
+Say looking at the "home" setting, each row contains survey information of the number of contacts.
+Specifically, the number of contacts from one age group to another age group, and then the nuber of participants in that age group.
+
+```{r show-polymod-home}
+polymod_contact_data$home
+```
+
+The survey data contains the lower age limit and the population in that age group.
+
+```{r show-polymod}
+polymod_survey_data
+```
+
+We can create a model for each of the settings with the function `fit_setting_contacts`
 
@@
 set.seed(2021-09-24)
-polymod_contact_data <- get_polymod_setting_data()
-polymod_survey_data <- get_polymod_population()
-
 setting_models <- fit_setting_contacts(
@@
 
-Then we take this model and extrapolate to the fairfield data:
+This contains a list of models, one for each setting. We can look at one, and get summary information out:
+
+```{r}
+names(setting_models)
+setting_models$home
+```
+
+So this gives us our baseline model of a contact model. We have fit this model to the existing contact survey data.
+
+We can now predict to another age population, to create our "synthetic" contact matrix. Say we want to create a contact matrix for the "Fairfield" LGA, we can extract it out like so:
+
+```{r get-fairfield}
+library(conmat)
+fairfield_age_pop <- abs_age_lga("Fairfield (C)")
+fairfield_age_pop
+```
+
+Then we take the model we had earlier, and extrapolate to the fairfield data with `predict_setting_contacts`, also providing some age breaks we want to predict to
 
@@
 
+This then returns a list of synthetic matrices, "home", "work", "school", "other", and "all", which is the sum of all matrices.
+
+```{r}
+str(synthetic_settings_5y_fairfield)
+synthetic_settings_5y_fairfield$home
+synthetic_settings_5y_fairfield$all
+```
+
+## Plotting
+
+Looking at the matrices is nice, but let's plot them. We can use `plot_setting_matrix` to plot all at once
+
 ```{r fairfield-synth-5-plot}
@@
 
+You can also plot individual matrices with `plot_matrix`
+
 ```{r plot-matrix-differents}
-set.seed(2021-09-24)
 plot_matrix(synthetic_settings_5y_fairfield$home)
-plot_matrix(synthetic_settings_5y_fairfield$work)
-plot_matrix(synthetic_settings_5y_fairfield$school)
-plot_matrix(synthetic_settings_5y_fairfield$other)
 plot_matrix(synthetic_settings_5y_fairfield$all)
@@
 
-```{r example}
-# build synthetic age-structured contact matrices with GAMs
-# analysis of polymod data
+## Note
 
-# set age breaks
-age_breaks_5y <- c(seq(0, 75, by = 5), Inf)
-age_breaks_1y <- c(seq(0, 100, by = 1), Inf)
-
-# fit a single overall contact model to polymod
-m_all <- fit_single_contact_model(
-  contact_data = get_polymod_contact_data("all"),
-  population = get_polymod_population()
-)
-
-m_all
-```
-
-```{r syn-all-5y}
-# predict contacts at 1y and 5y resolutions for inspection
-synthetic_all_5y <- predict_contacts(
-  model = m_all, 
-  population = get_polymod_population(),
-  age_breaks = age_breaks_5y
-) %>%
-  predictions_to_matrix()
-
-synthetic_all_5y
-```
-
-```{r matrix-plot}
-set.seed(2021-09-08)
-# predict contacts at 1y and 5y resolutions for inspection
-synthetic_all_5y <- predict_contacts(
-  model = m_all, 
-  population = get_polymod_population(),
-  age_breaks = age_breaks_5y
-) %>%
-  predictions_to_matrix()
-
-synthetic_all_5y
-
-library(ggplot2)
-plot_matrix(synthetic_all_5y) +
-  ggtitle("synthetic all at once")
-```
+The contact matrices created using this package are transposed when compared to the contact matrices discussed by [Prem](https://journals.plos.org/ploscompbiol/article?id=10.1371/journal.pcbi.1005697) and [Mossong](https://journals.plos.org/plosmedicine/article?id=10.1371/journal.pmed.0050074).
+That is, the rows are "age group to", and the columns are "age group from".
 
@@
 
-`conmat` now supports parallelisation, which is useful in a couple of contexts with the model fitting, here is an example:
+`conmat` supports parallelisation, which is useful in a couple of contexts with the model fitting, here is an example:
 
@@
 
-We set the future plan, saying multisession, with 4 workers.
-
-Then we run the code as normal:
+We set the future plan, saying "multisession", with 4 workers.
+Then we run the same code as above (note that you must specify the plan, otherwise it does not know how to parallelise.
+See the [future package documentation](https://future.futureverse.org/reference/plan.html) for more details):
 
@@
 
-This package provides data for use in calculating contact matrices.
+This package provides data and helper functions for the data, for use in calculating contact matrices.
+The data sources are from the Australian Bureau of Statistics (ABS), as we were using these a lot when we created the package.
+In the future we might wrap these data sources and helpers into another package, but for the time being they are here.
 
-These data are still being cleaned and processed, but their current forms are shown below:
+Below are a couple of examples of data provided, see the "data sources" vignette and helpful at the website for full details.
 
-### eyre_transmission_probabilities
+You can extract the age population structure for the LGA Fairfield, or Brisbane, like so:
 
-```{r eyre-transmission-probabilities}
-eyre_transmission_probabilities
-
-library(ggplot2)
-library(stringr)
-library(dplyr)
-eyre_transmission_probabilities %>%
-   group_by(
-     setting,
-     case_age_5y,
-     contact_age_5y
-   ) %>%
-   summarise(
-     across(
-       probability,
-       mean
-     ),
-     .groups = "drop"
-   ) %>%
-   rename(
-     case_age = case_age_5y,
-     contact_age = contact_age_5y
-   ) %>%
-   mutate(
-     across(
-       ends_with("age"),
-       ~ factor(.x,
-                levels = str_sort(
-                  unique(.x),
-                  numeric = TRUE
-                )
-       )
-     )
-   ) %>%
-   ggplot(
-     aes(
-       x = case_age,
-       y = contact_age,
-       fill = probability
-     )
-   ) +
-   facet_wrap(~setting) +
-   geom_tile() +
-   scale_fill_viridis_c() +
-   coord_fixed() +
-   theme_minimal() +
-   theme(
-     axis.text = element_text(angle = 45, hjust = 1)
-   )
-
+```{r abs-age-lga}
+abs_age_lga("Fairfield (C)")
+abs_age_lga("Brisbane (C)")
 ```
 
-### abs_education_state
+Note that you need to use the exact LGA name - you can look up LGA names in the data set `abs_lga_lookup`:
 
-```{r abs-education-state}
-abs_education_state
+```{r abs-lga-lookup}
+abs_lga_lookup
 ```
 
-### abs_education_state_2020
+Or get the information for states like so:
 
-```{r abs-education-state-2020}
-abs_education_state_2020
-```
-
-### abs_employ_age_lga
-
-```{r abs-employ-age-lga}
-abs_employ_age_lga
-```
-
-### abs_household_lga
-
-```{r abs-household-lga}
-abs_household_lga
-```
-
-### abs_pop_age_lga_2016
-
-```{r abs-pop-age-lga-2016}
-abs_pop_age_lga_2016
-```
-
-### abs_pop_age_lga_2020
-
-```{r abs-pop-age-lga-2020}
-abs_pop_age_lga_2020
-```
-
-### abs_state_age
-
-```{r abs-state-age}
-abs_state_age
+```{r abs-age-state}
+abs_age_state(state_name = "QLD")
+abs_age_state(state_name = "NSW")
 ```

### 2022-09-05 R/apply_vaccination.R
finish first round of polish on documentation for conmat!

@@ -1,52 +1,89 @@
-#' Apply vaccination effects to next generation contact matrices
-#' 
-#' @description Applies vaccination effects to next generation matrices that leads to reduction of acquisition and transmission in each age group
-#' @param ngm next generation matrices. See [generate_ngm()] for creating next generation matrices of a state or a local government area for specific age groups
-#' @param data data frame with location specific information on vaccine coverage, efficacy of acquisition/susceptibility and efficacy of transmission/infectiousness for the ordered age groups from lowest to highest of the next generation matrix 
-#' @param coverage_col bare variable name for the column with information on vaccine coverage by age groups
-#' @param acquisition_col bare variable name for the column with information on efficacy of acquisition
-#' @param transmission_col bare variable name for the column with information on efficacy of transmission
-#' @return list of contact matrices with reduction in transmission matching the next generation matrices
-#' @export
+#' @title Apply vaccination effects to next generation contact matrices
+#'
+#' @description Applies the effect of vaccination on the next generation of
+#'   infections, to understand and describe the reduction of acquisition and
+#'   transmission in each age group.
+#'
+#' @details Vaccination improves a person's immunity from a disease. When a
+#'   sizable section of the population receives vaccinations or when vaccine
+#'   coverage is sufficient enough, the likelihood that the unvaccinated
+#'   population will contract the disease is decreased. This helps to slow
+#'   infectious disease spread as well as lessen its severity. For this reason,
+#'   it is important to understand how much of a reduction in probability of
+#'   acquisition (the likelihood that an individual will contract the disease),
+#'   and probability of transmission (the likelihood that an individual will
+#'   spread the disease after contracting it), has occurred as an the effect of
+#'   vaccination, in other words the effect of vaccination on the next
+#'   generation of infections.
+#'
+#'   `apply_vaccination` returns the percentage reduction in acquisition and
+#'   transmission in each age group. It does this by taking the outer product
+#'   of these reductions in acquisition and transmission by age group, creating
+#'   a transmission reduction matrix. The next generation matrices with the
+#'   vaccination effects applied are then produced using the obtained
[…]

### 2022-09-05 R/data-davies-age-extended.R

@@ -1,16 +1,17 @@
 #' Susceptibility and clinical fraction parameters from Davies et al.
 #'
-#'
-#' A dataset containing data from ...(insert url here),
-#' When using this data, ensure that you cite the original authors at 
+#' A dataset containing data from  \url{https://www.nature.com/articles/s41591-020-0962-9#code-availability}
+#' When using this data, ensure that you cite the original authors at:
 #' 
-#' ""
+#' "Davies, N.G., Klepac, P., Liu, Y. et al. Age-dependent effects in the transmission and control of COVID-19 epidemics. Nat Med 26, 1205–1211 (2020). https://doi.org/10.1038/s41591-020-0962-9"
 #'
-#' @format A data frame of the probability of transmission from a case to a contact. There are 40,804 rows and 6 variables.
+#' @format A data frame of the probability of transmission from a case to a contact. There are 101 rows and 4 variables.
 #' \describe{
 #'   \item{age}{from 0 to 100}
-#'   \item{clinical_fraction}{fraction with clinical symptoms?}
-#'   \item{davies_original}{davies original estimates?}
-#'   \item{davies_updated}{davies updated estimates?}
+#'   \item{clinical_fraction}{Estimate of fraction with clinical symptoms, or the age-specific proportion of infections resulting in clinical sympttoms inferred by applying a smoothing spline to the mean estimates from Davies et al. }
+#'   \item{davies_original}{Age specific parameters of the relative susceptibility to 
+#'     infection inferred from a smoothing-spline estimate of the mean relative susceptibility estimate from Davies et al.}
+#'   \item{davies_updated}{Re-estimated parameter of the susceptibility profile for under-16s that is estimated in a similar way but to the age-distribution of infections in England from the UK ONS prevalence survey rather than case counts which may undercount children}
 #' }
 "davies_age_extended"
+  

### 2022-09-05 R/generate-ngm.R

@@ -1,8 +1,31 @@
-#' Get next generation contact matrices
-#' @param state_name target Australian state name in abbreviated form, such as "QLD", "NSW", or "TAS"
-#' @param lga_name target Australian local government area (LGA) name, such as "Fairfield (C)".  See 
-#'   [abs_lga_lookup()] for list of lga names
-#' @param age_breaks vector depicting age values with the highest age depicted as `Inf`. For example, c(seq(0, 85, by = 5), Inf)
+#' @title Calculate next generation contact matrices
+#' 
+#' @description Once infected, a person can transmit an infectious disease to 
+#'   another, creating generations of infected individuals. We can define a 
+#'   matrix describing the number of newly infected individuals in given 
+#'   categories, such as age, for consecutive generations. This matrix is 
+#'   called a "next generation matrix" (NGM). 
+#'   
+#' @details The NGM can be used to calculate the expected number of secondary 
+#'   infections in a given age group. Given certain age breaks, we compute the 
+#'   unscaled next generation matrices for that location across different 
+#'   settings & age groups using the contact rates extrapolated from POLYMOD 
+#'   survey data on the specified location, adjusted by the per capita 
+#'   household size and the setting-specific relative per-contact transmission 
+#'   probability matrices for the same age groups. These NGMs are then scaled 
+#'   according to a target reproduction number (which is provided as an 
+#'   argument) using the ratio of the desired R0 and the R0 of the NGM 
+#'   for the combination of all settings. The R0 of the combination of all 
+#'   settings is obtained by calculating the unique, positive eigen value of 
+#'   the combination NGM. This ratio is then used to scale all the setting 
+#'   specific NGMs. 
+#' 
+#' @param state_name target Australian state name in abbreviated form, such 
+#'   as "QLD", "NSW", or "TAS"
+#' @param lga_name target Australian local government area (LGA) name, such 
+#'   as "Fairfield (C)".  See [abs_lga_lookup()] for list of lga names.
+#' @param age_breaks vector depicting age values with the highest age depicted 
+#'   as `Inf`. For example, c(seq(0, 85, by = 5), Inf)
 #' @param R_target target reproduction number
 #'
 #' @export
@@ -20,7 +43,6 @@
 #'   R_target = 1.5
 #' )
 #' }
-
 generate_ngm <- function(state_name = NULL,
                          lga_name = NULL,
                          age_breaks,

### 2022-09-05 R/get_setting_transmission_matrices.R

@@ -32,13 +32,17 @@
 #' transmission and control of COVID-19 epidemics. Nat Med 26, 1205–1211 (2020).
 #' https://doi.org/10.1038/s41591-020-0962-9
 #'
-#' @param age_breaks vector of age breaks, defaults to `c(seq(0, 80, by = 5),
-#'   Inf)`
+#' @param age_breaks vector of age breaks, defaults to 
+#'   `c(seq(0, 80, by = 5), Inf)`
 #' @param asymptomatic_relative_infectiousness the assumed ratio of onward
-#'   infectiousness between asymptomatic and symptomatic cases
-#' @param susceptibility_estimate which estimate to use for susceptibiloty by
-#'   age - the smoothed original Davies et al estimates, or the set updated to match UK
-#'   under-16 infections (the default)
+#'   infectiousness between asymptomatic and symptomatic cases. This represents 
+#'   the infectiousness of asymptomatic relative to symptomatic. 
+#'   Default value is 0.5, which means the asymptomatic cases are 50% less 
+#'   infectious than symptomatic cases.
+#' @param susceptibility_estimate Which estimate to use for susceptibility by
+#'   age. Either, the smoothed original Davies et al estimates, 
+#'   "davies_original" or, the set updated to match UK under-16 infections
+#'    (the default), "davies_updated".
 #'
 #' @return list of matrices, containing the relative per-contact transmission
 #'   probability for each setting

### 2022-09-05 R/plot_matrix.R

@@ -1,12 +1,52 @@
-#' Use ggplot to plot a matrix in the output format
-#' @param matrix matrix
-#' @return a ggplot object
+#' Visualise predicted contact matrix
+#' 
+#' Visualising the predicted contact rates facilitates understanding the 
+#'   underlying patterns and relationships between age groups in different 
+#'   settings (workplace, home, school, other). The `plot_matrix()` function
+#'   takes a contact matrix and visualises it, with the x and y axes being 
+#'   different age groups.
+#' 
+#' @param matrix Square matrix with row and column names indicating the age
+#'   groups
+#' @return a ggplot visualisation of contact rates
 #' @examples
 #' \dontrun{
-#' if (interactive()) {
-#'   # EXAMPLE1
+#' 
+#' set.seed(2021-09-24)
+#' polymod_contact_data <- get_polymod_setting_data()
+#' polymod_survey_data <- get_polymod_population()
+#' 
+#' setting_models <- fit_setting_contacts(
+#'   contact_data_list = polymod_contact_data,
+#'   population = polymod_survey_data
+#' )
+#' 
+#' fairfield_age_pop <- abs_age_lga("Fairfield (C)")
+#' 
+#' fairfield_age_pop
+#' 
+#' synthetic_settings_5y_fairfield <- predict_setting_contacts(
+#'   population = fairfield_age_pop,
+#'   contact_model = setting_models,
+#'   age_breaks = c(seq(0, 85, by = 5), Inf)
+#' )
+#' 
+#' # Visualise the projected contact rates for "home" in the Fairfield LGA. The 
+#' # strong diagonal shows us that similar age groups typically have higher 
+#' # rates of home contact. We can also see parental links include middle-aged 
+#' # age groups having observable contact rates with younger age groups. 
+#' # For instance, ages between 25 and 45 have higher contact rates with 
+#' # newborns (0 to 5) and children (5 to 10), but older age groups, 
+#' # including those over 55, tend to have higher contact rates with age 
+#' # groups between 25 and 45, showing the interactions between parents and 
+#' # children. In addition to this, other patterns that indicates contact 
+#' # between children and their grandparents where higher contact rates between 
+#' # young children (years 0-5) and grandparents (age 55+) are present. 
+#' 
+#' 
+#' plot_matrix(synthetic_settings_5y_fairfield$home)
 #' }
-#' }
+#' 
 #' @export
 plot_matrix <- function(matrix) {
   matrix %>%

### 2022-09-07 R/extrapolate_polymod.R
more minor updates

@@ -22,6 +22,12 @@
 #' synthetic_settings_5y_polymod <- extrapolate_polymod(
 #'   population = polymod_population
 #' )
+#' synthetic_settings_5y_polymod
+#' synthetic_settings_5y_fairfield <- extrapolate_polymod(
+#'   population = abs_age_lga("Fairfield (C)")
+#' )
+#' synthetic_settings_5y_fairfield
+#' )
 #' }
 #' @export
 extrapolate_polymod <- function(population,

### 2022-09-08 R/add_population_age_to.R
various small fixes to documentation and vignettes

@@ -7,8 +7,8 @@
 #'   columns, `lower.age.limit`, and `population`. If population is 'polymod' 
 #'   then use the participant-weighted average of POLYMOD country/year 
 #'   distributions. It adds the population via interpolation, using 
-#'   [get_population_function()] to create a function that generates population
-#'   from ages.
+#'   [get_age_population_function()] to create a function that generates 
+#'   population from ages.
 #' 
 #' @param contact_data contact data containing columns `age_to` and `age_from`
 #' @param population Defaults to [get_polymod_population()], but can be any 

### 2022-09-08 R/age-population-year.R

@@ -88,12 +88,6 @@ age_population <- function(
 
   age_var <- dplyr::pull(data, {{ age_col }})
   
-  # ugh tried to make some logic to capture if only one of location and year
-  # were specified instead of the additional column
-  # check_if_only_one_null({{ location_col }} , {{ location }})
-  # check_if_only_one_null({{ year_col }} , {{ year }})
-
-
   if (is.numeric(age_var)) {
     label <- c(paste(
       seq(0, max(age_var), by = 5),

### 2022-09-08 R/checkers.R

@@ -3,9 +3,21 @@
 #'   For example, 'Albury (C).'
 #' @param multiple_lga logical response that allows multiple lgas to be checked
 #'   if set to `TRUE`. Default is FALSE.
-#' @return errors if LGA name not in ABS data
-#' @keywords internal
-#' @noRd
+#' @return errors if LGA name not in ABS data, otherwise returns nothing
+#' @examples 
+#' # returns nothing
+#' check_lga_name("Fairfield (C)")
+#' # if you want to check multiple LGAs you must use the `multiple_lga` flag.
+#' check_lga_name(lga_name = c("Fairfield (C)", "Sydney (C)"), 
+#'                multiple_lga = TRUE)
+#' # this will error, so isn't run
+#' \dontrun{
+#' # don't set the `multiple_lga` flag
+#' check_lga_name(lga_name = c("Fairfield (C)", "Sydney (C)"))
+#' # not a fully specified LGA
+#' check_lga_name("Fairfield")
+#' }
+#' @export
 check_lga_name <- function(
     lga_name,
     multiple_lga = FALSE
@@ -72,41 +84,4 @@ check_state_name <- function(state_name) {
       )
     )
   }
-}
-
-
-check_if_only_one_null <- function(x, y){
-  x_null <- is.null(x)
-  y_null <- is.null(y)
-  null_sum <- x_null + y_null
-  no_null <- null_sum == 0
-  one_null <- null_sum == 1
-  both_null <- null_sum == 2
-  
-  if (no_null){
-    return()
-  } 
-  
-  if (both_null){
-    return()
-  }
-  
-  if (one_null) {
-    msg <- cli::format_error(
-      c(
-        "Both variables need to be specified, only one is",
-        "i" = "{.var x} is {ifelse(is.null(x), 'NULL', x)}",
-        "i" = "{.var y} is {ifelse(is.null(y), 'NULL', y)}",
-        "You are seeing this error message because you need to specify both \\
-        of {.var location_col} & {.var location}, or {.var year_col} & \\
-        {.var year} as either NULL or with values"
-      )
-      
-    )
-    stop(
-      msg,
-      call. = FALSE
-    )
-  }
-  
 }

### 2022-09-08 R/conmat-package.R

@@ -92,6 +92,7 @@ globalVariables(
     "target_weight_sum",
     "transmission_multiplier",
     "update",
+    "upper.age.limit",
     "weight",
     "weight_sum",
     "work_education",

### 2022-09-08 R/predict_contacts_1y.R

@@ -43,6 +43,7 @@
 #' )
 #' @export
 predict_contacts_1y <- function(model, population, age_min = 0, age_max = 100) {
+  
   all_ages <- age_min:age_max
 
   # predict contacts to all integer years, adjusting for the population in a given place

### 2022-09-08 R/predict_setting_contacts.R

@@ -4,12 +4,12 @@
 #'   "school", "work", and "other") over specified age breaks, 
 #'  given some model of contact rate and population age structure. Optionally 
 #'  performs an adjustment for per capita household size. See "details" for more
-#'  information. [adjust_household_contact_matrix()] 
+#'  information.
 #'    
 #' @details The population data is used to determine age range to predict 
 #'   contact rates, and removes ages with zero population, so we do not 
 #'   make predictions for ages with zero populations. Contact rates are 
-#'   predicted yearly between the age groups, using [predict_contact_1y()], 
+#'   predicted yearly between the age groups, using [predict_contacts_1y()], 
 #'   then aggregates these predicted contacts using 
 #'   [aggregate_predicted_contacts()], which aggregates the predictions back to 
 #'   the same resolution as the data, appropriately weighting the contact rate 

### 2022-09-08 README.Rmd

@@
 <!-- badges: start -->
+[![R-CMD-check](https://github.com/njtierney/conmat/workflows/R-CMD-check/badge.svg)](https://github.com/njtierney/conmat/actions)
 [![Codecov test coverage](https://codecov.io/gh/njtierney/conmat/branch/master/graph/badge.svg)](https://codecov.io/gh/njtierney/conmat?branch=master)
-[![R-CMD-check](https://github.com/njtierney/conmat/workflows/R-CMD-check/badge.svg)](https://github.com/njtierney/conmat/actions)
 <!-- badges: end -->
@@
 Contact matrices describe the degree of contact between individuals of given age groups.
-These matrices are commonly used to model how diseases such as COVID-19 spread in a population through social contact.
+
+For example, this matrix describes the number of contacts between individuals
+
+```{r}
+#| label: show-contact
+#| echo: FALSE
+
+name_vec <- c("0-4", "5-9", "10-14")
+cmat <- matrix(
+  data = rep(NA, 9),
+  nrow = 3,
+  ncol = 3,
+  byrow = TRUE,
+  dimnames = list(
+    name_vec,
+    name_vec
+    )
+)
+
+diag(cmat) <- c(10,11,13)
+cmat[upper.tri(cmat)] <- 3:5
+cmat[lower.tri(cmat)] <- 3:5
+
+cmat
+```
+
+The rows and columns represent the age groups of the people.
+On the main diagonal we see that we have a higher number of contacts - showing that people of similar ages tend to interact more with one another.
+
+We can use the information in these matrices to model how diseases such as COVID-19 spread in a population through social contact.
 
@@
 library(conmat)
-polymod_contact_data <- get_polymod_setting_data()
+polymod_contact_data <- get_polymod_contact_data(setting = "work")
 polymod_survey_data <- get_polymod_population()
@@
 
-The contact data is a list of the contacts for each of the settings, "home", "work", "school", and "other". It contains a dataframe for each of these.
+The contact data is a data frame containing the age from and to, and the number of contacts for each of the specified settings, "home", "work", "school", "other", or "all" as well as the number of participants.
+By default, `polymod_contact_data` contains data from "all", but we're going to use the "work" set of data, as it produces an interesting looking dataset.
+Each row contains survey information of the number of contacts.
+Specifically, the number of contacts from one age group to another age group, and then the number of participants in that age group.
 
-```{r show-polymod-str}
-str(polymod_contact_data)
-```
-
-Say looking at the "home" setting, each row contains survey information of the number of contacts.
-Specifically, the number of contacts from one age group to another age group, and then the nuber of participants in that age group.
-
-```{r show-polymod-home}
-polymod_contact_data$home
-```
-
-The survey data contains the lower age limit and the population in that age group.
+The survey data, `polymod_survey_data` contains the lower age limit and the population in that age group.
 
@@
 
-We can create a model for each of the settings with the function `fit_setting_contacts`
+## Predicting the contact rate
+
+We can create a model of the contact *rate* with the function `fit_single_contact_model`
 
 ```{r fit-polymod}
-set.seed(2021-09-24)
-setting_models <- fit_setting_contacts(
-  contact_data_list = polymod_contact_data,
+set.seed(2022-09-06)
+contact_model <- fit_single_contact_model(
+  contact_data = polymod_contact_data,
   population = polymod_survey_data
@@
 
-This contains a list of models, one for each setting. We can look at one, and get summary information out:
+This fits a generalised additive model (GAM), predicting the contact rate, based on a series of prediction terms that describe various features of the contact rates.
 
-```{r}
-names(setting_models)
-setting_models$home
+```{r show-conctact-model}
+contact_model
 ```
 
-So this gives us our baseline model of a contact model. We have fit this model to the existing contact survey data.
+We can use this contact model to then predict the contact rate in a new population.
 
-We can now predict to another age population, to create our "synthetic" contact matrix. Say we want to create a contact matrix for the "Fairfield" LGA, we can extract it out like so:
+As a demonstration, let's take an age population from a given LGA in Australia (this was the initial motivation for the package, so there are some helper functions for Australian specific data).
 
-```{r get-fairfield}
-library(conmat)
+```{r fairfield}
 fairfield_age_pop <- abs_age_lga("Fairfield (C)")
@@
 
-Then we take the model we had earlier, and extrapolate to the fairfield data with `predict_setting_contacts`, also providing some age breaks we want to predict to
+We can then pass the contact model through to `predict_contacts`, along with the fairfield age population data, and some age breaks that we want to predict to.
 
-```{r fairfield-synth-5}
-set.seed(2021-09-24)
-synthetic_settings_5y_fairfield <- predict_setting_contacts(
+```{r predict-contacts}
+set.seed(2022-09-06)
+synthetic_contact_fairfield <- predict_contacts(
+  model = contact_model,
   population = fairfield_age_pop,
-  contact_model = setting_models,
   age_breaks = c(seq(0, 85, by = 5), Inf)
 )
-```
 
-This then returns a list of synthetic matrices, "home", "work", "school", "other", and "all", which is the sum of all matrices.
-
-```{r}
-str(synthetic_settings_5y_fairfield)
-synthetic_settings_5y_fairfield$home
-synthetic_settings_5y_fairfield$all
+synthetic_contact_fairfield
 ```
@@
 
-Looking at the matrices is nice, but let's plot them. We can use `plot_setting_matrix` to plot all at once
+Let's visualise the matrix to get a sense of the predictions with `plot_matrix`. First we need to transform the predictions to a matrix:
 
-```{r fairfield-synth-5-plot}
-# this code is erroring for the moment - something to do with rendering a large plot I think.
-plot_setting_matrices(
-  synthetic_settings_5y_fairfield,
-  title = "Setting-specific synthetic contact matrices (fairfield 2020 projected)"
-)
+```{r plot-matrix-differents}
+synthetic_contact_fairfield %>% 
+  predictions_to_matrix() %>% 
+  plot_matrix()
 ```
 
-You can also plot individual matrices with `plot_matrix`
+## Applying the model across all settings.
 
-```{r plot-matrix-differents}
-plot_matrix(synthetic_settings_5y_fairfield$home)
-plot_matrix(synthetic_settings_5y_fairfield$all)
-```
-
-## Note
-
-The contact matrices created using this package are transposed when compared to the contact matrices discussed by [Prem](https://journals.plos.org/ploscompbiol/article?id=10.1371/journal.pcbi.1005697) and [Mossong](https://journals.plos.org/plosmedicine/article?id=10.1371/journal.pmed.0050074).
-That is, the rows are "age group to", and the columns are "age group from".
-
-## Speeding up computation with `future`
-
-`conmat` supports parallelisation, which is useful in a couple of contexts with the model fitting, here is an example:
-
-```{r load-future}
-library(future)
-plan(multisession, workers = 4)
-```
-
-We set the future plan, saying "multisession", with 4 workers.
-Then we run the same code as above (note that you must specify the plan, otherwise it does not know how to parallelise.
-See the [future package documentation](https://future.futureverse.org/reference/plan.html) for more details):
-
-```{r show-off-furrr}
-polymod_setting_data <- get_polymod_setting_data()
-polymod_population <- get_polymod_population()
-
-contact_model <- fit_setting_contacts(
-  contact_data_list = polymod_setting_data,
-  population = polymod_population
-)
-
-contact_model_pred <- predict_setting_contacts(
-  population = polymod_population,
-  contact_model = contact_model,
-  age_breaks = c(seq(0, 75, by = 5), Inf)
-)
-```
-
-Notably this is about 3 times faster than without using that plan.
+You can also fit a model for all of the settings all at once with a series of functions, `fit_setting_contacts`, and `predict_setting_contacts`.
+This means we can do the above, but for each setting, "home", "work", "school", "other", and "all".
+We would recommend this when using conmat, as it is a pretty common use case.
+However for demonstration purposes we wanted to show how it works for a single matrix here first.
+We also provide details on how to fit the model to each of these settings in parallel.
+For more details on that workflow, see the "getting started" vignette.
 
@@
 In the future we might wrap these data sources and helpers into another package, but for the time being they are here.
-
 Below are a couple of examples of data provided, see the "data sources" vignette and helpful at the website for full details.
 
-You can extract the age population structure for the LGA Fairfield, or Brisbane, like so:
+You can extract the age population structure for the LGA, Brisbane, like so:
 
 ```{r abs-age-lga}
-abs_age_lga("Fairfield (C)")
 abs_age_lga("Brisbane (C)")
@@
 abs_age_state(state_name = "QLD")
-abs_age_state(state_name = "NSW")
 ```
+
+## Note
+
+The contact matrices created using this package are transposed when compared to the contact matrices discussed by [Prem](https://journals.plos.org/ploscompbiol/article?id=10.1371/journal.pcbi.1005697) and [Mossong](https://journals.plos.org/plosmedicine/article?id=10.1371/journal.pmed.0050074).
+That is, the rows are "age group to", and the columns are "age group from".
 

### 2022-10-20 README.Rmd

@@
 [![Codecov test coverage](https://codecov.io/gh/njtierney/conmat/branch/master/graph/badge.svg)](https://codecov.io/gh/njtierney/conmat?branch=master)
+[![R-CMD-check](https://github.com/njtierney/conmat/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/njtierney/conmat/actions/workflows/R-CMD-check.yaml)
 <!-- badges: end -->

### 2022-11-29 README.Rmd
replaced old plot functions with autoplot

--- 2022-09-08 README.Rmd
@@
 
-Let's visualise the matrix to get a sense of the predictions with `plot_matrix`. First we need to transform the predictions to a matrix:
+Let's visualise the matrix to get a sense of the predictions with `autoplot`. First we need to transform the predictions to a matrix:
 
@@
   predictions_to_matrix() %>% 
-  plot_matrix()
+  autoplot()
 ```

### 2022-12-14 README.Rmd
update README figure and minor text changes

--- 2022-11-29 README.Rmd
@@
 <!-- badges: start -->
-[![R-CMD-check](https://github.com/njtierney/conmat/workflows/R-CMD-check/badge.svg)](https://github.com/njtierney/conmat/actions)
+[![R-CMD-check](https://github.com/njtierney/conmat/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/njtierney/conmat/actions/workflows/R-CMD-check.yaml)
 [![Codecov test coverage](https://codecov.io/gh/njtierney/conmat/branch/master/graph/badge.svg)](https://codecov.io/gh/njtierney/conmat?branch=master)

### 2022-12-20 README.Rmd
code restyle

@@
 
-diag(cmat) <- c(10,11,13)
+diag(cmat) <- c(10, 11, 13)
 cmat[upper.tri(cmat)] <- 3:5
@@
 ```{r fit-polymod}
-set.seed(2022-09-06)
+set.seed(2022 - 09 - 06)
 contact_model <- fit_single_contact_model(
@@
 ```{r predict-contacts}
-set.seed(2022-09-06)
+set.seed(2022 - 09 - 06)
 synthetic_contact_fairfield <- predict_contacts(

### 2022-12-20 R/abbreviate_states.R

@@ -1,6 +1,6 @@
 #' Abbreviate Australian State Names
-#' 
-#' Given a full name (Title Case) of an Australian State or Territory, produces 
+#'
+#' Given a full name (Title Case) of an Australian State or Territory, produces
 #'   the abbreviated state name.
 #'
 #' @param state_names vector of state names in long form

### 2022-12-20 R/abs_household_size_population.R

@@ -1,46 +1,41 @@
 #' @title Get population associated with each household size in an LGA or a state
 #' @param state target Australian state name in abbreviated form, such as "QLD", "NSW", or "TAS"
-#' @param lga target Australian local government area (LGA) name, such as "Fairfield (C)".  See 
+#' @param lga target Australian local government area (LGA) name, such as "Fairfield (C)".  See
 #'   [abs_lga_lookup()] for list of lga names
-#' @return returns a data frame with household size and the population associated with it in each LGA or state. 
+#' @return returns a data frame with household size and the population associated with it in each LGA or state.
 #' @export
-#' @examples 
-#'abs_household_size_population(state = "NSW")
+#' @examples
+#' abs_household_size_population(state = "NSW")
 abs_household_size_population <- function(state = NULL, lga = NULL) {
-  
   level <- dplyr::case_when(
     is.null(state) & is.null(lga) ~ "national",
     !is.null(state) & is.null(lga) ~ "state",
     is.null(state) & !is.null(lga) ~ "lga",
     TRUE ~ "erroneous"
   )
-  
-# get state mean household sizes
-household_data <- abs_household_lga %>%
-  dplyr::filter(year == max(year),
-                n_persons_usually_resident != "total") %>%
-  dplyr::mutate(
-    # household size as a number, assuming all people in households 8+ are
-    # exactly 8
-    size = readr::parse_number(n_persons_usually_resident),
-    # number of *people* in a household of that size
-    n_people = n_households * size,
-  ) %>%
-  dplyr::select(-c(n_persons_usually_resident, n_households)) %>%
-  dplyr::rename(household_size = size)
 
-household_data <- switch(
-  
-  level,
-  
-  national = household_data,
-  
-  state = household_data %>%
-    dplyr::filter(state == !!state),
-  
-  lga = household_data %>%
-    dplyr::filter(lga == !!lga) 
-  
-)
-return(household_data)
+  # get state mean household sizes
+  household_data <- abs_household_lga %>%
+    dplyr::filter(
+      year == max(year),
+      n_persons_usually_resident != "total"
+    ) %>%
+    dplyr::mutate(
+      # household size as a number, assuming all people in households 8+ are
+      # exactly 8
+      size = readr::parse_number(n_persons_usually_resident),
+      # number of *people* in a household of that size
+      n_people = n_households * size,
+    ) %>%
[…]

### 2022-12-20 R/abs_per_capita_household_size_lga.R

@@ -1,15 +1,13 @@
 #' @title Get household size distribution based on  LGA name
-#' @param lga target Australian local government area (LGA) name, such as "Fairfield (C)".  See 
+#' @param lga target Australian local government area (LGA) name, such as "Fairfield (C)".  See
 #'   [abs_lga_lookup()] for list of lga names
-#' @return returns a numeric value depicting the per capita household size of the specified LGA 
+#' @return returns a numeric value depicting the per capita household size of the specified LGA
 #' @export
-#' @examples 
-#' abs_per_capita_household_size_lga(lga ="Fairfield (C)")
-#' 
+#' @examples
+#' abs_per_capita_household_size_lga(lga = "Fairfield (C)")
+#'
 abs_per_capita_household_size_lga <- function(lga = NULL) {
-  
-  
-  check_lga_name(lga,multiple_lga = FALSE)
+  check_lga_name(lga, multiple_lga = FALSE)
 
   # given ABS data on household sizes for a *single location*, get average
   # household sizes *per person* from ABS - assuming a max of 8 people per
@@ -17,18 +15,17 @@ abs_per_capita_household_size_lga <- function(lga = NULL) {
   # than 7, by comparing with LGA populations, but they were improbably
   # enormous, probably because some of the population lives in facilities, not
   # households.
-  
+
   lga <- rlang::enquo(lga)
-  
-  household_data <-  abs_household_size_population(lga=lga)
+
+  household_data <- abs_household_size_population(lga = lga)
   # set up aggregation
-  household_data <-  household_data %>%
+  household_data <- household_data %>%
     dplyr::filter(lga == !!lga) %>%
     dplyr::group_by(lga)
-  
-  
+
+
   # aggregate and average household sizes
   household_data %>%
     per_capita_household_size()
-    
 }

### 2022-12-20 R/add_modelling_features.R

@@ -1,33 +1,33 @@
 #' Add features required for modelling to the dataset
-#' 
+#'
 #' This function adds three main groups of features to the data. It is used
 #'   internally in [fit_single_contact_model()] and [predict_contacts_1y()].
-#'  It requires columns named `age_to` and `age_from`. The three types of 
+#'  It requires columns named `age_to` and `age_from`. The three types of
 #'  features it adds are described below:
-#'   1) Population distribution of contact ages from the function 
-#'     [add_population_age_to()], which requires a column called "age_to" 
+#'   1) Population distribution of contact ages from the function
+#'     [add_population_age_to()], which requires a column called "age_to"
 #'     representing the age of the person who had contact. It creates a column
 #'     called `pop_age_to`. [add_population_age_to()] takes an extra argument
 #'     for population, which defaults to [get_polymod_population()], but needs
 #'     to be a data frame with columns, `lower.age.limit`, and `population`.
-#'   2) School work participation, which is from the function 
-#'     [add_school_work_participation()]. This requires columns `age_to` and 
+#'   2) School work participation, which is from the function
+#'     [add_school_work_participation()]. This requires columns `age_to` and
 #'     `age_from`, but will operate on any column starting with `age` and adds
-#'     columns: `school_probability`, `work_probability`, 
+#'     columns: `school_probability`, `work_probability`,
 #'     `school_year_probability`, and `school_weighted_pop_fraction`.
-#'   3) Offset is added on to the data using [add_offset()]. This requires 
-#'     variables `school_weighted_pop_fraction` (from 
-#'     [add_school_work_participation()]) and `pop_age_to` (from 
-#'     [add_school_work_participation()]). It adds two columns, 
+#'   3) Offset is added on to the data using [add_offset()]. This requires
+#'     variables `school_weighted_pop_fraction` (from
+#'     [add_school_work_participation()]) and `pop_age_to` (from
+#'     [add_school_work_participation()]). It adds two columns,
 #'     `log_contactable_population_school`, and `log_contactable_population`.
 #'
 #' @param contact_data contact data with columns `age_to` and `age_from`
-#' @param ... extra dots passed to `population` argument of 
+#' @param ... extra dots passed to `population` argument of
 #'   [add_population_age_to()]
 #' @return data frame with 11 extra columns - the contents of `contact_data`,
[…]

### 2022-12-20 R/add_symmetrical_features.R

@@ -2,7 +2,7 @@
 #' @description This function adds 6 columns to assist with describing
 #'   various age based interactions for model fitting. Requires that the
 #'   age columns are called "age_from", and "age_to"
-#' 
+#'
 #' @param data data.frame with columns, `age_from`, and `age_to`
 #' @return data.frame with 6 more columns, `gam_age_offdiag`, `gam_age_offdiag_2`, `gam_age_diag_prod`, `gam_age_diag_sum`, `gam_age_pmax`, `gam_age_pmin`,
 #' @examples
@@ -11,13 +11,13 @@
 #'   age_from = vec_age,
 #'   age_to = vec_age
 #' )
-#' 
+#'
 #' add_symmetrical_features(dat_age)
-#' 
+#'
 #' @export
 add_symmetrical_features <- function(data) {
   # add terms back into the data frame
-  data %>% 
+  data %>%
     dplyr::mutate(
       gam_age_offdiag = abs(age_from - age_to),
       gam_age_offdiag_2 = abs(age_from - age_to)^2,
@@ -26,7 +26,6 @@ add_symmetrical_features <- function(data) {
       gam_age_pmax = pmax(age_from, age_to),
       gam_age_pmin = pmin(age_from, age_to)
     )
-
 }
 
 # gam(

### 2022-12-20 R/age-population-year.R

@@ -2,22 +2,22 @@
 #'
 #' @description This function helps clean up datasets of population data, which
 #'   might be similar to `socialmixr::wpp_age()` or a dataset with columns
-#'   representing: population, location, age, and year. If age is numeric, it 
-#'   groups ages into age groups with 5 year bins (0-4, 5-9, etc). It then 
-#'   separates age groups into two column of these lower and upper limits. 
-#'   Finally, it filters data passed to the specified year and location. If no 
+#'   representing: population, location, age, and year. If age is numeric, it
+#'   groups ages into age groups with 5 year bins (0-4, 5-9, etc). It then
+#'   separates age groups into two column of these lower and upper limits.
+#'   Finally, it filters data passed to the specified year and location. If no
 #'   year or location is provided then all years or locations are used.
 
 #' @param data dataset containing information on population for a given age,
 #'   country, and year
 #' @param age_col bare variable name for the column with age information
-#' @param location_col bare variable name for the column with location 
+#' @param location_col bare variable name for the column with location
 #'   information. If using, both `location_col` & `location` must be specified.
-#' @param location character vector with location names. If using, both 
+#' @param location character vector with location names. If using, both
 #'   `location_col` & `location` must be specified.
-#' @param year_col bare variable name for the column with year information. If 
+#' @param year_col bare variable name for the column with year information. If
 #'   using, both `year_col` & `year` must be specified.
-#' @param year numeric vector representing the desired year(s). If using, both 
+#' @param year numeric vector representing the desired year(s). If using, both
 #'   `year_col` & `year` must be specified.
 #' @return tidy dataset with information on population of different age bands
 #' @export
@@ -41,7 +41,7 @@
 #'   location = "Afghanistan",
 #'   age_col = lower.age.limit
 #' )
-#' 
+#'
 #' # Tidy data for a given location irrespective of location
 #' age_population(
 #'   data = world_data,
@@ -74,20 +74,17 @@
 #'   year = 2020
 #' )
 #'
-age_population <- function(
-  data,
-  location_col = NULL,
-  location = NULL,
-  age_col,
-  year_col = NULL,
-  year = NULL
-) {
-
+age_population <- function(data,
+                           location_col = NULL,
+                           location = NULL,
+                           age_col,
+                           year_col = NULL,
+                           year = NULL) {
   # checks the data type of age col and puts age into buckets if its numeric
[…]

### 2022-12-20 R/apply_vaccination.R

@@ -66,19 +66,15 @@
 #'   acquisition_col = acquisition,
 #'   transmission_col = transmission
 #' )
-#'}
+#' }
 #' @export
-apply_vaccination <- function(
-  ngm,
-  data,
-  coverage_col,
-  acquisition_col,
-  transmission_col
-) {
-  
-  
-  check_dimensions(ngm,data)
-  
+apply_vaccination <- function(ngm,
+                              data,
+                              coverage_col,
+                              acquisition_col,
+                              transmission_col) {
+  check_dimensions(ngm, data)
+
   transmission_reduction_matrix <- data %>%
     # compute percentage reduction in acquisition and transmission in each age group
     dplyr::mutate(

### 2022-12-20 R/checkers.R

@@ -4,12 +4,14 @@
 #' @param multiple_lga logical response that allows multiple lgas to be checked
 #'   if set to `TRUE`. Default is FALSE.
 #' @return errors if LGA name not in ABS data, otherwise returns nothing
-#' @examples 
+#' @examples
 #' # returns nothing
 #' check_lga_name("Fairfield (C)")
 #' # if you want to check multiple LGAs you must use the `multiple_lga` flag.
-#' check_lga_name(lga_name = c("Fairfield (C)", "Sydney (C)"), 
-#'                multiple_lga = TRUE)
+#' check_lga_name(
+#'   lga_name = c("Fairfield (C)", "Sydney (C)"),
+#'   multiple_lga = TRUE
+#' )
 #' # this will error, so isn't run
 #' \dontrun{
 #' # don't set the `multiple_lga` flag
@@ -19,17 +21,15 @@
 #' }
 #' @keywords internal
 #' @noRd
-check_lga_name <- function(
-    lga_name,
-    multiple_lga = FALSE
-) {
+check_lga_name <- function(lga_name,
+                           multiple_lga = FALSE) {
   lga_match <- dplyr::filter(
     abs_pop_age_lga_2020,
     lga %in% lga_name
   )
-  
+
   does_lga_match <- nrow(lga_match) > 1
-  
+
   if (!does_lga_match) {
     rlang::abort(
       message = c(
@@ -40,15 +40,15 @@ check_lga_name <- function(
       )
     )
   }
-  
+
   if (does_lga_match) {
     unique_lga_names <- abs_pop_age_lga_2020 %>%
       dplyr::filter(lga %in% lga_name) %>%
       dplyr::pull(lga) %>%
       unique()
-    
+
     more_than_one_lga <- length(unique_lga_names) > 1
-    
+
     if (more_than_one_lga & !multiple_lga) {
       rlang::abort(
         message = c(
@@ -69,18 +69,18 @@ check_lga_name <- function(
 #' @keywords internal
 #' @noRd
 check_state_name <- function(state_name, multiple_state = FALSE) {
-  state_that_matches <-  abs_pop_age_lga_2020 %>%
+  state_that_matches <- abs_pop_age_lga_2020 %>%
     dplyr::select(state) %>%
     dplyr::distinct() %>%
     dplyr::filter(state %in% state_name) %>%
     dplyr::pull(state)
-  
+
   state_match <- is.element(state_name, state_that_matches)
-  
+
[…]

### 2022-12-20 R/conmat-package.R

@@ -8,7 +8,7 @@
 #' @export
 ggplot2::autoplot
 
-#' @import rlang 
+#' @import rlang
 
 # The following block is used by usethis to automatically manage
 # roxygen namespace tags. Modify with care!

### 2022-12-20 R/constructors.R

@@ -1,10 +1,12 @@
-new_prediction_matrix <- function(matrix){
+new_prediction_matrix <- function(matrix) {
   class(matrix) <- c("conmat_prediction_matrix", class(matrix))
   matrix
 }
 
-new_setting_prediction_matrix <- function(list_matrix){
-  class(list_matrix) <- c("conmat_setting_prediction_matrix", 
-                          class(list_matrix))
+new_setting_prediction_matrix <- function(list_matrix) {
+  class(list_matrix) <- c(
+    "conmat_setting_prediction_matrix",
+    class(list_matrix)
+  )
   list_matrix
 }

### 2022-12-20 R/data_abs_education_state_2020.R

@@ -1,9 +1,9 @@
-#' @title 2020 ABS education population data, interpolated into 1 year bins, 
+#' @title 2020 ABS education population data, interpolated into 1 year bins,
 #'   by state.
 #'
-#' @description A dataset containing Australian Bureau of Statistics education 
-#'   data by state for 2020. These were interpolated into 1 year age bins. 
-#'   There are still some issued with the methods used, as the interpolated 
+#' @description A dataset containing Australian Bureau of Statistics education
+#'   data by state for 2020. These were interpolated into 1 year age bins.
+#'   There are still some issued with the methods used, as the interpolated
 #'   values are sometimes higher than the population.
 #'
 #' @format A data frame with 808 rows and 6 variables:

### 2022-12-20 R/data_abs_state_work.R

@@ -1,8 +1,8 @@
 #' State wise ABS work population data on different ages for year 2016
 #'
-#' A dataset containing Australian Bureau of Statistics labour force population 
-#'   data by state for 2016. The data sourced from 2016 Census - Employment, 
-#'   Income and Education through TableBuilder have been randomly adjusted by 
+#' A dataset containing Australian Bureau of Statistics labour force population
+#'   data by state for 2016. The data sourced from 2016 Census - Employment,
+#'   Income and Education through TableBuilder have been randomly adjusted by
 #'   the ABS to avoid the release of confidential data.
 #'
 #' @format A data frame with 1044 rows and 6 variables:
@@ -11,7 +11,7 @@
 #'   \item{state}{String. Abbreviated name of state or territory, e.g., 'NSW',
 #'     'VIC', 'QLD' and so on.}
 #'   \item{age}{Ages from 0 to 115.}
-#'   \item{employed_population}{Number of people employed including people 
+#'   \item{employed_population}{Number of people employed including people
 #'     with full-time, part-time employment status.}
 #'   \item{total_population}{Total population belonging to the age.}
 #'   \item{proportion}{The ratio of employed population and total population

### 2022-12-20 R/data_age_group_lookup.R

@@ -1,7 +1,7 @@
 #' Lookup table of age groups in 5 year bins
 #'
-#' A dataset containing age lower and upper levels with age group 
-#' 
+#' A dataset containing age lower and upper levels with age group
+#'
 #'
 #' @format A data frame with 21 rows and 3 variables:
 #' \describe{

### 2022-12-20 R/extrapolate_polymod.R

@@ -1,20 +1,20 @@
 #' Fit all-of-polymod model and extrapolate to a given population an age breaks
-#' 
+#'
 #' Uses [estimate_setting_contacts()] to fit a contact model on the data from
 #'   polymod and later extrapolate on to a desired population.
 #'
 #' @param population data set with information on the population of the desired
 #'   location - containing `lower.age.limit` and `population` columns. See
 #'   `get_polymod_population()` for an example of this data.
-#' @param age_breaks vector depicting age values. Default value is 
+#' @param age_breaks vector depicting age values. Default value is
 #'   `c(seq(0, 75, by = 5), Inf)`
-#' @param per_capita_household_size Optional (defaults to NULL). When set, it 
-#'   adjusts the household contact matrix by some per capita household size. 
+#' @param per_capita_household_size Optional (defaults to NULL). When set, it
+#'   adjusts the household contact matrix by some per capita household size.
 #'   To set it, provide a single number, the per capita household size. More
-#'   information is provided below in Details. See 
+#'   information is provided below in Details. See
 #'   [get_per_capita_household_size()] function for a helper for Australian
 #'    data with a workflow on how to get this number.
-#' @return Returns setting-specific and combined contact matrices for the 
+#' @return Returns setting-specific and combined contact matrices for the
 #'   desired ages.
 #' @examples
 #' \dontrun{
@@ -27,22 +27,19 @@
 #'   population = abs_age_lga("Fairfield (C)")
 #' )
 #' synthetic_settings_5y_fairfield
-#' )
 #' }
 #' @export
 extrapolate_polymod <- function(population,
                                 age_breaks = c(seq(0, 75, by = 5), Inf),
                                 per_capita_household_size = NULL) {
-  
   contact_model_pred <- predict_setting_contacts(
     population = population,
-    # using already fit polymod_setting_models object 
+    # using already fit polymod_setting_models object
     # from `create-polymod-model.R`
     contact_model = polymod_setting_models,
     age_breaks = age_breaks,
     per_capita_household_size = per_capita_household_size
   )
-  
+
   contact_model_pred
-  
 }

### 2022-12-20 R/fit_setting_contacts.R

@@ -1,50 +1,49 @@
 #' Fit a contact model to a survey poulation
-#' 
+#'
 #' fits a gam model for each setting on the survey population data & the
-#'   setting wise contact data. The underlying method is described in more 
+#'   setting wise contact data. The underlying method is described in more
 #'   detail in [fit_single_contact_model()]. The models can be fit in parallel,
 #'   see the examples.
-#' 
+#'
 #' @param contact_data_list A list of dataframes, each containing informatio
 #'   on the setting (home, work, school, other), age_from, age_to,
 #'   the number of contacts, and the number of participants. Example data
 #'   can be retrieved with [get_polymod_setting_data()].
-#' @param population survey population data, containing columns 
+#' @param population survey population data, containing columns
 #'   `lower.age.limit` and `population`. Example data can be retrieved with
 #'   [get_polymod_population()].
-#' @param symmetrical whether to enforce symmetrical terms in the model. 
-#'   Defaults to TRUE. See `details` of `fit_single_contact_model` for more 
+#' @param symmetrical whether to enforce symmetrical terms in the model.
+#'   Defaults to TRUE. See `details` of `fit_single_contact_model` for more
 #'   information.
 #' @return list of fitted gam models - one for each setting provided
 #' @author Nicholas Tierney
 #' @export
-#' @examples 
+#' @examples
 #' # These aren't being  run as they take too long to fit
 #' \dontrun{
 #' contact_model <- fit_setting_contacts(
-#'   contact_data_list = get_polymod_setting_data(), 
+#'   contact_data_list = get_polymod_setting_data(),
 #'   population = get_polymod_population()
 #' )
-#' 
+#'
 #' # can fit the model in parallel
 #' library(future)
 #' plan(multisession, workers = 4)
-#' 
+#'
 #' polymod_setting_data <- get_polymod_setting_data()
 #' polymod_population <- get_polymod_population()
-#' 
+#'
 #' contact_model <- fit_setting_contacts(
 #'   contact_data_list = polymod_setting_data,
 #'   population = polymod_population
 #' )
 #' }
-fit_setting_contacts <- function(contact_data_list, 
+fit_setting_contacts <- function(contact_data_list,
                                  population,
                                  symmetrical = TRUE) {
-
   check_if_list(contact_data_list)
-  
-  
+
+
   furrr::future_map(
     .x = contact_data_list,
     .f = fit_single_contact_model,
[…]

### 2022-12-20 R/fit_single_contact_model.R

@@ -1,24 +1,24 @@
 #' @title Fit a single GAM contact model to a dataset
-#' 
+#'
 #' @description This is the workhorse of the `conmat` package, and is typically
-#'   used inside [fit_setting_contacts()]. It predicts the contact rate between 
-#'   all age bands (the contact rate between ages 0 and 1, 0 and 2, 0 and 3, 
-#'   and so on), for a specified setting, with specific terms being added for 
+#'   used inside [fit_setting_contacts()]. It predicts the contact rate between
+#'   all age bands (the contact rate between ages 0 and 1, 0 and 2, 0 and 3,
+#'   and so on), for a specified setting, with specific terms being added for
 #'   given settings. See "details" for further information.
-#'   
-#' @details The model fit is a Generalised Additive Model (GAM). We provide two 
-#'   "modes" for model fitting. Either using "symmetric" or "non-symmetric" 
+#'
+#' @details The model fit is a Generalised Additive Model (GAM). We provide two
+#'   "modes" for model fitting. Either using "symmetric" or "non-symmetric"
 #'   model predictor terms with the logical variance "symmetrical", which is set
-#'   to TRUE by default. We recommend using the "symmetrical" terms as it 
-#'   reflects the fact that contacts are symmetric - person A having contact 
+#'   to TRUE by default. We recommend using the "symmetrical" terms as it
+#'   reflects the fact that contacts are symmetric - person A having contact
 #'   with person B means person B has had contact with person A. We've included
-#'   a variety of terms to account for assortativity with age, where people of 
-#'   similar ages have more contact with each other. And included terms to 
-#'   account for intergenerational contact patterns, where parents and 
+#'   a variety of terms to account for assortativity with age, where people of
+#'   similar ages have more contact with each other. And included terms to
+#'   account for intergenerational contact patterns, where parents and
 #'   grandparents will interact with their children and grand children.
-#'   These terms are fit with a smoothing function. Specifically, the relevant 
+#'   These terms are fit with a smoothing function. Specifically, the relevant
 #'   code looks like this:
-#'   
+#'
 #'   ``` r
 #'   # abs(age_from - age_to)
 #'   s(gam_age_offdiag) +
@@ -33,24 +33,24 @@
 #'   # pmin(age_from, age_to)
 #'   s(gam_age_pmin)
 #'   ```
-#'   
-#'   We also include predictors for the probability of attending school, and 
-#'   attending work. These are computed as the probability that a person goes 
[…]

### 2022-12-20 R/generate-ngm.R

@@ -1,30 +1,30 @@
 #' @title Calculate next generation contact matrices
-#' 
-#' @description Once infected, a person can transmit an infectious disease to 
-#'   another, creating generations of infected individuals. We can define a 
-#'   matrix describing the number of newly infected individuals in given 
-#'   categories, such as age, for consecutive generations. This matrix is 
-#'   called a "next generation matrix" (NGM). 
-#'   
-#' @details The NGM can be used to calculate the expected number of secondary 
-#'   infections in a given age group. Given certain age breaks, we compute the 
-#'   unscaled next generation matrices for that location across different 
-#'   settings & age groups using the contact rates extrapolated from POLYMOD 
-#'   survey data on the specified location, adjusted by the per capita 
-#'   household size and the setting-specific relative per-contact transmission 
-#'   probability matrices for the same age groups. These NGMs are then scaled 
-#'   according to a target reproduction number (which is provided as an 
-#'   argument) using the ratio of the desired R0 and the R0 of the NGM 
-#'   for the combination of all settings. The R0 of the combination of all 
-#'   settings is obtained by calculating the unique, positive eigen value of 
-#'   the combination NGM. This ratio is then used to scale all the setting 
-#'   specific NGMs. 
-#' 
-#' @param state_name target Australian state name in abbreviated form, such 
+#'
+#' @description Once infected, a person can transmit an infectious disease to
+#'   another, creating generations of infected individuals. We can define a
+#'   matrix describing the number of newly infected individuals in given
+#'   categories, such as age, for consecutive generations. This matrix is
+#'   called a "next generation matrix" (NGM).
+#'
+#' @details The NGM can be used to calculate the expected number of secondary
+#'   infections in a given age group. Given certain age breaks, we compute the
+#'   unscaled next generation matrices for that location across different
+#'   settings & age groups using the contact rates extrapolated from POLYMOD
+#'   survey data on the specified location, adjusted by the per capita
+#'   household size and the setting-specific relative per-contact transmission
+#'   probability matrices for the same age groups. These NGMs are then scaled
+#'   according to a target reproduction number (which is provided as an
+#'   argument) using the ratio of the desired R0 and the R0 of the NGM
+#'   for the combination of all settings. The R0 of the combination of all
[…]

### 2022-12-20 R/get_data_abs_age_education.R

@@ -1,75 +1,66 @@
-#' @title Return  data on educated population for a given age and state or 
+#' @title Return  data on educated population for a given age and state or
 #'   lga of Australia.
-#' @param state target Australian state name or a vector with multiple state 
+#' @param state target Australian state name or a vector with multiple state
 #'   names in its abbreviated form, such as "QLD", "NSW", or "TAS"
-#' @param lga target Australian local government area (LGA) name, such as 
-#'   "Fairfield (C)" or a vector with multiple lga names. See 
+#' @param lga target Australian local government area (LGA) name, such as
+#'   "Fairfield (C)" or a vector with multiple lga names. See
 #'   [abs_lga_lookup()] for list of lga names.
 #' @param age a numeric or numeric vector denoting ages between 0 to 115. The
 #'    default is to return all ages.
-#' @return dataset with information on the number of educated people belonging 
+#' @return dataset with information on the number of educated people belonging
 #'   to a particular age, its total population and the corresponding proportion.
 #' @export
 #' @examples
-#' get_data_abs_age_education(state="VIC")
-#' get_data_abs_age_education(state="WA",lga="Albany (C)",age=1:5)
-#' get_data_abs_age_education(state=c("QLD","TAS"),age=5)
-#' get_data_abs_age_education(lga=c("Albury (C)","Barcoo (S)"),age=10)
-
+#' get_data_abs_age_education(state = "VIC")
+#' get_data_abs_age_education(state = "WA", lga = "Albany (C)", age = 1:5)
+#' get_data_abs_age_education(state = c("QLD", "TAS"), age = 5)
+#' get_data_abs_age_education(lga = c("Albury (C)", "Barcoo (S)"), age = 10)
+#'
 get_data_abs_age_education <- function(age = NULL, state = NULL, lga = NULL) {
-   
-  # checks only for state 
-   if (!is.null(state) & is.null(lga)) {
-      
-     check_state_name(state,multiple_state = TRUE)
-     data_subset <- data_abs_state_education %>%
-        dplyr::filter(state %in% {{ state }})
-      
-    } else{
-      # checks for lga 
-      if (!is.null(lga)) {
-        
-        check_lga_name(lga, multiple_lga = TRUE)
-        
-        # checks if there is a state argument as well
-        # if state argument present, it filters for it
-        if (!is.null(state))
-        {
-          data_subset <- data_abs_lga_education %>%
-            dplyr::filter(lga %in% {{ lga }} , state %in% {{ state }})
-         
-          # if empty tibble , error message 
[…]

### 2022-12-20 R/get_per_capita_household_size.R

@@ -5,7 +5,7 @@
 #'     or LGA.
 #' @author Nick Golding
 #' @export
-#' @examples 
+#' @examples
 #' get_per_capita_household_size(lga = "Fairfield (C)")
 #' get_per_capita_household_size(state = "NSW")
 #' \dontrun{
@@ -13,37 +13,36 @@
 #' get_per_capita_household_size(state = "NSW", lga = "Fairfield (C)")
 #' }
 get_per_capita_household_size <- function(state = NULL, lga = NULL) {
-  
   level <- dplyr::case_when(
     is.null(state) & is.null(lga) ~ "national",
     !is.null(state) & is.null(lga) ~ "state",
     is.null(state) & !is.null(lga) ~ "lga",
     TRUE ~ "erroneous"
   )
-  
+
   if (level == "erroneous") {
-    stop ("only one of state and lga may be specified")
+    stop("only one of state and lga may be specified")
   }
-  
+
   if (length(state) > 1 | length(lga) > 1) {
-    stop ("only one state or LGA at a time, please")
+    stop("only one state or LGA at a time, please")
   }
-  
+
   if (!is.null(state)) {
     check_state_name(state)
   }
-  
-  if (!is.null(lga)){
+
+  if (!is.null(lga)) {
     check_lga_name(lga)
   }
-  
+
   # given ABS data on household sizes for a *single location*, get average
   # household sizes *per person* from ABS - assuming a max of 8 people per
   # households. Note - I tried computing the mean size of the households larger
   # than 7, by comparing with LGA populations, but they were improbably
   # enormous, probably because some of the population lives in facilities, not
   # households.
-  
+
   # get state mean household sizes
   household_data <- abs_household_lga %>%
     dplyr::filter(
@@ -57,33 +56,27 @@ get_per_capita_household_size <- function(state = NULL, lga = NULL) {
       # number of *people* in a household of that size
       n_people = n_households * size,
     )
-  
+
   state <- rlang::enquo(state)
   lga <- rlang::enquo(lga)
-  
+
   # set up aggregation
-  household_data <- switch(
-    
-    level,
-    
+  household_data <- switch(level,
     national = household_data,
-    
     state = household_data %>%
       dplyr::filter(state == !!state) %>%
       dplyr::group_by(state),
-    
     lga = household_data %>%
       dplyr::filter(lga == !!lga) %>%
       dplyr::group_by(lga)
-    
   )
-  
+
[…]

### 2022-12-20 R/get_polymod_per_capita_household_size.R

@@ -1,11 +1,11 @@
 #' @title Get polymod per capita houshold size.
-#' 
+#'
 #' @description Convenience function to help get the per capita household size.
 #'   This is calculated as `mean(socialmixr::polymod$participants$hh_size)`.
-#' 
+#'
 #' @return number, 3.248971
 #' @author Nicholas Tierney
 #' @export
 get_polymod_per_capita_household_size <- function() {
-    mean(socialmixr::polymod$participants$hh_size)
+  mean(socialmixr::polymod$participants$hh_size)
 }

### 2022-12-20 R/get_polymod_population.R

@@ -5,31 +5,31 @@
 #'   participants). Note that we don't want to weight by survey age
 #'   distributions for this, since the total number of *participants*
 #'   represents the sampling. It uses the participant data from the polymod
-#'   survey as well as the age specific population data from `socialmixr` 
-#'   R package to return the age specific average population of different, 
-#'   countries weighted by the number of participants from those countries who 
+#'   survey as well as the age specific population data from `socialmixr`
+#'   R package to return the age specific average population of different,
+#'   countries weighted by the number of participants from those countries who
 #'   participated in the polymod survey.
 #'
 #' @param countries countries to extract data from. Default is to get: Belgium,
-#'   Finland, Germany, Italy, Luxembourg, Netherlands, Poland, and 
+#'   Finland, Germany, Italy, Luxembourg, Netherlands, Poland, and
 #'   United Kingdom.
 #' @return data frame with two columns: `lower.age.limit` and `population`
 #' @examples
 #' get_polymod_population()
-#' get_polymod_population("Belgium") 
-#' get_polymod_population("United Kingdom") 
-#' get_polymod_population("Italy") 
+#' get_polymod_population("Belgium")
+#' get_polymod_population("United Kingdom")
+#' get_polymod_population("Italy")
 #' @export
 get_polymod_population <- function(countries = c(
-    "Belgium",
-    "Finland",
-    "Germany",
-    "Italy",
-    "Luxembourg",
-    "Netherlands",
-    "Poland",
-    "United Kingdom"
-  )) {
+                                     "Belgium",
+                                     "Finland",
+                                     "Germany",
+                                     "Italy",
+                                     "Luxembourg",
+                                     "Netherlands",
+                                     "Poland",
+                                     "United Kingdom"
+                                   )) {
   socialmixr::polymod$participants %>%
     dplyr::filter(
       !is.na(year),
@@ -55,7 +55,7 @@ get_polymod_population <- function(countries = c(
     ) %>%
     dplyr::summarise(
       population = stats::weighted.mean(population, participants)
-    ) %>% 
+    ) %>%
     conmat_population(
       age = lower.age.limit,
       population = population

### 2022-12-20 R/get_polymod_setting_data.R

@@ -1,18 +1,20 @@
 #' Get polymod setting data
-#' 
-#' `get_polymod_setting_data()` acts as an extension of 
-#'   `get_polymod_contact_data()`, and extracts the setting wise contact data 
+#'
+#' `get_polymod_setting_data()` acts as an extension of
+#'   `get_polymod_contact_data()`, and extracts the setting wise contact data
 #'   on the desired country, as a list.
 
 #' @param countries countries to extract data from
-#' @return A list of data frames, of the polymod data. One list per setting: 
+#' @return A list of data frames, of the polymod data. One list per setting:
 #'   "home", "work", "school", and "other".
 #' @examples
 #' get_polymod_setting_data()
 #' get_polymod_setting_data("Belgium")
 #' @export
-get_polymod_setting_data <- function(countries = c("Belgium", "Finland", "Germany", "Italy", "Luxembourg", "Netherlands", 
-                                                   "Poland", "United Kingdom")) {
+get_polymod_setting_data <- function(countries = c(
+                                       "Belgium", "Finland", "Germany", "Italy", "Luxembourg", "Netherlands",
+                                       "Poland", "United Kingdom"
+                                     )) {
   list(
     home = get_polymod_contact_data(
       setting = "home",

### 2022-12-20 R/model-tidiers.R

@@ -8,30 +8,30 @@
 #' formula_terms <- get_formulas_terms(sim_m)
 #' formula_terms
 #' }
-
-get_formulas_terms <- function(model){
-  as.character(attr(stats::terms(model$formula), "variables"))[-c(1,2)]
+#'
+get_formulas_terms <- function(model) {
+  as.character(attr(stats::terms(model$formula), "variables"))[-c(1, 2)]
 }
 
 # extract_term_name(formula_terms)
-extract_term_name <- function(x){
+extract_term_name <- function(x) {
   term <- as.character(stringr::str_extract_all(x, "(?<=\\().+?(?=\\))"))
   glue::glue("fitted_{term}")
 }
 
 # head(predict_gam_term(sim_m, sim_data, formula_terms[1]))
 # tail(predict_gam_term(sim_m, sim_data, formula_terms[1]))
-predict_gam_term <- function(model, data, terms){
+predict_gam_term <- function(model, data, terms) {
   c(
     predict(model,
-            data, 
-            type = "terms", 
-            terms = terms)
+      data,
+      type = "terms",
+      terms = terms
+    )
   )
-  
 }
 
-add_intercept <- function(data, model){
+add_intercept <- function(data, model) {
   dplyr::mutate(
     .data = data,
     fitted_intercept = model$coefficients[1]
@@ -40,23 +40,22 @@ add_intercept <- function(data, model){
 
 tidy_predict_term <- function(data,
                               model,
-                              term){
+                              term) {
   term_name <- extract_term_name(term)
-  
+
   dat_term <- tibble::tibble(x = predict_gam_term(model, data, term))
-  
+
   stats::setNames(dat_term, term_name)
-  
 }
 
-add_fitted_overall <- function(data){
-  data %>% 
+add_fitted_overall <- function(data) {
+  data %>%
     dplyr::mutate(
       fitted_overall = rowSums(
         dplyr::across(
           .cols = c(tidyselect::starts_with("fitted"))
-          )
         )
+      )
     )
 }
 
@@ -69,10 +68,9 @@ add_gam_predictions <- function(data, model, term) {
     data = data_modelling,
     model = model
   )
-  
-  data %>% 
-    add_intercept(model) %>% 
-    dplyr::bind_cols(predictions) %>% 
+
+  data %>%
+    add_intercept(model) %>%
+    dplyr::bind_cols(predictions) %>%
     add_fitted_overall()
-  
 }

### 2022-12-20 R/plot_matrix.R

@@ -1,52 +1,52 @@
 #' Visualise predicted contact matrix
-#' 
-#' Visualising the predicted contact rates facilitates understanding the 
-#'   underlying patterns and relationships between age groups in different 
+#'
+#' Visualising the predicted contact rates facilitates understanding the
+#'   underlying patterns and relationships between age groups in different
 #'   settings (workplace, home, school, other). The `plot_matrix()` function
-#'   takes a contact matrix and visualises it, with the x and y axes being 
+#'   takes a contact matrix and visualises it, with the x and y axes being
 #'   different age groups.
-#' 
+#'
 #' @param matrix Square matrix with row and column names indicating the age
 #'   groups
 #' @return a ggplot visualisation of contact rates
 #' @examples
 #' \dontrun{
-#' 
-#' set.seed(2021-09-24)
+#'
+#' set.seed(2021 - 09 - 24)
 #' polymod_contact_data <- get_polymod_setting_data()
 #' polymod_survey_data <- get_polymod_population()
-#' 
+#'
 #' setting_models <- fit_setting_contacts(
 #'   contact_data_list = polymod_contact_data,
 #'   population = polymod_survey_data
 #' )
-#' 
+#'
 #' fairfield_age_pop <- abs_age_lga("Fairfield (C)")
-#' 
+#'
 #' fairfield_age_pop
-#' 
+#'
 #' synthetic_settings_5y_fairfield <- predict_setting_contacts(
 #'   population = fairfield_age_pop,
 #'   contact_model = setting_models,
 #'   age_breaks = c(seq(0, 85, by = 5), Inf)
 #' )
-#' 
-#' # Visualise the projected contact rates for "home" in the Fairfield LGA. The 
-#' # strong diagonal shows us that similar age groups typically have higher 
-#' # rates of home contact. We can also see parental links include middle-aged 
-#' # age groups having observable contact rates with younger age groups. 
-#' # For instance, ages between 25 and 45 have higher contact rates with 
-#' # newborns (0 to 5) and children (5 to 10), but older age groups, 
-#' # including those over 55, tend to have higher contact rates with age 
-#' # groups between 25 and 45, showing the interactions between parents and 
-#' # children. In addition to this, other patterns that indicates contact 
-#' # between children and their grandparents where higher contact rates between 
-#' # young children (years 0-5) and grandparents (age 55+) are present. 
-#' 
-#' 
+#'
+#' # Visualise the projected contact rates for "home" in the Fairfield LGA. The
[…]

### 2022-12-20 R/plot_setting_matrices.R

@@ -1,48 +1,47 @@
 #' Visualise predicted contact matrix for each setting
-#' 
+#'
 #' This is an extension of [plot_matrix()], which visualises the contact
 #'   matrix for each setting. It uses `patchwork` to combine all the matrices
 #'   together
-#' 
-#' @param matrices A list of square matrices, with row and column names 
+#'
+#' @param matrices A list of square matrices, with row and column names
 #'   indicating the age groups.
-#' @param title Title to give to plot setting matrices. Default value is: 
+#' @param title Title to give to plot setting matrices. Default value is:
 #'   "Setting-specific synthetic contact matrices (all polymod data)'"
 #' @return ggplot visualisation of contact rates for each setting
 #' @examples
 #' \dontrun{
-#' 
-#' set.seed(2021-09-24)
+#'
+#' set.seed(2021 - 09 - 24)
 #' polymod_contact_data <- get_polymod_setting_data()
 #' polymod_survey_data <- get_polymod_population()
-#' 
+#'
 #' setting_models <- fit_setting_contacts(
 #'   contact_data_list = polymod_contact_data,
 #'   population = polymod_survey_data
 #' )
-#' 
+#'
 #' fairfield_age_pop <- abs_age_lga("Fairfield (C)")
-#' 
+#'
 #' fairfield_age_pop
-#' 
+#'
 #' synthetic_settings_5y_fairfield <- predict_setting_contacts(
 #'   population = fairfield_age_pop,
 #'   contact_model = setting_models,
 #'   age_breaks = c(seq(0, 85, by = 5), Inf)
 #' )
-#' 
+#'
 #' plot_setting_matrix(synthetic_settings_5y_fairfield)
 #' }
 #' @noRd
 #' @note internal
 plot_setting_matrices <- function(matrices,
                                   title = "Setting-specific synthetic contact matrices") {
-  
   plot_home <- plot_matrix(matrices$home) + ggplot2::ggtitle("home")
-  plot_school <- plot_matrix(matrices$school) + ggplot2::ggtitle("school") 
+  plot_school <- plot_matrix(matrices$school) + ggplot2::ggtitle("school")
   plot_work <- plot_matrix(matrices$work) + ggplot2::ggtitle("work")
   plot_other <- plot_matrix(matrices$other) + ggplot2::ggtitle("other")
-    
+
   patchwork::wrap_plots(
     plot_home,
     plot_school,

### 2022-12-20 R/predict_contacts.R

@@ -1,67 +1,67 @@
 #' @title Predict contact rate between two age populations, given some model.
-#' 
-#' @description Predicts the expected contact rate over specified age breaks, 
-#'  given some model of contact rate and population age structure. 
-#'  This function is used internally in [predict_setting_contacts()], which 
-#'  performs this prediction across all settings (home, work, school, other), 
-#'  and optionally performs an adjustment for per capita household size. You 
-#'  can use `predict_contacts()` by itself, just be aware you will need to 
-#'  separately apply a per capita household size adjustment if required. See 
+#'
+#' @description Predicts the expected contact rate over specified age breaks,
+#'  given some model of contact rate and population age structure.
+#'  This function is used internally in [predict_setting_contacts()], which
+#'  performs this prediction across all settings (home, work, school, other),
+#'  and optionally performs an adjustment for per capita household size. You
+#'  can use `predict_contacts()` by itself, just be aware you will need to
+#'  separately apply a per capita household size adjustment if required. See
 #'  details below on `adjust_household_contact_matrix` for more information.
-#'    
-#' @details The population data is used to determine age range to predict 
-#'   contact rates, and removes ages with zero population, so we do not 
-#'   make predictions for ages with zero populations. Contact rates are 
-#'   predicted yearly between the age groups, using [predict_contacts_1y()], 
-#'   then aggregates these predicted contacts using 
-#'   [aggregate_predicted_contacts()], which aggregates the predictions back to 
-#'   the same resolution as the data, appropriately weighting the contact rate 
+#'
+#' @details The population data is used to determine age range to predict
+#'   contact rates, and removes ages with zero population, so we do not
+#'   make predictions for ages with zero populations. Contact rates are
+#'   predicted yearly between the age groups, using [predict_contacts_1y()],
+#'   then aggregates these predicted contacts using
+#'   [aggregate_predicted_contacts()], which aggregates the predictions back to
+#'   the same resolution as the data, appropriately weighting the contact rate
 #'   by the population.
-#'   
-#'   Regarding the `adjust_household_contact_matrix` function, we use 
+#'
+#'   Regarding the `adjust_household_contact_matrix` function, we use
 #'     Per-capita household size instead of mean household size.
-#'     Per-capita household size is different to mean household size, as the 
[…]

### 2022-12-20 data-raw/clean-household.R

@@ -41,10 +41,10 @@ abs_household_lga <- read_csv(file = here("data-raw/ABS_C16_T23_LGA_060920211607
       n_persons_usually_resident == "Eight or more persons" ~ "8+"
     )
   ) %>%
-  filter(household_composition == "Total Households") %>% 
-  select( - household_composition) %>% 
-  mutate(state = abbreviate_states(state))  %>% 
-  drop_na() %>% 
+  filter(household_composition == "Total Households") %>%
+  select(-household_composition) %>%
+  mutate(state = abbreviate_states(state)) %>%
+  drop_na() %>%
   rename(lga = lga_name) %>%
   # renaming LGAs according to abs_lga_lookup & abs_pop_age_lga_2020
   mutate(

### 2022-12-20 data-raw/clean-population-by-age-2016.R

@@ -36,7 +36,7 @@ abs_pop_age_lga_2016_raw <- file_path %>%
     state = `S/T name`,
     LGA_NAME19 = `LGA name`,
     LGA_CODE19 = `LGA code`
-  ) %>% 
+  ) %>%
   pivot_longer(
     cols = -c(state, LGA_NAME19, LGA_CODE19),
     names_to = "age",
@@ -53,25 +53,30 @@ abs_pop_age_lga_2016_raw <- file_path %>%
     lga_code = lga_code19,
     lga = lga_name19
   ) %>%
-  mutate(state = abbreviate_states(state)) %>% 
-  select(-lga_code) %>% 
-  rename(age_group = age) %>% 
+  mutate(state = abbreviate_states(state)) %>%
+  select(-lga_code) %>%
+  rename(age_group = age) %>%
   # replace emdash
   mutate(
-    age_group = str_replace_all(age_group,
-                                "–",
-                                "-"),
+    age_group = str_replace_all(
+      age_group,
+      "–",
+      "-"
+    ),
     age_group = factor(age_group,
-                       levels = str_sort(unique(age_group), numeric = TRUE))
-  ) %>% 
-  arrange(state,
-          age_group)
-  
+      levels = str_sort(unique(age_group), numeric = TRUE)
+    )
+  ) %>%
+  arrange(
+    state,
+    age_group
+  )
+
 # there's about 1% missing...
-abs_pop_age_lga_2016_raw %>% 
+abs_pop_age_lga_2016_raw %>%
   naniar::miss_var_summary()
 
-abs_pop_age_lga_2016 <- abs_pop_age_lga_2016_raw %>% 
+abs_pop_age_lga_2016 <- abs_pop_age_lga_2016_raw %>%
   drop_na()
 
 use_data(abs_pop_age_lga_2016, overwrite = TRUE)

### 2022-12-20 data-raw/clean-population-by-age-2020.R

@@ -49,29 +49,34 @@ abs_pop_age_lga_2020_raw <- file_path %>%
   rename(
     lga_code = lga_code19,
     lga = lga_name19
-  ) %>% 
-  mutate(state = abbreviate_states(state)) %>% 
-  select(-lga_code) %>% 
-  rename(age_group = age) %>% 
+  ) %>%
+  mutate(state = abbreviate_states(state)) %>%
+  select(-lga_code) %>%
+  rename(age_group = age) %>%
   # replace emdash
   mutate(
-    age_group = str_replace_all(age_group,
-                                "–",
-                                "-"),
+    age_group = str_replace_all(
+      age_group,
+      "–",
+      "-"
+    ),
     age_group = factor(age_group,
-                       levels = str_sort(unique(age_group), numeric = TRUE))
-  ) %>% 
-  arrange(state,
-          age_group)
+      levels = str_sort(unique(age_group), numeric = TRUE)
+    )
+  ) %>%
+  arrange(
+    state,
+    age_group
+  )
 
 # about 1% missing data for state, lga, and population
-abs_pop_age_lga_2020_raw %>% 
+abs_pop_age_lga_2020_raw %>%
   naniar::miss_var_summary()
 
-abs_pop_age_lga_2020_raw %>% 
+abs_pop_age_lga_2020_raw %>%
   naniar::gg_miss_var(facet = state)
 
-abs_pop_age_lga_2020 <- abs_pop_age_lga_2020_raw %>% 
+abs_pop_age_lga_2020 <- abs_pop_age_lga_2020_raw %>%
   drop_na()
 
 use_data(abs_pop_age_lga_2020, overwrite = TRUE)

### 2022-12-20 data-raw/clean-state-age-pop.R

@@ -27,25 +27,28 @@ abs_state_age <- read_excel(
   filter(
     age_group != "All ages",
     state != "Australia"
-  ) %>% 
-  mutate(state = abbreviate_states(state)) %>% 
+  ) %>%
+  mutate(state = abbreviate_states(state)) %>%
   relocate(
-    state, 
+    state,
     age_group,
     population
-  ) %>% 
+  ) %>%
   mutate(
     # replace emdash.
-    age_group = str_replace_all(age_group,
-                                "–",
-                                "-"),
-  age_group = case_when(
-    age_group == "100 and over" ~ "100+",
-    TRUE ~ age_group
-  ),
+    age_group = str_replace_all(
+      age_group,
+      "–",
+      "-"
+    ),
+    age_group = case_when(
+      age_group == "100 and over" ~ "100+",
+      TRUE ~ age_group
+    ),
     age_group = factor(age_group,
-                       levels = str_sort(unique(age_group), numeric = TRUE))
+      levels = str_sort(unique(age_group), numeric = TRUE)
     )
+  )
 
 abs_state_age
 

### 2022-12-20 data-raw/euclidean_join.R

@@ -7,28 +7,27 @@
 #' @return
 #' @author Nick Golding
 #' @export
-euclidean_join <- function (.data,
-                            legend,
-                            by = intersect(names(.data), names(legend))) {
+euclidean_join <- function(.data,
+                           legend,
+                           by = intersect(names(.data), names(legend))) {
   # Do Euclidean lookup from matrix pixels to legends
-  
+
   # get Euclidean distance matrix between data and legend
   distances <- rdist(
     .data[, by],
     legend[, by]
   )
-  
+
   # find the index to the nearest value in the legend
   row_idx <- apply(distances, 1, which.min)
-  
+
   # get the new columns from the legend
   by_col_idx <- match(by, names(legend))
   new_cols <- legend[, -by_col_idx]
-  
+
   # combine them
   bind_cols(
     .data,
     new_cols[row_idx, ]
   )
-  
 }

### 2022-12-20 tests/testthat/test-abs-age-lga.R

@@ -5,5 +5,5 @@ test_that("abs_age_lga() returns the right shape works", {
 test_that("abs_age_lga() returns the right shape errors", {
   expect_snapshot_error(
     abs_age_lga("Imaginary World")
-    )
+  )
 })

### 2022-12-20 tests/testthat/test-check-if-data-list.R

@@ -1,11 +1,11 @@
 test_that("check_if_list() returns error when argument class is not a list", {
-  set.seed(2021-10-4)
- polymod_setting_data <-  get_polymod_setting_data()
+  set.seed(2021 - 10 - 4)
+  polymod_setting_data <- get_polymod_setting_data()
   expect_snapshot_error(check_if_list(polymod_setting_data$home))
 })
 
 test_that("check_if_list() returns nothing when argument class is a list", {
-  set.seed(2021-10-4)
-  polymod_setting_data <-  get_polymod_setting_data()
+  set.seed(2021 - 10 - 4)
+  polymod_setting_data <- get_polymod_setting_data()
   expect_silent((check_if_list(polymod_setting_data)))
 })

### 2022-12-20 tests/testthat/test-get-polymod-population.R

@@ -1,17 +1,17 @@
 test_that("get_polymod_contact_data() works", {
   skip_on_ci()
-  set.seed(2021-10-4)
+  set.seed(2021 - 10 - 4)
   expect_snapshot_output(get_polymod_contact_data())
 })
 
 test_that("get_polymod_population() works", {
   skip_on_ci()
-  set.seed(2021-10-4)
+  set.seed(2021 - 10 - 4)
   expect_snapshot_output(get_polymod_population())
 })
 
 test_that("get_polymod_setting_data() works", {
   skip_on_ci()
-  set.seed(2021-10-4)
+  set.seed(2021 - 10 - 4)
   expect_snapshot_output(get_polymod_setting_data())
 })

### 2022-12-20 tests/testthat/test-per_capita_household_size.R

@@ -5,8 +5,10 @@ test_that("refactored code works", {
 })
 
 test_that("refactored code works with lga", {
-  expect_equal(abs_per_capita_household_size_lga(unique(abs_lga_lookup$lga)[1]),
-               get_per_capita_household_size(lga=unique(abs_lga_lookup$lga)[1]))
+  expect_equal(
+    abs_per_capita_household_size_lga(unique(abs_lga_lookup$lga)[1]),
+    get_per_capita_household_size(lga = unique(abs_lga_lookup$lga)[1])
+  )
 })
 
 

### 2022-12-22 R/apply_vaccination.R
some minor restructuring of the vignettes

@@ -73,6 +73,10 @@ apply_vaccination <- function(ngm,
                               coverage_col,
                               acquisition_col,
                               transmission_col) {
+  # NOTE
+  # `apply_vaccination` should accept an ngm class object otherwise
+  # give an error maybe?
+  # also should it be `vaccination_data` not `data`, so it is more descriptive?
   check_dimensions(ngm, data)
 
   transmission_reduction_matrix <- data %>%

### 2022-12-23 R/generate-ngm.R
getting generate_ngm S3 methods to work but the dimensions need to be the same as the length of age_breaks at the moment

@@ -4,7 +4,10 @@
 #'   another, creating generations of infected individuals. We can define a
 #'   matrix describing the number of newly infected individuals in given
 #'   categories, such as age, for consecutive generations. This matrix is
-#'   called a "next generation matrix" (NGM).
+#'   called a "next generation matrix" (NGM). We can generate an NGM from two
+#'   sources - a `conmat_population` object (such as the output from 
+#'   [abs_age_lga()]), or a `conmat_setting_prediction_matrix`, which is the
+#'   output from [extrapolate_polymod()] or [predict_setting_contacts()].
 #'
 #' @details The NGM can be used to calculate the expected number of secondary
 #'   infections in a given age group. Given certain age breaks, we compute the
@@ -20,13 +23,37 @@
 #'   the combination NGM. This ratio is then used to scale all the setting
 #'   specific NGMs.
 #'
-#' @param x data input - could be a `conmat_population` object or a `conmat_setting_preduction_matrix`.
+#' @param x data input - could be a `conmat_population` (such as the output from 
+#'   [abs_age_lga()]), or a `conmat_setting_prediction_matrix`, which is the
+#'   output from [extrapolate_polymod()] or [predict_setting_contacts()].
 #' @param age_breaks vector depicting age values with the highest age depicted
 #'   as `Inf`. For example, c(seq(0, 85, by = 5), Inf)
 #' @param R_target target reproduction number
-#' @param ... extra arguments
-#' @export
+#' @param ... extra arguments, currently not used
+#' @name generate_ngm
 #' @examples
+#' \dontrun{
+#'  perth <- abs_age_lga("Perth (C)")
+#'  perth_hh <- get_per_capita_household_size(lga = "Perth (C)")
+#'  
+#'  # you can also run this without `per_capita_household_size`
+#'  perth_ngm_lga <- generate_ngm(perth,
+#'                                age_breaks = c(seq(0, 75, by = 5), Inf),
+#'                                per_capita_household_size = perth_hh,
+#'                                R_target = 1.5)
+#'  
+#'                            
+#'  perth_contact <- extrapolate_polymod(
+#'    perth,
+#'    per_capita_household_size = perth_hh
+#'  )
+#'  
+#'  perth_ngm <- generate_ngm(perth_contact,
[…]

### 2023-01-11 R/generate-ngm.R
first initial commit of new transmission matrix - probably going to be overwritten by Michael

@@ -35,6 +35,13 @@
 #' @param age_breaks vector depicting age values with the highest age depicted
 #'   as `Inf`. For example, c(seq(0, 85, by = 5), Inf)
 #' @param R_target target reproduction number
+#' @param transmission_matrix default is NULL, which calculates the transmission
+#'   matrix using `get_setting_transmission_matrices(age_breaks)`. You can 
+#'   provide your own transmission matrix, but its rows and columns must match
+#'   the number of rows and columns, and must be a list of one matrix for each 
+#'   setting. See the output for `get_setting_transmission_matrices(age_breaks)`
+#'   to get a sense of the structure. See [get_setting_transmission_matrices()] 
+#'   for more detail.
 #' @param ... extra arguments, currently not used
 #' @name generate_ngm
 #' @examples
@@ -42,28 +49,45 @@
 #'  perth <- abs_age_lga("Perth (C)")
 #'  perth_hh <- get_per_capita_household_size(lga = "Perth (C)")
 #'  
+#'  age_breaks_0_80 <- c(seq(0, 80, by = 5), Inf)
 #'  # you can also run this without `per_capita_household_size`
 #'  perth_ngm_lga <- generate_ngm(perth,
-#'                                age_breaks = c(seq(0, 75, by = 5), Inf),
+#'                                age_breaks = age_breaks_0_80,
 #'                                per_capita_household_size = perth_hh,
 #'                                R_target = 1.5)
 #'  
 #'                            
-#'  perth_contact <- extrapolate_polymod(
+#'  perth_contact_0_80 <- extrapolate_polymod(
 #'    perth,
-#'    per_capita_household_size = perth_hh
+#'    per_capita_household_size = perth_hh,
+#'    age_breaks = age_breaks_0_80
 #'  )
 #'  
-#'  perth_ngm <- generate_ngm(perth_contact,
-#'                            age_breaks = c(seq(0, 75, by = 5), Inf),
+#'  perth_ngm <- generate_ngm(perth_contact_0_80,
+#'                            age_breaks = age_breaks_0_80,
 #'                            R_target = 1.5)
 #'                            
+#' # using our own transmission matrix
+#' new_transmission_matrix <- get_setting_transmission_matrices(
+#'   age_breaks = age_breaks_0_80,
+#'   # is normally 0.5
+#'   asymptomatic_relative_infectiousness = 0.75
+#' )
+#' 
[…]

### 2023-01-11 R/generate-ngm.R
minor restyle and add example of using your own transmission matrix

@@ -41,30 +41,52 @@
 #' \dontrun{
 #' perth <- abs_age_lga("Perth (C)")
 #' perth_hh <- get_per_capita_household_size(lga = "Perth (C)")
+#' 
+#' age_breaks_0_80_plus <- c(seq(0, 80, by = 5), Inf)
 #'
 #' # you can also run this without `per_capita_household_size`
-#' perth_ngm_lga <- generate_ngm(perth,
-#'   age_breaks = c(seq(0, 75, by = 5), Inf),
+#' perth_ngm_lga <- generate_ngm(
+#'   perth,
+#'   age_breaks = age_breaks_0_80_plus,
 #'   per_capita_household_size = perth_hh,
 #'   R_target = 1.5
 #' )
-#'
 #'
 #' perth_contact <- extrapolate_polymod(
 #'   perth,
 #'   per_capita_household_size = perth_hh
 #' )
 #'
-#' perth_ngm <- generate_ngm(perth_contact,
-#'   age_breaks = c(seq(0, 75, by = 5), Inf),
+#' perth_ngm <- generate_ngm(
+#'   perth_contact,
+#'   age_breaks = age_breaks_0_80_plus,
 #'   R_target = 1.5
 #' )
+#' 
+#' # using our own transmission matrix
+#' new_transmission_matrix <- get_setting_transmission_matrices(
+#'   age_breaks = age_breaks_0_80_plus,
+#'   # is normally 0.5
+#'   asymptomatic_relative_infectiousness = 0.75
+#' )
+#' 
+#' new_transmission_matrix
+#' 
+#' perth_ngm_0_80_new_tmat <- generate_ngm(
+#'   perth_contact,
+#'   age_breaks = age_breaks_0_80_plus,
+#'   R_target = 1.5,
+#'   setting_transmission_matrix = new_transmission_matrix
+#' )
+#' 
 #' }
 #' @export
-generate_ngm <- function(x,
-                         age_breaks,
-                         R_target,
-                         ...) {
+generate_ngm <- function(
+  x,
+  age_breaks,
+  R_target,
+  ...
+) {
   # detect if state_name or lga_name are used
   # then give an informative error that the user should use
   # `generate_ngm_oz`
@@ -85,14 +107,16 @@ generate_ngm <- function(x,
 #' }
 #' @rdname generate_ngm
 #' @export
-generate_ngm.conmat_setting_prediction_matrix <- function(x,
-                                                          age_breaks,
-                                                          R_target,
-                                                          per_capita_household_size = NULL,
[…]

### 2023-01-11 R/estimate_setting_contacts.R
style pkg

@@ -5,7 +5,7 @@
 #'   individuals in the survey), a representative population distribution for
 #'   the survey, and a set of age breaks at which to aggregate contacts, return
 #'   a set of predicted contact matrices for each setting, and for all combined.
-#'   Note that this function is parallelisable with `future`, and will be 
+#'   Note that this function is parallelisable with `future`, and will be
 #'   impacted by any `future` plans provided.
 #'
 #' @param contact_data_list list of data sets with information on the contacts

### 2023-01-11 R/generate-ngm.R

@@ -36,11 +36,11 @@
 #'   as `Inf`. For example, c(seq(0, 85, by = 5), Inf)
 #' @param R_target target reproduction number
 #' @param setting_transmission_matrix default is NULL, which calculates the transmission
-#'   matrix using `get_setting_transmission_matrices(age_breaks)`. You can 
+#'   matrix using `get_setting_transmission_matrices(age_breaks)`. You can
 #'   provide your own transmission matrix, but its rows and columns must match
-#'   the number of rows and columns, and must be a list of one matrix for each 
+#'   the number of rows and columns, and must be a list of one matrix for each
 #'   setting. See the output for `get_setting_transmission_matrices(age_breaks)`
-#'   to get a sense of the structure. See [get_setting_transmission_matrices()] 
+#'   to get a sense of the structure. See [get_setting_transmission_matrices()]
 #'   for more detail.
 #' @param ... extra arguments, currently not used
 #' @name generate_ngm
@@ -48,7 +48,7 @@
 #' \dontrun{
 #' perth <- abs_age_lga("Perth (C)")
 #' perth_hh <- get_per_capita_household_size(lga = "Perth (C)")
-#' 
+#'
 #' age_breaks_0_80_plus <- c(seq(0, 80, by = 5), Inf)
 #'
 #' # you can also run this without `per_capita_household_size`
@@ -69,32 +69,29 @@
 #'   age_breaks = age_breaks_0_80_plus,
 #'   R_target = 1.5
 #' )
-#' 
+#'
 #' # using our own transmission matrix
 #' new_transmission_matrix <- get_setting_transmission_matrices(
 #'   age_breaks = age_breaks_0_80_plus,
 #'   # is normally 0.5
 #'   asymptomatic_relative_infectiousness = 0.75
 #' )
-#' 
+#'
 #' new_transmission_matrix
-#' 
+#'
 #' perth_ngm_0_80_new_tmat <- generate_ngm(
 #'   perth_contact,
 #'   age_breaks = age_breaks_0_80_plus,
 #'   R_target = 1.5,
 #'   setting_transmission_matrix = new_transmission_matrix
 #' )
-#' 
 #' }
 #' @export
-generate_ngm <- function(
-  x,
-  age_breaks,
-  R_target,
-  setting_transmission_matrix,
-  ...
-) {
+generate_ngm <- function(x,
+                         age_breaks,
+                         R_target,
+                         setting_transmission_matrix,
+                         ...) {
[…]

### 2023-01-17 R/get_setting_transmission_matrices.R
add `autoplot` methods for ngm, vaccination, and transmission probability and upate snapshots, fix a bunch of spelling mistakes

@@ -22,7 +22,7 @@
 #' transmissibility in work and other settings due to hygiene behaviour; and
 #' estimates of the relative transmissibility in household vs non-household
 #' settings - scaled linearly for non-household transmission and binomially for
-#' household transmission (so that onward onfections do not to exceed the number
+#' household transmission (so that onward infections do not to exceed the number
 #' of other household members).
 #'
 #' When using this data, ensure that you cite this package, and the original

### 2023-01-17 R/autoplot.R
This commit:
* simplifies names given to objects when using `abs_age_lga`.
* passes `symmetrical` argument to `estimate_setting_contacts`
* gives more detail on fitting a model outside of using `extrapolate_polymod`
* give `estimate_setting_contacts` some more example of using fairfield data

@@ -19,13 +19,13 @@
 #'     population = polymod_survey_data
 #'   )
 #'
-#'   fairfield_age_pop <- abs_age_lga("Fairfield (C)")
+#'   fairfield <- abs_age_lga("Fairfield (C)")
 #'
 #'   fairfield_hh_size <-
 #'     get_per_capita_household_size(lga = "Fairfield (C)")
 #'
 #'   synthetic_settings_5y_fairfield_hh <- predict_setting_contacts(
-#'     population = fairfield_age_pop,
+#'     population = fairfield,
 #'     contact_model = setting_models,
 #'     age_breaks = c(seq(0, 85, by = 5), Inf),
 #'     per_capita_household_size = fairfield_hh_size
@@ -47,8 +47,8 @@
 #' }
 #' @export
 autoplot.conmat_age_matrix <- function(object,
-                                              ...,
-                                              title = "Contact Matrices") {
+                                       ...,
+                                       title = "Contact Matrices") {
   plot_matrix(object) +
     ggplot2::ggtitle(title)
 }

### 2023-01-19 README.Rmd

@@
 ```{r fairfield}
-fairfield_age_pop <- abs_age_lga("Fairfield (C)")
-fairfield_age_pop
+fairfield <- abs_age_lga("Fairfield (C)")
+fairfield
 ```
@@
   model = contact_model,
-  population = fairfield_age_pop,
+  population = fairfield,
   age_breaks = c(seq(0, 85, by = 5), Inf)

### 2023-01-20 R/extrapolate_polymod.R
change `get_per_capita_household_size` to `get_abs_per_capita_household_size`

@@ -21,7 +21,7 @@
 #'   adjusts the household contact matrix by some per capita household size.
 #'   To set it, provide a single number, the per capita household size. More
 #'   information is provided below in Details. See
-#'   [get_per_capita_household_size()] function for a helper for Australian
+#'   [get_abs_per_capita_household_size()] function for a helper for Australian
 #'    data with a workflow on how to get this number.
 #' @return Returns setting-specific and combined contact matrices for the
 #'   desired ages.

### 2023-01-20 tests/testthat/test-per_capita_household_size.R

@@ -1,13 +1,13 @@
 
 
 test_that("refactored code works", {
-  expect_equal(abs_per_capita_household_size_state("NSW"), get_per_capita_household_size("NSW"))
+  expect_equal(abs_per_capita_household_size_state("NSW"), get_abs_per_capita_household_size("NSW"))
 })
 
 test_that("refactored code works with lga", {
   expect_equal(
     abs_per_capita_household_size_lga(unique(abs_lga_lookup$lga)[1]),
-    get_per_capita_household_size(lga = unique(abs_lga_lookup$lga)[1])
+    get_abs_per_capita_household_size(lga = unique(abs_lga_lookup$lga)[1])
   )
 })
 

### 2023-01-23 R/setting-prediction-matrix.R
adding some more constructors to facilitate creating setting prediction and transmission probability matrices

@@ -1,0 +1,56 @@
+new_setting_prediction_matrix <- function(list_matrix,
+                                          age_breaks = NULL) {
+  structure(
+    list_matrix,
+    age_breaks = age_breaks,
+    class = c("conmat_setting_prediction_matrix", class(list_matrix))
+  )
+}
+
+#' Create a setting prediction matrix
+#'
+#' Helper function to create your own setting prediction matrix, which you
+#'   may want to use in `generate_ngm`, or `autoplot`. This class is the
+#'   output of functions like `extrapolate_polymod`, and
+#'   `predict_setting_contacts`. We recommend using this function is only for
+#'   advanced users, who are creating their own setting prediction matrix.
+#'
+#' @param ... list of matrices
+#' @param age_breaks age breaks - numeric
+#'
+#' @return setting prediction matrix
+#'
+#' @examples
+#'
+#' age_breaks_0_80_plus <- c(seq(0, 80, by = 10), Inf)
+#' one_by_nine <- matrix(1, nrow = 9, ncol = 9)
+#'
+#' x_example <- setting_prediction_matrix(
+#'   home = one_by_nine,
+#'   work = one_by_nine,
+#'   age_breaks = age_breaks_0_80_plus
+#' )
+#'
+#' x_example <- setting_prediction_matrix(
+#'   one_by_nine,
+#'   one_by_nine,
+#'   age_breaks = age_breaks_0_80_plus
+#' )
+#'
+#' x_example
+#'
+#' @export
+setting_prediction_matrix <- function(...,
+                                      age_breaks) {
+  list_matrix <- prepare_list_matrix(...)
+
+  setting_pred_matrix <- set_age_breaks_matrices(
+    list_matrix,
+    age_breaks
+  )
+
+  new_setting_prediction_matrix(
+    list_matrix = setting_pred_matrix,
+    age_breaks = group_age_breaks(age_breaks)
+  )
+}

### 2023-01-23 R/setting-transmission-matrix.R

@@ -1,0 +1,57 @@
+
+new_transmission_probability_matrix <- function(list_matrix,
+                                                age_breaks = NULL) {
+  structure(
+    list_matrix,
+    age_breaks = age_breaks,
+    class = c("transmission_probability_matrix", class(list_matrix))
+  )
+}
+
+#' Create a setting transmission matrix
+#'
+#' Helper function to create your own setting transmission matrix, which you
+#'   may want to use in ... or `autoplot`. This class is the
+#'   output of functions like `...`, and ... . We recommend using this
+#'   function is only for advanced users, who are creating their own
+#'   transmission probability matrix.
+#'
+#' @param ... list of matrices
+#' @param age_breaks age breaks - numeric
+#'
+#' @return transmission probability matrix
+#'
+#' @examples
+#'
+#' age_breaks_0_80_plus <- c(seq(0, 80, by = 10), Inf)
+#' one_05 <- matrix(0.05, nrow = 9, ncol = 9)
+#'
+#' x_example <- transmission_probability_matrix(
+#'   home = one_05,
+#'   work = one_05,
+#'   age_breaks = age_breaks_0_80_plus
+#' )
+#'
+#' x_example <- transmission_probability_matrix(
+#'   one_05,
+#'   one_05,
+#'   age_breaks = age_breaks_0_80_plus
+#' )
+#'
+#' x_example
+#'
+#' @export
+transmission_probability_matrix <- function(...,
+                                            age_breaks) {
+  list_matrix <- prepare_list_matrix(...)
+
+  setting_transmission_mat <- set_age_breaks_matrices(
+    list_matrix,
+    age_breaks
+  )
+
+  new_transmission_probability_matrix(
+    list_matrix = setting_transmission_mat,
+    age_breaks = group_age_breaks(age_breaks)
+  )
+}

### 2023-01-23 R/utils.R

@@ -243,3 +243,104 @@ print.setting_data <- function(x, ...) {
     object_class = "data.frame"
   )
 }
+
+group_age_breaks <- function(x, pad_inf = TRUE) {
+  # don't add extra Inf values
+  if (any(is.infinite(x))) {
+    pad_inf <- FALSE
+  }
+  pad_value <- ifelse(pad_inf, Inf, NA)
+  from <- stats::na.omit(dplyr::lag(x))
+  to <- stats::na.omit(dplyr::lead(x))
+
+  if (pad_inf) {
+    last_to <- to[length(to)]
+    from <- c(from, last_to)
+    to <- c(to, Inf)
+  }
+
+  glue::glue("[{from},{to})")
+}
+
+ungroup_age_breaks <- function(x) {
+  strsplit(
+    x = x,
+    # remove , and ) and [
+    split = ",|\\)|\\["
+  ) %>%
+    unlist() %>%
+    as.numeric() %>%
+    na.omit() %>%
+    unique() %>%
+    sort()
+}
+#
+# group_age_breaks(1:10, pad_inf = FALSE)
+# group_age_breaks(1:10, pad_inf = FALSE) %>% ungroup_age_breaks()
+# group_age_breaks(1:10, pad_inf = TRUE)
+# group_age_breaks(1:10, pad_inf = TRUE) %>% ungroup_age_breaks()
+#
+# group_age_breaks(c(1:10, Inf), pad_inf = TRUE)
+# group_age_breaks(c(1:10, Inf), pad_inf = TRUE) %>% ungroup_age_breaks()
+#
+# group_age_breaks(c(1:10, Inf), pad_inf = FALSE)
+# group_age_breaks(c(1:10, Inf), pad_inf = FALSE) %>% ungroup_age_breaks()
+#
+# group_age_breaks(age_breaks_0_80_plus)
+# group_age_breaks(1:10, pad_inf = FALSE)
+# group_age_breaks(1:9, pad_inf = FALSE)
+# group_age_breaks(1:8, pad_inf = FALSE)
+# group_age_breaks(1:10)
+# group_age_breaks(1:9)
+# group_age_breaks(1:8)
+
+all_matrix <- function(x) {
+  all(vapply(
+    X = x,
+    inherits,
+    what = "matrix",
+    FUN.VALUE = logical(1)
+  ))
+}
+
+name_list <- function(list) {
+  n_list <- length(list)
+  names(list) <- english::english(seq_len(n_list))
+}
+
+
[…]

### 2023-02-17 R/conmat-population.R
:wrench: :dizzy: :wrench:

@@ -68,10 +68,23 @@ as_conmat_population.default <- function(data, ...) {
         a {.cls conmat_population} object.")
 }
 
-#' @param age age column - numeric
-#' @param population population column - numeric
+#' @param age age column - an unquoted variable of numeric integer ages
+#' @param population population column - an unquoted variable, numeric value
 #' @rdname as_conmat_population
 #' @export
+#' @examples
+#' some_age_pop <- data.frame(
+#'   age = 1:10,
+#'   pop = 101:110
+#' )
+#'
+#' some_age_pop
+#'
+#' as_conmat_population(
+#'   some_age_pop,
+#'   age = age,
+#'   population = pop
+#' )
 as_conmat_population.data.frame <- function(data, age, population, ...) {
   # strip any existing classes
   data <- as.data.frame(data)

### 2023-02-17 tests/testthat/test-lga_household_works.R

@@ -8,15 +8,6 @@ test_that("get_abs_per_capita_household_size errors for some lgas", {
     .f = ~ get_abs_per_capita_household_size(lga = .x)
   ))
 })
-safe_get_abs_per_capita_household_size <- safely(get_abs_per_capita_household_size)
-
-household_per_capita_runs <- map(
-  .x = unique(abs_household_lga$lga),
-  .f = ~ safe_get_abs_per_capita_household_size(lga = .x)
-)
-
-# t_household_per_capita_runs <- transpose(household_per_capita_runs)
-# compact(t_household_per_capita_runs$error)
 
 test_that("check_lga_name errors for some lgas", {
   skip_on_ci()
@@ -26,12 +17,29 @@ test_that("check_lga_name errors for some lgas", {
   ))
 })
 
-safe_check_lga_name <- safely(check_lga_name)
+# safe_get_abs_per_capita_household_size <- safely(get_abs_per_capita_household_size)
+#
+# household_per_capita_runs <- map(
+#   .x = unique(abs_household_lga$lga),
+#   .f = ~ safe_get_abs_per_capita_household_size(lga = .x)
+# )
 
-check_lga_name_runs <- map(
-  .x = unique(abs_household_lga$lga),
-  .f = ~ safe_check_lga_name(lga = .x)
-)
+# t_household_per_capita_runs <- transpose(household_per_capita_runs)
+# compact(t_household_per_capita_runs$error)
 
-# t_check_lga_name_runs <- transpose(check_lga_name_runs)
-# compact(t_check_lga_name_runs$error)
+
+# thinking about which ones error?
+# safe_check_lga_name <- safely(check_lga_name)
+#
+# check_lga_name_runs <- map(
+#   .x = unique(abs_household_lga$lga),
+#   .f = ~ safe_check_lga_name(lga = .x)
+# )
+#
+# transpose_errors <- transpose(check_lga_name_runs)
+#
+# which_errors <- which(map_lgl(
+#   transpose_errors$error,
+#   \(x) !is.null(x)
+# )
+# )

### 2023-04-05 R/fit_single_contact_model.R
first pass at working on #151

@@ -130,7 +130,6 @@ fit_single_contact_model <- function(contact_data,
   # programatically add the offset term to the formula, so the model defines
   # information about the setting, without us having to pass it through to the
   # prediction data
-
   if (symmetrical) {
     formula_no_offset <- contacts ~
       # Prem method did a post-hoc smoothing

### 2024-01-11 paper/paper.Rmd

---
title: 'conmat: generate synthetic contact matrices for a given age population'
authors:
- affiliation: 1
  name: Nicholas Tierney
  orcid: 0000-0003-1460-8722
- affiliation: 1,2
  name: Nick Golding
  orcid: 
- affiliation: 1,3
  name: Aarathy Babu
  orcid: 
- affiliation: 4
  name: Michael Lydeamore
  orcid: 
date: "14 April 2023"
output:
  html_document:
    keep_md: yes
  pdf_document: default
bibliography: paper.bib
tags:
- epidemiology
- R
- infectious disease
affiliations:
- index: 1
  name: Telethon Kids Institute
- index: 2
  name: Curtin University
- index: 3
  name: 
- index: 4
  name: Monash University
---

# Summary

Epidemiologists and public policy makers need to understand the spread of infectious diseases in a population. Knowing which groups are most vulnerable and how disease spread will unfold helps to make proactive decisions that benefit the most people.  Diseases like influenza and coronavirus spread via human-to-human, "social contact".  If we can measure the amount of social contact, we can use this to understand how diseases spread.

We can measure social contact through social contact surveys, where people  describe the number and type of social contact they have. These surveys provide the empirical estimates of the number of social contacts from one age group to another, as well as the setting of contact. For example, homes have higher contact with 25-50 year olds with 0-15 year olds, workplaces have high contact within 25-60 year olds.

These surveys exist for a variety of countries, for example, Mossong et al., the "POLYMOD" study, covered 8 European countries: Belgium, Germany, Finland, Great Britain, Italy, Luxembourg, The Netherlands and Poland. However, what do we do when we want to look at contact rates in different countries that haven’t been measured? We can use this existing data to help us project to countries or places that do not have empirical survey data. These are called "synthetic contact matrices". A very popular approach by Prem et al projected from the POLYMOD study to 177 countries, and provided contact matrices at "urban" and "rural" levels for each country.

However not all countries were included in this list from Prem et al, and for some analyses these synthetic contact matrices were at a large area, such as "urban" or "rural" for a given country. We needed to make predictions at finer grained regions, were required. It was challenging to apply the methodology used by Prem et al, as while their analysis code was provided, it was not designed for reuse. We needed to create contact matrices based on existing studies like POLYMOD but projected to the age population in a given local government area in Australia.

Conmat was created to fill a specific need for creating synthetic contact matrices for specific local government areas for Australia, for work commissioned by the Australian government. We created methods and software to facilitate the following:

- Input: age and population data, and Output: synthetic contact matrix
- Create next generation matrices (NGMs)
- Apply vaccination reduction to NGMs
- Use NGMs in disease modelling
- Provide tidy Australian survey data from the Australian Bureau of Statistics for use.

# Example

As an example, let us generate a contact matrix for a local area using POLYMOD data.

Suppose we want to get a contact matrix for a given region in Australia, let's say the city of Perth. We can get that from a helper function, `abs_age_lga`.

```{r}
perth <- abs_age_lga("Perth (C)")
perth
```

We can get a contact matrix made for `perth` using the `extrapolate_polymod` function:

```{r}
perth_contact <- extrapolate_polymod(population = perth)
perth_contact
```

We can plot this with `autoplot`

```{r}
autoplot(perth_contact)
```

# Implementation

Conmat was built to predict at four settings: work, school, home, and other. The model is built to predict four separate models, one for each setting.
The model is a poisson generalised additive model (gam), predicting the count of contacts, with an offset of the log of participants. There are six terms to explain six key features of the relationship between ages, and optional terms for attendance at school or work, depending on which setting the model is predicting to.

The six key features of the relationship are shown in the figure below

```{r}
# use DHARMA to show a partial dep plot of the six main terms
```

## Model interfaces

We provide multiple levels for the user to interact with for model fitting, further detail can be seen at: https://njtierney.github.io/conmat/dev/

* `fit_single_contact_model()`
    * Using contact survey data to fit a GAM model, adding provided target population information to provide population size information. Recommended for when you want to fit to just a single setting, for which you might want to provide your own contact survey data.

* `predict_contacts()`

    * This takes a fitted model from `fit_single_contact_model`, and then predicts to a provided population

* `fit_setting_contacts()`
    * Fits the `fit_single_contact_model()` to each setting. Recommended for when you have multiple settings to fit. Returns a list of fitted models.

* `predict_setting_contacts()`
    * Takes a list of fitted models from `fit_setting_contacts()` and predicts to a given population for each setting.

* `estimate_setting_contacts()`
    * A convenience function that fits multiple models, one for each setting. This means fitting `fit_setting_contacts()` and then `predict_setting_contacts()`. Recommended for when you have multiple settings to fit and want to predict to a given population as well.

* `extrapolate_polymod()`
    * Takes population information and projects pre-fit model from POLYMOD - used for speed when you know you want to take an already fit model from POLYMOD and just fit it to your provided population.

# Future Work

* Create a contact matrix using a custom contact survey from another source, such as the `socialmixr` R package.
* Predict to any age brackets - such as monthly ages, for example, 1, 3, 6, month year old infants
* Add ability to fit multiple contact surveys at once, e.g., POLYMOD and another dataset
* Add ability to include known household age distributions as offsets in the 'home' setting model, in place of the whole population distribution. So compute household age matrices (like age-structured contact matrices, but for household members instead of contacts) from Polymod data. If we compute a different one for each household size, in the Polymod data (probably estimated with another GAM, to make best use of the limited data) we might be able to extrapolate household age matrices to new countries based on the distribution of household sizes.
* Add methods for including household size distributions
* Add uncertainty to estimates
* Move Australian centric data into its own package
* Add documentation on specifying your own GAM model and using this workflow

# References

- Prem 2017: https://journals.plos.org/ploscompbiol/article?id=10.1371/journal.pcbi.1005697
- Prem 2021: https://journals.plos.org/ploscompbiol/article?id=10.1371/journal.pcbi.1009098
- Mossonget al 2007: https://journals.plos.org/plosmedicine/article?id=10.1371/journal.pmed.0050074

### 2024-05-30 paper/paper.Rmd
Added ORCID numbers

@@
   name: Nick Golding
-  orcid: 
+  orcid: 0000-0001-8916-5570
 - affiliation: 1,3
@@
   name: Michael Lydeamore
-  orcid: 
-date: "14 April 2023"
+  orcid: 0000-0001-6515-827X
+- affiliation: 1,3
+  name: Chitra Saraswati
+  orcid: 0000-0002-8159-0414
+date: "03 May 2024"
 output:
@@
   pdf_document: default
-bibliography: paper.bib
+bibliography: references.bib
 tags:
@@
 
+```{r}
+#| label: setup
+#| echo: false
+#| message: false
+#| warning: false
+#| comment: false
+knitr::opts_chunk$set(comment = "#>",
+                      echo = TRUE,
+                      out.width = "95%",
+                      retina = 3,
+                      fig.height = 4,
+                      fig.align = "center",
+                      dpi = 300,
+                      dev = "png")
+options(tinytex.clean = FALSE)
+```
+
 # Summary
@@
 Epidemiologists and public policy makers need to understand the spread of infectious diseases in a population.
-Knowing which groups are most vulnerable and how disease spread will unfold helps to make proactive decisions that benefit the most people.
+Knowing which groups are most vulnerable, and how disease spread will unfold facilitates public health decision-making.
 Diseases like influenza and coronavirus spread via human-to-human, "social contact".
@@
 We can measure social contact through social contact surveys, where people  describe the number and type of social contact they have.
-These surveys provide the empirical estimates of the number of social contacts from one age group to another, as well as the setting of contact.
-For example, homes have higher contact with 25-50 year olds with 0-15 year olds, workplaces have high contact within 25-60 year olds.
+These surveys provide an empirical estimate of the number of social contacts from one age group to another, as well as the setting of contact.
+For example, we might learn from a contact survey that homes have higher contact with 25-50 year olds and with 0-15 year olds, whereas workplaces might have high contact within 25-60 year olds.
 
-These surveys exist for a variety of countries, for example, Mossong et al., the "POLYMOD" study, covered 8 European countries: Belgium, Germany, Finland, Great Britain, Italy, Luxembourg, The Netherlands and Poland.
+These surveys exist for a variety of countries, for example, @mossong2008 the "POLYMOD" study, covered 8 European countries: Belgium, Germany, Finland, Great Britain, Italy, Luxembourg, The Netherlands and Poland [@mossong2008].
 However, what do we do when we want to look at contact rates in different countries that haven’t been measured?
@@
 These are called "synthetic contact matrices".
-A very popular approach by Prem et al projected from the POLYMOD study to 177 countries, and provided contact matrices at "urban" and "rural" levels for each country.
+A very popular approach by Prem et al projected from the POLYMOD study to 152 countries [@prem2017].
+This which was later updated to include contact matrices for 177 countries at "urban" and "rural" levels for each country [@prem2021].
 
-However not all countries were included in this list from Prem et al, and for some analyses these synthetic contact matrices were at a large area, such as "urban" or "rural" for a given country.
-We needed to make predictions at finer grained regions, were required.
+However not all countries were included in this list from @prem2021, and for some analyses these synthetic contact matrices were at a large area, such as "urban" or "rural" for a given country.
+One limitation of this is that the predictions were not provided at smaller grained regons.
+This might be important, if for example, a public health group needed to make predictions for specific areas.
 It was challenging to apply the methodology used by Prem et al, as while their analysis code was provided, it was not designed for reuse.
-We needed to create contact matrices based on existing studies like POLYMOD but projected to the age population in a given local government area in Australia.
 
-Conmat was created to fill a specific need for creating synthetic contact matrices for specific local government areas for Australia, for work commissioned by the Australian government.
+The `conmat` package was created to fill a specific need for creating synthetic contact matrices for specific local government areas for Australia, for work commissioned by the Australian government.
 We created methods and software to facilitate the following:
@@
 ```{r}
+#| label: load-conmat
+library(conmat)
 perth <- abs_age_lga("Perth (C)")
@@
 ```{r}
+#| label: extrapolate-polymod
+#| echo: true
 perth_contact <- extrapolate_polymod(population = perth)
@@
 ```{r}
+#| label: autoplot-contacts
 autoplot(perth_contact)
@@
 
-We provide multiple levels for the user to interact with for model fitting, further detail can be seen at: https://njtierney.github.io/conmat/dev/
+We provide multiple levels for the user to interact with for model fitting, further detail can be seen at: https://idem-lab.github.io/conmat/dev/
 
@@
 * Add ability to include known household age distributions as offsets in the 'home' setting model, in place of the whole population distribution.
-So compute household age matrices (like age-structured contact matrices, but for household members instead of contacts) from Polymod data.
-If we compute a different one for each household size, in the Polymod data (probably estimated with another GAM, to make best use of the limited data) we might be able to extrapolate household age matrices to new countries based on the distribution of household sizes.
+So compute household age matrices (like age-structured contact matrices, but for household members instead of contacts) from POLYMOD data.
+If we compute a different one for each household size, in the POLYMOD data (probably estimated with another GAM, to make best use of the limited data) we might be able to extrapolate household age matrices to new countries based on the distribution of household sizes.
 * Add methods for including household size distributions
@@
 # References
-
-- Prem 2017: https://journals.plos.org/ploscompbiol/article?id=10.1371/journal.pcbi.1005697
-- Prem 2021: https://journals.plos.org/ploscompbiol/article?id=10.1371/journal.pcbi.1009098
-- Mossonget al 2007: https://journals.plos.org/plosmedicine/article?id=10.1371/journal.pmed.0050074

### 2024-06-10 paper/paper.Rmd
Partial dependency plots, test

@@
 
-```{r}
+```{r Document Setup}
 #| label: setup
@@
 
-```{r}
+```{r load conmat}
 #| label: load-conmat
@@
 
-```{r}
+```{r extrapolate polymod}
 #| label: extrapolate-polymod
@@
 
-```{r}
+```{r autoplot contacts}
 #| label: autoplot-contacts
@@
 
-The six key features of the relationship are shown in the figure below
+The six terms are
+
+The six key features of the relationship are shown in the figure below.
 
@@
 ```
+
+[#TODO notes-to-self: the model structure wasn't generated through any particularly robust process, it was just coming up with structures that looked mildly appropriate for our use case. ]
 

### 2024-06-13 paper/paper.Rmd
Improved draft

@@
 
-As an example, let us generate a contact matrix for a local area using POLYMOD data.
+As an example, let us generate a contact matrix for a local area using a model fitted from the POLYMOD data.
 
-Suppose we want to get a contact matrix for a given region in Australia, let's say the city of Perth. We can get that from a helper function, `abs_age_lga`.
+Suppose we want to generate a contact matrix for the City of Perth in Australia. We can get the population data for Perth from the helper function `abs_age_lga`:
 
@@
 
-We can get a contact matrix made for `perth` using the `extrapolate_polymod` function:
+We can generate a contact matrix for `perth` using the `extrapolate_polymod` function, where the contact matrix is generated using a model fitted from the POLYMOD data.
 
@@
 
-We can plot this with `autoplot`
+We can plot the resulting contact matrix with `autoplot`:
 
@@
 Conmat was built to predict at four settings: work, school, home, and other. The model is built to predict four separate models, one for each setting.
-The model is a poisson generalised additive model (gam), predicting the count of contacts, with an offset of the log of participants.
+The model is a Poisson generalised additive model (GAM), predicting the count of contacts, with an offset of the log of participants.
 There are six terms to explain six key features of the relationship between ages, and optional terms for attendance at school or work, depending on which setting the model is predicting to.

### 2024-06-13 paper/paper.Rmd
Improved example section

@@
 ---
-title: 'conmat: generate synthetic contact matrices for a given age population'
+title: 'conmat: generate synthetic contact matrices for a given age-stratified population'
 authors:
@@
 
-As an example, let us generate a contact matrix for a local area using a model fitted from the POLYMOD data.
+As an example, let us generate a contact matrix for a local government area within Australia, using a model fitted from the POLYMOD data.
 
-Suppose we want to generate a contact matrix for the City of Perth in Australia. We can get the population data for Perth from the helper function `abs_age_lga`:
+Suppose we want to generate a contact matrix for the City of Perth. We can get the age-stratified population data for Perth from the helper function `abs_age_lga`:
 
@@
 
-We can plot the resulting contact matrix with `autoplot`:
+We can plot the resulting contact matrix for Perth with `autoplot`:
 

### 2024-06-13 paper/paper.Rmd
Updated implementation section

@@
 
-Conmat was built to predict at four settings: work, school, home, and other. The model is built to predict four separate models, one for each setting.
+`conmat` was built to predict at four settings: work, school, home, and other. 
+The model is built to predict four separate models, one for each setting. [ #TODO a better way of saying the sentence prior? Predict four separate matrices?]
 The model is a Poisson generalised additive model (GAM), predicting the count of contacts, with an offset of the log of participants.
@@
 
-[#TODO notes-to-self: the model structure wasn't generated through any particularly robust process, it was just coming up with structures that looked mildly appropriate for our use case. ]
+Each cell in the resulting contact matrix, indexed *i*, *j*, is the predicted number of people in age group *j* that a single individual in age group *i* will have contact with per day.
+If you sum across all the *j* age groups for each *i* age group, you get the predicted total number of contacts per day for each individual of age group *i*.
+[ #TODO expected, predicted, or average?]
+
+[ #TODO notes-to-self: the model structure wasn't generated through any particularly robust process, it was just coming up with structures that looked mildly appropriate for our use case.
 

### 2024-06-13 paper/paper.Rmd
Updated paper

@@
 
-Epidemiologists and public policy makers need to understand the spread of infectious diseases in a population.
-Knowing which groups are most vulnerable, and how disease spread will unfold facilitates public health decision-making.
-Diseases like influenza and coronavirus spread via human-to-human, "social contact".
-If we can measure the amount of social contact, we can use this to understand how diseases spread.
+Epidemiologists and public policy makers need to understand the dynamics of infectious disease transmission in a population.
+Identifying vulnerable groups and predicting disease transmission dynamics are essential for informed public health decision-making.
+Infectious diseases such as influenza and coronavirus spread through human-to-human interactions, or in other words, "social contact".
+Quantifying social contact and its patterns can provide critical insights into how diseases spread.
 
 We can measure social contact through social contact surveys, where people  describe the number and type of social contact they have.
-These surveys provide an empirical estimate of the number of social contacts from one age group to another, as well as the setting of contact.
-For example, we might learn from a contact survey that homes have higher contact with 25-50 year olds and with 0-15 year olds, whereas workplaces might have high contact within 25-60 year olds.
+These surveys provide an empirical estimate of the number of social contacts from one age group to another and the setting of contact.
+For example, we might learn from a contact survey that homes have higher contact between 25-50 year olds and 0-15 year olds, whereas workplaces might have high contact within 25-60 year olds.
 

### 2024-06-20 paper/paper.Rmd
Updated paper introduction

@@
 
-```{r Document Setup}
+```{r setup}
 #| label: setup
@@
 
-Epidemiologists and public policy makers need to understand the dynamics of infectious disease transmission in a population.
-Identifying vulnerable groups and predicting disease transmission dynamics are essential for informed public health decision-making.
+#TODO - A better first sentence that encapsulates conmat use? 
+Understanding the dynamics of infectious disease transmission in a population is an important task (?) for epidemiologists and public policy makers.
+Identifying vulnerable groups and predicting disease transmission (?)dynamics are essential for informed public health decision-making.
 Infectious diseases such as influenza and coronavirus spread through human-to-human interactions, or in other words, "social contact".
@@
 We can measure social contact through social contact surveys, where people describe the number and type of social contact they have.
-These surveys provide an empirical estimate of the number of social contacts from one age group to another and the setting of contact.
+These surveys provide (?) a measure of contact rates: an empirical estimate of the number of social contacts from one age group to another and the setting of contact.
 For example, we might learn from a contact survey that homes have higher contact between 25-50 year olds and 0-15 year olds, whereas workplaces might have high contact within 25-60 year olds.
 
-These surveys exist for a variety of countries, for example, @mossong2008 the "POLYMOD" study, covered 8 European countries: Belgium, Germany, Finland, Great Britain, Italy, Luxembourg, The Netherlands and Poland [@mossong2008].
-However, what do we do when we want to look at contact rates in different countries that haven’t been measured?
+These social contact surveys exist for a few countries.
+As an example, @mossong2008 the "POLYMOD" study covered 8 European countries: Belgium, Germany, Finland, Great Britain, Italy, Luxembourg, The Netherlands, and Poland [@mossong2008].
+However, what do we do when we want to (?)look at/estimate contact rates in different countries that have not been measured?
 We can use this existing data to help us project to countries or places that do not have empirical survey data.
@@
 
-```{r load conmat}
+```{r}
 #| label: load-conmat
@@
 
-```{r extrapolate polymod}
+```{r}
 #| label: extrapolate-polymod
@@
 
-```{r autoplot contacts}
+```{r}
 #| label: autoplot-contacts
@@
 [ #TODO notes-to-self: the model structure wasn't generated through any particularly robust process, it was just coming up with structures that looked mildly appropriate for our use case.
+
+The results are surveys that can be found in the syncomat package, which can be seen at: https://idem-lab
 

### 2024-06-20 paper/paper.Rmd
Updated paper intro

@@
 These social contact surveys exist for a few countries.
-As an example, @mossong2008 the "POLYMOD" study covered 8 European countries: Belgium, Germany, Finland, Great Britain, Italy, Luxembourg, The Netherlands, and Poland [@mossong2008].
-However, what do we do when we want to (?)look at/estimate contact rates in different countries that have not been measured?
+As an example, the "POLYMOD" study by @mossong2008 covered 8 European countries: Belgium, Germany, Finland, Great Britain, Italy, Luxembourg, The Netherlands, and Poland [@mossong2008].
+However, what do we do when we want to (?)look at/estimate contact rates in other countries that have not been measured?
 We can use this existing data to help us project to countries or places that do not have empirical survey data.
 These are called "synthetic contact matrices".
-A very popular approach by Prem et al projected from the POLYMOD study to 152 countries [@prem2017].
-This which was later updated to include contact matrices for 177 countries at "urban" and "rural" levels for each country [@prem2021].
+A popular approach by @prem2017 projected from the POLYMOD study to 152 countries.
+This was later updated to include synthetic contact matrices for 177 countries at "urban" and "rural" levels for each country [@prem2021].
 
 However not all countries were included in this list from @prem2021, and for some analyses these synthetic contact matrices were at a large area, such as "urban" or "rural" for a given country.
-One limitation of this is that the predictions were not provided at smaller grained regons.
+One limitation of this is that the predictions were not provided at smaller grained regions.
 This might be important, if for example, a public health group needed to make predictions for specific areas.

### 2024-06-20 tests/testthat/test-models-fit-with-furrr.R
Working on resolving #160
* exports `new_ngm_setting_matrix()` and `new_setting_data()`
* Exports new `age_breaks()` method for class `setting_contact_model` (used in `fit_setting_contacts()`).

@@ -10,7 +10,8 @@ polymod_setting_short <- map(
   .f = function(x) {
     x %>% filter(age_from <= 20, age_to <= 20)
   }
-)
+) |> 
+  new_setting_data()
 
 polymod_population_short <- polymod_population %>% filter(lower.age.limit <= 20)
 
@@ -18,11 +19,16 @@ contact_model <- fit_setting_contacts(
   contact_data_list = polymod_setting_short,
   population = polymod_population_short
 )
+
 contact_model_pred <- predict_setting_contacts(
   population = polymod_population_short,
   contact_model = contact_model,
   age_breaks = c(seq(0, 20, by = 5), Inf)
 )
+
+test_that("predict_setting_contact model prints appropriately", {
+  expect_snapshot(contact_model_pred)
+})
 
 # check that you can specify your own population data for school and work demographics
 contact_model_diff_data <- fit_setting_contacts(
@@ -31,6 +37,10 @@ contact_model_diff_data <- fit_setting_contacts(
   school_demographics = conmat_original_school_demographics,
   work_demographics = conmat_original_work_demographics
 )
+
+test_that("fit_setting_contact model prints appropriately",{
+  expect_snapshot(contact_model)
+})
 
 test_that("list names are kept", {
   expect_snapshot(names(contact_model))

### 2024-07-01 paper/paper.Rmd
Updated introduction

@@
 However, what do we do when we want to (?)look at/estimate contact rates in other countries that have not been measured?
-We can use this existing data to help us project to countries or places that do not have empirical survey data.
+We can use this existing data to help us project to countries or places that do not have empirical contact survey data.
 These are called "synthetic contact matrices".
-A popular approach by @prem2017 projected from the POLYMOD study to 152 countries.
+A popular approach by @prem2017 projected contact rates from the POLYMOD study to 152 countries.
 This was later updated to include synthetic contact matrices for 177 countries at "urban" and "rural" levels for each country [@prem2021].
 
-However not all countries were included in this list from @prem2021, and for some analyses these synthetic contact matrices were at a large area, such as "urban" or "rural" for a given country.
-One limitation of this is that the predictions were not provided at smaller grained regions.
-This might be important, if for example, a public health group needed to make predictions for specific areas.
-It was challenging to apply the methodology used by Prem et al, as while their analysis code was provided, it was not designed for reuse.
+However, there were major limitations with the methods in @prem2021.
+First, not all countries were included in their analyses.
+Second, some of the synthetic contact matrices did not have enough granularity; they covered a large area, such as "urban" or "rural" for a given country.
+This is disadvantegous as public health groups might need to make predictions for more fine-grained areas within a country, such as a district or municipality.
+Third, the methodology used by Prem et al.
+was challenging to reuse in other contexts.
+Prem et al.
+provided the code used for their analysis, but that code was not designed for replicability and user-defined inputs.
 

### 2024-07-01 paper/paper.Rmd

@@
 ```
+
+[comment]: Revised, edited text below the original text.
 
@@
 
+[ #NOTE revised text of above paragraph ]
 `conmat` was built to predict at four settings: work, school, home, and other. 
-The model is built to predict four separate models, one for each setting. [ #TODO a better way of saying the sentence prior? Predict four separate matrices?]
-The model is a Poisson generalised additive model (GAM), predicting the count of contacts, with an offset of the log of participants.
-There are six terms to explain six key features of the relationship between ages, and optional terms for attendance at school or work, depending on which setting the model is predicting to.
+The model fitted is a Poisson generalised additive model (GAM) which predicts the count of contacts, with an offset for the log of participants.
+The model has six (?)covariates/terms to explain six key features of the relationship between ages, and two optional terms for attendance at school or work.
+The two optional terms are included depending on which setting the model is fitted for.
+There are four resulting models, with one model fitted for each setting.
 
-The six terms are
+The six terms are the `|i-j|`,
 

### 2024-07-16 paper/paper.Rmd
Updated "model interface" section

@@
 
-- Input: age and population data, and Output: synthetic contact matrix
-- Create next generation matrices (NGMs)
-- Apply vaccination reduction to NGMs
-- Use NGMs in disease modelling
-- Provide tidy Australian survey data from the Australian Bureau of Statistics for use.
+The `conmat` package was developed to fill the specific need of creating synthetic contact matrices for local government areas in Australia.
+This package is used for [ #TODO what work, specifically?
+Health?
+Provide example.
+Or is *this* package commissioned by the Aus govt?
+] work commissioned by the Australian government.
+We developed methods and software to facilitate the following tasks.
+
+- Generate, as output, synthetic contact matrices from age-stratfied population data.
+- Create next generation matrices (NGMs).
+- Apply vaccination reduction to NGMs.
+- Use NGMs in disease modelling.
+- Provide tidied population data from the Australian Bureau of Statistics.
 
@@
 
-[ #NOTE revised text of above paragraph ]
 `conmat` was built to predict at four settings: work, school, home, and other. 
@@
 
-The six key features of the relationship are shown in the figure below.
+The six key features of the relationship between the age groups, represented by the six terms, are displayed in the figure below.
 
@@
 If you sum across all the *j* age groups for each *i* age group, you get the predicted total number of contacts per day for each individual of age group *i*.
-[ #TODO expected, predicted, or average?]
+[ #TODO expected, predicted, or average?
+]
 
-[ #TODO notes-to-self: the model structure wasn't generated through any particularly robust process, it was just coming up with structures that looked mildly appropriate for our use case.
+[ #TODO notes-to-self: the model structure wasn't generated through any particularly robust process, it was just coming up with structures that looked mildly appropriate for our use case. ]
 
@@
 
-We provide multiple levels for the user to interact with for model fitting, further detail can be seen at: https://idem-lab.github.io/conmat/dev/
+We provide functions for model fitting at various use cases. Further detail for each of the following functions can be seen at: https://idem-lab.github.io/conmat/dev/
 
 * `fit_single_contact_model()`
-    * Using contact survey data to fit a GAM model, adding provided target population information to provide population size information.
-Recommended for when you want to fit to just a single setting, for which you might want to provide your own contact survey data.
+    * Fits a generalised additive model (GAM) using contact survey data and population size information.
+This function is recommended for when you want to fit a model to only one setting, for which you might want to provide your own contact survey data.
 
@@
 
-    * This takes a fitted model from `fit_single_contact_model`, and then predicts to a provided population
+    * This takes a fitted model from `fit_single_contact_model()` and predicts [ #TODO what is predicted? ] to a provided (?) population structure.
 
 * `fit_setting_contacts()`
-    * Fits the `fit_single_contact_model()` to each setting. Recommended for when you have multiple settings to fit. Returns a list of fitted models.
+    * Fits the `fit_single_contact_model()` to each setting. This function is useful for when you have multiple settings to fit. Returns a list of fitted models.
 
 * `predict_setting_contacts()`
-    * Takes a list of fitted models from `fit_setting_contacts()` and predicts to a given population for each setting.
+    * Takes a list of fitted models from `fit_setting_contacts()` and predicts [ #TODO what is predicted? ] to a given population for each setting.
 
@@
     * Takes population information and projects pre-fit model from POLYMOD - used for speed when you know you want to take an already fit model from POLYMOD and just fit it to your provided population.
+
+[ #TODO for the above it's good to explain what exactly is predicted. Otherwise it's confusing for the user to understand what each of the model outputs? ]
 

### 2024-07-16 paper/paper.Rmd
Updated conclusion section
Added an abstract
Updated abstract

@@
 
-# Summary
+# Abstract
+
+This article introduces `conmat`, an R package which generates synthetic contact matrices.
+
+There are currently few options to generate synthetic contact matrices with existing contact surveys. 
+Existing methods to generate synthetic contact matrices are not designed for replicability, do not have enough granularity, and does not cover enough administrative areas (some countries are not included).
+
+A higher level of granularity however is sometimes required to make public health decisions for a given population.
+
+[ What's different and useful about conmat? ]
+
+[ What else is covered in this paper? ] The implemented methods are tested and an example of its use is provided for a local government area (i.e. sub-national level) in Australia.
+
+# Motivation / Introduction
 
@@
 Prem et al.
-provided the code used for their analysis, but that code was not designed for replicability and user-defined inputs.
+provided the code used for their analysis, but that code was not designed for replicability and use with user-defined inputs.
 
-The `conmat` package was created to fill a specific need for creating synthetic contact matrices for specific local government areas for Australia, for work commissioned by the Australian government.
+[REVISED PARAGRAPH BELOW] The `conmat` package was created to fill a specific need for creating synthetic contact matrices for specific local government areas for Australia, for work commissioned by the Australian government.
 We created methods and software to facilitate the following:
@@
 
-# Future Work
+# Conclusions and Future Direction
 

### 2024-07-16 paper/paper.Rmd
Updated abstract

@@
 
-[comment]: Revised, edited text below the original text.
-
 # Abstract
@@
 
+[ What's different and useful about conmat? ] 
 A higher level of granularity however is sometimes required to make public health decisions for a given population.
 
-[ What's different and useful about conmat? ]
+`conmat` also provides flexibility, in that it allows users to specify the area in which they would like the contact matrices to be generated; it allows users to specify their own age groups and population structures; it allows users to upload their own contact surveys to fit the model on; and it allows users to generate the contact matrices at different settings.
 

### 2024-07-16 paper/paper.Rmd
Updated conlcusion

@@
 
-# Conclusions and Future Direction
+# Conclusions and future directions
 
+Our future direction for `conmat` includes adding the following functionalities:
 * Create a contact matrix using a custom contact survey from another source, such as the `socialmixr` R package.
@@
 
+[ #TODO Change the following sentence, copied ad verbatim from JSS bizicount because I like it ] For now, however, we feel that our base `bizicount` package is sufficiently general to assist in estimating the models most often encountered by applied researchers.
+
 # References

### 2024-07-16 paper/paper.Rmd
Updated syncomat implementation example

@@
 
-The results are surveys that can be found in the syncomat package, which can be seen at: https://idem-lab
+One of the issues with the contact matrices generated by @prem2017 is that some countries are missing.
+To remedy this we generated synthetic contact matrices for 200 countries, based on a list of country names by the UN, fitted on the POLYMOD contact surveys.
+We also ensured that the analysis pipeline is reproducible and transparent by utilising a targets workflow, which allows ease of editing for users.
+The resulting synthetic contact matrices, and a replicable / extensible (?) analysis pipeline, can be found in the syncomat analysis pipeline ([GitHub](https://github.com/idem-lab/syncomat), [Zenodo](https://zenodo.org/records/11365943)).
 

### 2024-07-17 paper/paper.Rmd
Updated implementation section
Updated abstract

@@
 
-There are currently few options to generate synthetic contact matrices with existing contact surveys. 
-Existing methods to generate synthetic contact matrices are not designed for replicability, do not have enough granularity, and does not cover enough administrative areas (some countries are not included).
+There are currently few options for a user to generate their own synthetic contact matrices. 
+Existing methods to generate synthetic contact matrices are not designed for replicability, do not have enough granularity, and does not cover enough administrative areas (in other words, some countries are not included).
 
 [ What's different and useful about conmat? ] 
+Users might have their own contact survey data that they would like to generate synthetic contact matrices from.
+Perhaps the population demography is different, or the contact rates varying.
 A higher level of granularity however is sometimes required to make public health decisions for a given population.
@@
 
-[ What else is covered in this paper? ] The implemented methods are tested and an example of its use is provided for a local government area (i.e. sub-national level) in Australia.
+[ What else is covered in this paper? ] The implemented methods are tested and an example of its use is provided for a local government area (i.e. at the sub-national level) in Australia.
 
@@
 
+[ #TODO Is this also a heat map? ]
+
 # Implementation
@@
 
-The six terms are the `|i-j|`,
-
-The six key features of the relationship between the age groups, represented by the six terms, are displayed in the figure below.
-
-```{r}
-# use DHARMA to show a partial dep plot of the six main terms
-```
-
 Each cell in the resulting contact matrix, indexed *i*, *j*, is the predicted number of people in age group *j* that a single individual in age group *i* will have contact with per day.
@@
 [ #TODO expected, predicted, or average?
+Does it matter?
 ]
 
+The six terms are $|i-j|$, ${|i-j|}^{2}$, $i + j$, $i \times j$, $\text{max}(i, j)$ and $\text{min}(i, j)$.
+
+The six key features of the relationship between the age groups, represented by the six terms, are displayed in the figure below. 
 [ #TODO notes-to-self: the model structure wasn't generated through any particularly robust process, it was just coming up with structures that looked mildly appropriate for our use case. ]
+
+```{r}
+# Show partial dep plot of the six main terms
+```
 

### 2024-07-17 paper/paper.Rmd
Updated motivation / introduction

@@
 #TODO - A better first sentence that encapsulates conmat use? 
-Understanding the dynamics of infectious disease transmission in a population is an important task (?) for epidemiologists and public policy makers.
-Identifying vulnerable groups and predicting disease transmission (?)dynamics are essential for informed public health decision-making.
+Understanding the dynamics of infectious disease transmission is an important task (?) for epidemiologists and public policy makers.
+Identifying vulnerable groups and predicting disease transmission (?)dynamics / how diseases spread are essential for informed public health decision-making. 
 Infectious diseases such as influenza and coronavirus spread through human-to-human interactions, or in other words, "social contact".
-Quantifying social contact and its patterns can provide critical insights into how diseases spread.
+Quantifying social contact and its patterns can provide critical insights into how these diseases spread.
+[ Is this circular?
+] / and how best to mitigate the spread of these diseases.
 
@@
 As an example, the "POLYMOD" study by @mossong2008 covered 8 European countries: Belgium, Germany, Finland, Great Britain, Italy, Luxembourg, The Netherlands, and Poland [@mossong2008].
-However, what do we do when we want to (?)look at/estimate contact rates in other countries that have not been measured?
-We can use this existing data to help us project to countries or places that do not have empirical contact survey data.
+However, what do we do when we want to estimate contact rates in other countries where this is not yet measured?
+We can use existing data--the contact rates obtained from contact surveys--to help us project / predict these estimates to countries or places that do not have them.
 These are called "synthetic contact matrices".
@@
 This was later updated to include synthetic contact matrices for 177 countries at "urban" and "rural" levels for each country [@prem2021].
+[ #TODO is project or predict a better word? Does it matter? ]
 
@@
 First, not all countries were included in their analyses.
-Second, some of the synthetic contact matrices did not have enough granularity; they covered a large area, such as "urban" or "rural" for a given country.
-This is disadvantegous as public health groups might need to make predictions for more fine-grained areas within a country, such as a district or municipality.
+Second, some of the synthetic contact matrices did not have enough granularity; in other words, they covered areas that are too large, such as the "urban" or "rural" parts of a country.
+This is disadvantageous as public health groups might need to make predictions for more fine-grained areas within a country, such as a district or municipality.
 Third, the methodology used by Prem et al.
@@
 Prem et al.
-provided the code used for their analysis, but that code was not designed for replicability and use with user-defined inputs.
+provided the code used for their analysis, but that code was not designed for replicability and easy modification with user-defined inputs.
 
@@
 
-We can generate a contact matrix for `perth` using the `extrapolate_polymod` function, where the contact matrix is generated using a model fitted from the POLYMOD data.
+We can then generate a contact matrix for `perth` using the `extrapolate_polymod` function, where the contact matrix is generated using a model fitted from the POLYMOD data.
 
@@
 ```
-
-[ #TODO Is this also a heat map? ]
 

### 2024-07-23 paper/paper.Rmd
Updated for JOSS format
Updated explanation on partial dependency plots, and how exponentiating them after adding them up together provides more 'realistic' numbers

@@
 
-# Abstract
+# Summary
+
+A summary describing the high-level functionality and purpose of the software for a diverse, non-specialist audience.
 
@@
 
-# Motivation / Introduction
+# Statement of need
+
+A Statement of need section that clearly illustrates the research purpose of the software and places it in the context of related work.
 
@@
 
+Note that these partial dependency plots are on the log scale. 
+When the six terms are added up together for each setting (in other words, each model) and exponentiated, they show the following patterns:
+
+```{r}
+# Show combined partial dep plot (i.e. sum of the partial dependencies for all six terms) in each setting: home, school, work and other
+```
+
+In other words, the six terms above provide patterns that are useful in modelling the different settings,
+and correspond with real-life situations of how contact would look like. 
+In the home setting for example, [ #TODO describe how children interact with parents and elderly generation, grandparents ].
+When the terms for school and work are added, these terms also provide patterns that correspond with real-life situations.
+https://idem-lab.github.io/conmat/dev/articles/visualising-conmat.html
+In the school setting, children tend to contact other children in the same age groups as them.
+In the work setting, there are no contacts with children under the age of ten and minimal contact with adults beyond retirement age.
+
 One of the issues with the contact matrices generated by @prem2017 is that some countries are missing.

### 2024-07-23 paper/paper.Rmd
Improved explanation for model fitting

@@
 `conmat` was built to predict at four settings: work, school, home, and other. 
-The model fitted is a Poisson generalised additive model (GAM) which predicts the count of contacts, with an offset for the log of participants.
-The model has six (?)covariates/terms to explain six key features of the relationship between ages, and two optional terms for attendance at school or work.
+One model is fitted for each setting. 
+Each model fitted is a Poisson generalised additive model (GAM) which predicts the count of contacts, with an offset for the log of participants. 
+The model has six (?)covariates/terms to explain six key features of the relationship between ages, 
+and two optional terms for attendance at school or work.
 The two optional terms are included depending on which setting the model is fitted for.
-There are four resulting models, with one model fitted for each setting.
 
@@
 
-The six terms are $|i-j|$, ${|i-j|}^{2}$, $i + j$, $i \times j$, $\text{max}(i, j)$ and $\text{min}(i, j)$.
+The six terms are 
+$|i-j|$, 
+${|i-j|}^{2}$, 
+$i + j$, 
+$i \times j$, 
+$\text{max}(i, j)$ and 
+$\text{min}(i, j)$.
 

### 2024-07-23 paper/paper.Rmd
improved wording

@@
 
-We provide functions for model fitting at various use cases. Further detail for each of the following functions can be seen at: https://idem-lab.github.io/conmat/dev/
+We provide functions for model fitting at various use cases. Further detail for each of the following functions are available at: https://idem-lab.github.io/conmat/dev/
 
@@
     * Fits a generalised additive model (GAM) using contact survey data and population size information.
-This function is recommended for when you want to fit a model to only one setting, for which you might want to provide your own contact survey data.
+This function is recommended when you want to fit a model to only one setting, for which you might want to provide your own contact survey data.
 

### 2024-07-24 paper/paper.Rmd
Updated intro and conclusion; improved wording

@@
 
-A summary describing the high-level functionality and purpose of the software for a diverse, non-specialist audience.
+[ A summary describing the high-level functionality and purpose of the software for a diverse, non-specialist audience. ]
 
@@
 
-[ What else is covered in this paper? ] The implemented methods are tested and an example of its use is provided for a local government area (i.e. at the sub-national level) in Australia.
+[ What else is covered in this paper? ] An example use-case for `conmat` is provided for a local government area (i.e. at the sub-national level) in Australia.
+Also provided is an analysis pipeline to support conmat, [`syncomat`](https://github.com/idem-lab/syncomat), which generates synthetic contact matrices for 200 countries.
 
@@
 
-A Statement of need section that clearly illustrates the research purpose of the software and places it in the context of related work.
+[ A Statement of need section that clearly illustrates the research purpose of the software and places it in the context of related work. ]
 
@@
 
-[ #TODO Change the following sentence, copied ad verbatim from JSS bizicount because I like it ] For now, however, we feel that our base `bizicount` package is sufficiently general to assist in estimating the models most often encountered by applied researchers.
+[ #TODO Change concluding sentence.
+The following is copied ad verbatim from JSS bizicount because I like it ] For now, however, we feel that our base `bizicount` package is sufficiently general to assist in estimating the models most often encountered by applied researchers.
 

### 2024-07-26 README.Rmd
Update README to include cran instructions

@@
 <!-- badges: start -->
-[![R-CMD-check](https://github.com/njtierney/conmat/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/njtierney/conmat/actions/workflows/R-CMD-check.yaml)
-[![Codecov test coverage](https://codecov.io/gh/njtierney/conmat/branch/master/graph/badge.svg)](https://codecov.io/gh/njtierney/conmat?branch=master)
+[![R-CMD-check](https://github.com/idem-lab/conmat/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/idem-lab/conmat/actions/workflows/R-CMD-check.yaml)
+[![Codecov test coverage](https://codecov.io/gh/idem-lab/conmat/branch/master/graph/badge.svg)](https://codecov.io/gh/idem-lab/conmat?branch=master)
 <!-- badges: end -->
@@
 
+You can install the stable version from cran with:
+
+```r
+install.packages("conmat")
+```
+
 You can install the development version with:
@@
 ```r
-install.packages("conmat", repos = "https://njtierney.r-universe.dev")
+install.packages("conmat", repos = "https://idem-lab.r-universe.dev")
 ```
@@
 # install.packages("remotes")
-remotes::install_github("njtierney/conmat")
+remotes::install_github("idem-lab/conmat")
 ```

### 2024-07-26 README.Rmd
Fix rogue links

@@
 [![R-CMD-check](https://github.com/idem-lab/conmat/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/idem-lab/conmat/actions/workflows/R-CMD-check.yaml)
-[![Codecov test coverage](https://codecov.io/gh/idem-lab/conmat/branch/master/graph/badge.svg)](https://codecov.io/gh/idem-lab/conmat?branch=master)
+[![Codecov test coverage](https://codecov.io/gh/idem-lab/conmat/branch/master/graph/badge.svg)](https://app.codecov.io/gh/idem-lab/conmat?branch=master)
 <!-- badges: end -->

### 2024-07-26 R/data_abs_household_lga.R

@@ -16,6 +16,6 @@
 #'   \item{n_households}{number of households with that number of people}
 #' }
 #' @note still need to clean this
-#' @source  \url{https://stat.data.abs.gov.au/Index.aspx?Datasetcode=ABS_FAMILY_PROJ}
+#' @source  \url{https://www.abs.gov.au/statistics}
 #' (downloaded the CSV) PEOPLE > People and Communities > Household Composition > Census 2016, T23 Household Composition By Number Of Persons Usually Resident (LGA)
 "abs_household_lga"

### 2024-08-07 paper/paper.Rmd
adding some notes from review

@@
 
-There are currently few options for a user to generate their own synthetic contact matrices. 
-Existing methods to generate synthetic contact matrices are not designed for replicability, do not have enough granularity, and does not cover enough administrative areas (in other words, some countries are not included).
+There are currently few options for a user to generate their own synthetic contact matrices. [TODO add references/examples - e.g., socialmixr].
+Existing methods to generate synthetic contact matrices are not designed for replicability, do not have enough granularity, and not all areas of interest (countries) are included.
 
 [ What's different and useful about conmat? ]
-Users might have their own contact survey data that they would like to generate synthetic contact matrices from.
-Perhaps the population demography is different, or the contact rates varying.
-A higher level of granularity however is sometimes required to make public health decisions for a given population.
 
-`conmat` also provides flexibility, in that it allows users to specify the area in which they would like the contact matrices to be generated; it allows users to specify their own age groups and population structures; it allows users to upload their own contact surveys to fit the model on; and it allows users to generate the contact matrices at different settings.
+Current interfaces to contact matrices are typically fixed to a given country.
+This means there aren't clear options for retrieving contact matrices for areas of different sizes.
+This is important as not all public health decisions are made at country levels - they might need to be made for specific smaller areas, such as cities and suburbs.
+Perhaps a smaller suburb within a country, or perhaps several countries all together.
+The conmat software allows users to provide their own age population data and combine this with information from an existing contact survey, such as POLYMOD (cite polymod).
+The software exposes model fitting and prediction separately to the user.
+This means users can generate synthetic contact matrices for any region they have age population information for.
 
-[ What else is covered in this paper? ] An example use-case for `conmat` is provided for a local government area (i.e. at the sub-national level) in Australia.
-Also provided is an analysis pipeline to support conmat, [`syncomat`](https://github.com/idem-lab/syncomat), which generates synthetic contact matrices for 200 countries.
+[ What else is covered in this paper? ]
+
+We demonstrate a use-case for `conmat` by creating contact matrices for a state (i.e.
+at the sub-national level) in Australia.
+It is also worth noting that there is an updated analysis pipeline that uses conmat, [`syncomat`](https://github.com/idem-lab/syncomat), to generate synthetic contact matrices for 200 countries.
 
@@
 #TODO - A better first sentence that encapsulates conmat use?
-Understanding the dynamics of infectious disease transmission is an important task (?) for epidemiologists and public policy makers.
+
+Infectious diseases like influenza and COVID19 spread via social contact.
+If we can understand patterns of contact - which people are more likely be in contact with each other - then we will be able to create models of how disease spreads.
+Epidemiologists and public policy makers can uses these models to make decisions to keep a population safe and healthy.
+
 Identifying vulnerable groups and predicting disease transmission (?)dynamics / how diseases spread are essential for informed public health decision-making. 
@@
 This was later updated to include synthetic contact matrices for 177 countries at "urban" and "rural" levels for each country [@prem2021].
-[ #TODO is project or predict a better word? Does it matter? ]
+[ #TODO is project or predict a better word? Does it matter? ] (decision - use *predict*)
 
@@
 Or is *this* package commissioned by the Aus govt?
-] work commissioned by the Australian government.
+note: @MikeLydeamore will reference the official government report] work commissioned by the Australian government.
 We developed methods and software to facilitate the following tasks.
@@
 Each model fitted is a Poisson generalised additive model (GAM) which predicts the count of contacts, with an offset for the log of participants. 
-The model has six (?)covariates/terms to explain six key features of the relationship between ages, 
-and two optional terms for attendance at school or work.
-The two optional terms are included depending on which setting the model is fitted for.
+The model has six covariates to explain six key features of the relationship between ages, 
+and two optional covariates for attendance at school or work.
+The two optional covariates are included depending on which setting the model is fitted for.
 
@@
 Does it matter?
-]
+note: currently going with predicted]
 
-The six terms are 
+The six covariates are 
 $|i-j|$, 
@@
 
-The six key features of the relationship between the age groups, represented by the six terms, are displayed in the figure below. 
+The six key features of the relationship between the age groups, represented by the six covariates, are displayed in the figure below. 
 [ #TODO notes-to-self: the model structure wasn't generated through any particularly robust process, it was just coming up with structures that looked mildly appropriate for our use case. ]
@@
 ```{r}
-# Show partial dep plot of the six main terms
+# Show partial dep plot of the six main covariates
 ```
@@
 Note that these partial dependency plots are on the log scale. 
-When the six terms are added up together for each setting (in other words, each model) and exponentiated, they show the following patterns:
+When the six covariates are added up together for each setting (in other words, each model) and exponentiated, they show the following patterns:
 
 ```{r}
-# Show combined partial dep plot (i.e. sum of the partial dependencies for all six terms) in each setting: home, school, work and other
+# Show combined partial dep plot (i.e. sum of the partial dependencies for all six covariates) in each setting: home, school, work and other
 ```
 
-In other words, the six terms above provide patterns that are useful in modelling the different settings,
+In other words, the six covariates above provide patterns that are useful in modelling the different settings,
 and correspond with real-life situations of how contact would look like. 
 In the home setting for example, [ #TODO describe how children interact with parents and elderly generation, grandparents ].
-When the terms for school and work are added, these terms also provide patterns that correspond with real-life situations.
+When the covariates for school and work are added, these covariates also provide patterns that correspond with real-life situations.
 https://idem-lab.github.io/conmat/dev/articles/visualising-conmat.html
@@
 # References
+
+# Cutting Room Floor
+
+`conmat` also provides flexibility, in that it allows users to specify the area in which they would like the contact matrices to be generated; it allows users to specify their own age groups and population structures; it allows users to upload their own contact surveys to fit the model on; and it allows users to generate the contact matrices at different settings.

### 2024-08-08 paper/paper.Rmd
more minor touches

@@
 This article introduces `conmat`, an R package which generates synthetic contact matrices.
+Contact matrices describe the number of contacts between individuals, typically age groups.
+They are used to create models of infectious disease spread.
 
-There are currently few options for a user to generate their own synthetic contact matrices. [TODO add references/examples - e.g., socialmixr].
-Existing methods to generate synthetic contact matrices are not designed for replicability, do not have enough granularity, and not all areas of interest (countries) are included.
+There are currently only a few options for a user to access synthetic contact matrices [@socialmixr; @prem].
+Existing methods describing how to generate synthetic contact matrices from @prem are not designed for replicability, and not all areas of interest (countries) are included.
 
@@
 Current interfaces to contact matrices are typically fixed to a given country.
-This means there aren't clear options for retrieving contact matrices for areas of different sizes.
-This is important as not all public health decisions are made at country levels - they might need to be made for specific smaller areas, such as cities and suburbs.
-Perhaps a smaller suburb within a country, or perhaps several countries all together.
-The conmat software allows users to provide their own age population data and combine this with information from an existing contact survey, such as POLYMOD (cite polymod).
+There is not a designed interface for someone to access a contact matrix for a sub-region of a country, such as a state, city, or suburb.
+These sub-region areas are important, as many public health decisions are made at that level.
+
+The conmat software allows users to generate their own contact matrix, by providing their own age population data and combining this with information from an existing contact survey, such as POLYMOD [@polymod].
 The software exposes model fitting and prediction separately to the user.
-This means users can generate synthetic contact matrices for any region they have age population information for.
+Users can fit a model based on a contact survey such as POLYMOD, then predict from this model to their own data.
+This means users can generate synthetic contact matrices for any region, with any contact survey, provided they have the relevant data.
 
@@
 
-We demonstrate a use-case for `conmat` by creating contact matrices for a state (i.e.
-at the sub-national level) in Australia.
+We demonstrate a use-case for `conmat` by creating contact matrices for a state (i.e. at the sub-national level) in Australia.
+
+[Need to work out where to fit in `syncomat`]
+
 It is also worth noting that there is an updated analysis pipeline that uses conmat, [`syncomat`](https://github.com/idem-lab/syncomat), to generate synthetic contact matrices for 200 countries.
@@
 If we can understand patterns of contact - which people are more likely be in contact with each other - then we will be able to create models of how disease spreads.
-Epidemiologists and public policy makers can uses these models to make decisions to keep a population safe and healthy.
+Epidemiologists and public policy makers can use these models to make decisions to keep a population safe and healthy.
 
-Identifying vulnerable groups and predicting disease transmission (?)dynamics / how diseases spread are essential for informed public health decision-making. 
+Identifying vulnerable groups and predicting how diseases spread are essential for informed public health decision-making.
 Infectious diseases such as influenza and coronavirus spread through human-to-human interactions, or in other words, "social contact".
@@
 
-We can measure social contact through social contact surveys, where people describe the number and type of social contact they have.
+Social contact surveys quantify social contact by asking people to describe the frequency and type of social contact across different settings (home, work, school, other).
 These surveys provide (?) a measure of contact rates: an empirical estimate of the number of social contacts from one age group to another and the setting of contact.
@@
 However, what do we do when we want to estimate contact rates in other countries where this is not yet measured?
-We can use existing data--the contact rates obtained from contact surveys--to help us project / predict these estimates to countries or places that do not have them.
+We can use existing data--the contact rates obtained from contact surveys--to help us predict these estimates to countries or places that do not have them.
 These are called "synthetic contact matrices".
-A popular approach by @prem2017 projected contact rates from the POLYMOD study to 152 countries.
+A popular approach by @prem2017 predicted contact rates from the POLYMOD study to 152 countries.
 This was later updated to include synthetic contact matrices for 177 countries at "urban" and "rural" levels for each country [@prem2021].
-[ #TODO is project or predict a better word? Does it matter? ] (decision - use *predict*)
 
@@
 * `extrapolate_polymod()`
-    * Takes population information and projects pre-fit model from POLYMOD - used for speed when you know you want to take an already fit model from POLYMOD and just fit it to your provided population.
+    * Takes population information and predicts pre-fit model from POLYMOD - used for speed when you know you want to take an already fit model from POLYMOD and just fit it to your provided population.
 

### 2024-08-08 paper/paper.Rmd
updates from meeting with Mike

@@
 
-Our future direction for `conmat` includes adding the following functionalities:
+The `conmat` software provides a flexible interface to generating synthetic contact matrices using population data and contact surveys.
+These contact matrices can then be used in infectious disease modelling and surveillance.
+
+## Strengths + Weaknesses
+
+The main strength of `conmat` is its interface requiring only age population data to create a synthetic contact matrix.
+Current approaches provide only a selection of country level contact matrices.
+This software can predict to arbitrary demography, such as sub-national, or simulated populations.
+
+We provide a trained model of contact rate that is fit to the POLYMOD survey for ease of use.
+The software also has an interface to use other contact surveys, such as @comix.
+This is important as POLYMOD represents contact patterns in 8 countries in Europe, and contact patterns are known to differ across nations and cultures.
+
+The model structure (covariates?) provided in conmat was designed to represent the key features that are typically present in a contact matrix for different settings (work, school, home, other).
+Including other sources of information that may better describe these contact patterns, such as ..., may improve model performance.
+
+The interface to the model formula in conmat is fixed; users cannot change the covariates of the model.
+This means that if there is an unusual structure in their contact data it might not be accurately captured by conmat.
+It was a design decision that was made to focus on the key feature of conmat: using just age population data to predict a contact matrix.
+
+## Meaning of the work
+
+Public health decisions are often based on age specific information, which means the more accurate your age specific models are, the better those decisions are likely to be.
+This is the first piece of software that will provide appropriate contact matrices for a population, which means more accurate models of disease.
+
+This work was used as a key input into several models for COVID19 in Australia and contributed directly to decisions around vaccination policy.
+
+## Unanswered questions / Future Directions
+
+Future directions for this software could include:
+
 * Create a contact matrix using a custom contact survey from another source, such as  the `socialmixr` R package.
@@
 
-[ #TODO Change concluding sentence.
-The following is copied ad verbatim from JSS bizicount because I like it ] For now, however, we feel that our base `bizicount` package is sufficiently general to assist in estimating the models most often encountered by applied researchers.
+Software is never finished, and the software in its current format has proven useful for infectious disease modelling.
+In time we hope it can become more widely used and be useful for more applications in epidemiology and public health.
 
 # References
+
+https://www.doherty.edu.au/our-work/institute-themes/viral-infectious-diseases/covid-19/covid-19-modelling/modelling
 

### 2024-08-09 paper/paper.Rmd
various word cutting down from meeting

@@
 output:
+  pdf_document: default
   html_document:
     keep_md: yes
-  pdf_document: default
 bibliography: references.bib
@@
 
-[ A summary describing the high-level functionality and purpose of the software for a diverse, non-specialist audience. ]
-
 This article introduces `conmat`, an R package which generates synthetic contact matrices.
@@
 There are currently only a few options for a user to access synthetic contact matrices [@socialmixr; @prem].
-Existing methods describing how to generate synthetic contact matrices from @prem are not designed for replicability, and not all areas of interest (countries) are included.
+Existing methods describing how to generate synthetic contact matrices from @prem are not designed for replicability, and are restricted to only selected countries with no sub-national demographic estimates available.
 
-[ What's different and useful about conmat? ]
-
-Current interfaces to contact matrices are typically fixed to a given country.
-There is not a designed interface for someone to access a contact matrix for a sub-region of a country, such as a state, city, or suburb.
-These sub-region areas are important, as many public health decisions are made at that level.
-
-The conmat software allows users to generate their own contact matrix, by providing their own age population data and combining this with information from an existing contact survey, such as POLYMOD [@polymod].
 The software exposes model fitting and prediction separately to the user.
@@
 
-[ What else is covered in this paper? ]
-
 We demonstrate a use-case for `conmat` by creating contact matrices for a state (i.e. at the sub-national level) in Australia.
 
-[Need to work out where to fit in `syncomat`]
-
-It is also worth noting that there is an updated analysis pipeline that uses conmat, [`syncomat`](https://github.com/idem-lab/syncomat), to generate synthetic contact matrices for 200 countries.
+One of the issues with the contact matrices generated by @prem2017 is that some countries are missing.
+To remedy this we generated synthetic contact matrices for 200 countries, based on a list of country names by the UN, fitted on the POLYMOD contact surveys.
+We also ensured that the analysis pipeline is reproducible and transparent by utilising a targets workflow, which allows ease of editing for users.
+The resulting synthetic contact matrices, and a replicable / extensible (?) analysis pipeline, can be found in the syncomat analysis pipeline ([GitHub](https://github.com/idem-lab/syncomat), [Zenodo](https://zenodo.org/records/11365943)).
 
 # Statement of need
-
-[ A Statement of need section that clearly illustrates the research purpose of the software and places it in the context of related work. ]
-
-#TODO - A better first sentence that encapsulates conmat use?
 
@@
 
-Identifying vulnerable groups and predicting how diseases spread are essential for informed public health decision-making.
-Infectious diseases such as influenza and coronavirus spread through human-to-human interactions, or in other words, "social contact".
-Quantifying social contact and its patterns can provide critical insights into how these diseases spread.
-[ Is this circular?
-] / and how best to mitigate the spread of these diseases.
+Empirical estimates of social contact are provided by social contact surveys. These provide the frequency and type of social contact across different settings (home, work, school, other).
 
-Social contact surveys quantify social contact by asking people to describe the frequency and type of social contact across different settings (home, work, school, other).
-These surveys provide (?) a measure of contact rates: an empirical estimate of the number of social contacts from one age group to another and the setting of contact.
-For example, we might learn from a contact survey that homes have higher contact between 25-50 year olds and 0-15 year olds, whereas workplaces might have high contact within 25-60 year olds.
+An prominent contact survey is the "POLYMOD" study by @mossong2008, which covered 8 European countries: Belgium, Germany, Finland, Great Britain, Italy, Luxembourg, The Netherlands, and Poland [@mossong2008].
 
-These social contact surveys exist for a few countries.
-As an example, the "POLYMOD" study by @mossong2008 covered 8 European countries: Belgium, Germany, Finland, Great Britain, Italy, Luxembourg, The Netherlands, and Poland [@mossong2008].
-However, what do we do when we want to estimate contact rates in other countries where this is not yet measured?
-We can use existing data--the contact rates obtained from contact surveys--to help us predict these estimates to countries or places that do not have them.
-These are called "synthetic contact matrices".
-A popular approach by @prem2017 predicted contact rates from the POLYMOD study to 152 countries.
-This was later updated to include synthetic contact matrices for 177 countries at "urban" and "rural" levels for each country [@prem2021].
+These social contact surveys can be projected on to a given demographic structure to produce estimated daily contact rates between age groups.
+These are known as contact matrices or synthetic contact matrices.
+A widely used approach by @prem2017 [@prem2021] produced contact matrices for 177 countries at "urban" and "rural" levels for each country.
 
@@
 First, not all countries were included in their analyses.
-Second, some of the synthetic contact matrices did not have enough granularity; in other words, they covered areas that are too large, such as the "urban" or "rural" parts of a country.
-This is disadvantageous as public health groups might need to make predictions for more fine-grained areas within a country, such as a district or municipality.
-Third, the methodology used by Prem et al.
-was challenging to reuse in other contexts.
-Prem et al.
-provided the code used for their analysis, but that code was not designed for replicability and easy modification with user-defined inputs.
+Second, the contact matrices only covered broad scale areas.
+This presents challenges for decision makers who are often working at a sub-national geographical scale.
+Third, the code provided by Prem et al., was not designed for replicability and easy modification with user-defined inputs.
 
-[REVISED PARAGRAPH BELOW] The `conmat` package was created to fill a specific need for creating synthetic contact matrices for specific local government areas for Australia, for work commissioned by the Australian government.
-We created methods and software to facilitate the following:
-
-The `conmat` package was developed to fill the specific need of creating synthetic contact matrices for local government areas in Australia.
-This package is used for [ #TODO what work, specifically?
-Health?
-Provide example.
-Or is *this* package commissioned by the Aus govt?
-note: @MikeLydeamore will reference the official government report] work commissioned by the Australian government.
-We developed methods and software to facilitate the following tasks.
-
-- Generate, as output, synthetic contact matrices from age-stratfied population data.
-- Create next generation matrices (NGMs).
-- Apply vaccination reduction to NGMs.
-- Use NGMs in disease modelling.
-- Provide tidied population data from the Australian Bureau of Statistics.
+The `conmat` package was developed to fill the specific need of creating contact matrices for arbitrary demographic structures.
+We developed the method primarily to output contact matrices.
+We also provided methods to create next generation matrices.
 
@@
 
-As an example, let us generate a contact matrix for a local government area within Australia, using a model fitted from the POLYMOD data.
-
-Suppose we want to generate a contact matrix for the City of Perth. We can get the age-stratified population data for Perth from the helper function `abs_age_lga`:
+We will generate a contact matrix for Tasmania area within Australia, using a model fitted from the POLYMOD contact survey.
+We can get the age-stratified population data for Tasmania from the helper function `abs_age_state()`:
 
@@
 library(conmat)
-perth <- abs_age_lga("Perth (C)")
-perth
+tasmania <- abs_age_state("TAS")
+tasmania
 ```
 
-We can then generate a contact matrix for `perth` using the `extrapolate_polymod` function, where the contact matrix is generated using a model fitted from the POLYMOD data.
+We can then generate a contact matrix for Tasmania using `extrapolate_polymod()`.
 
@@
 #| label: extrapolate-polymod
-#| echo: true
-perth_contact <- extrapolate_polymod(population = perth)
-perth_contact
+tasmania_contact <- extrapolate_polymod(population = tasmania)
+tasmania_contact
 ```
 
-We can plot the resulting contact matrix for Perth with `autoplot`:
+We can plot the resulting contact matrix for Tasmania with `autoplot`:
 
@@
 #| label: autoplot-contacts
-autoplot(perth_contact)
+#| fig.width: 8
+#| fig.height: 8
+autoplot(tasmania_contact)
 ```
@@
 # Implementation
+
+The overall approach of `conmat` has two parts:
+
+1) Fit a model to predict individual contact rate, using an existing contact survey
+2) Predict a contact matrix using age population data
+
+## Model fitting
 
@@
 The six key features of the relationship between the age groups, represented by the six covariates, are displayed in the figure below.
+
 [ #TODO notes-to-self: the model structure wasn't generated through any particularly robust process, it was just coming up with structures that looked mildly appropriate for our use case. ]
@@
 Note that these partial dependency plots are on the log scale.
+
 When the six covariates are added up together for each setting (in other words, each model) and exponentiated, they show the following patterns:
@@
 In the work setting, there are no contacts with children under the age of ten and minimal contact with adults beyond retirement age.
-
-One of the issues with the contact matrices generated by @prem2017 is that some countries are missing.
-To remedy this we generated synthetic contact matrices for 200 countries, based on a list of country names by the UN, fitted on the POLYMOD contact surveys.
-We also ensured that the analysis pipeline is reproducible and transparent by utilising a targets workflow, which allows ease of editing for users.
-The resulting synthetic contact matrices, and a replicable / extensible (?) analysis pipeline, can be found in the syncomat analysis pipeline ([GitHub](https://github.com/idem-lab/syncomat), [Zenodo](https://zenodo.org/records/11365943)).
-
-## Model interfaces
-
-We provide functions for model fitting at various use cases. Further detail for each of the following functions are available at: https://idem-lab.github.io/conmat/dev/
-
-* `fit_single_contact_model()`
-    * Fits a generalised additive model (GAM) using contact survey data and population size information.
-This function is recommended when you want to fit a model to only one setting, for which you might want to provide your own contact survey data.
-
-* `predict_contacts()`
-
-    * This takes a fitted model from `fit_single_contact_model()` and predicts [ #TODO what is predicted? ] to a provided (?) population structure.
-
-* `fit_setting_contacts()`
-    * Fits the `fit_single_contact_model()` to each setting. This function is useful for when you have multiple settings to fit. Returns a list of fitted models.
-
-* `predict_setting_contacts()`
-    * Takes a list of fitted models from `fit_setting_contacts()` and predicts [ #TODO what is predicted? ] to a given population for each setting.
-
-* `estimate_setting_contacts()`
-    * A convenience function that fits multiple models, one for each setting.
-This means fitting `fit_setting_contacts()` and then `predict_setting_contacts()`.
-Recommended for when you have multiple settings to fit and want to predict to a given population as well.
-
-* `extrapolate_polymod()`
-    * Takes population information and predicts pre-fit model from POLYMOD - used for speed when you know you want to take an already fit model from POLYMOD and just fit it to your provided population.
-
-[ #TODO for the above it's good to explain what exactly is predicted. Otherwise it's confusing for the user to understand what each of the model outputs? ]
 
@@
 
-Future directions for this software could include:
+Some future directions for this software include:
 
-* Create a contact matrix using a custom contact survey from another source, such as  the `socialmixr` R package.
+* Demonstrate fitting a model to other contact surveys from sources such as the `socialmixr` R package [@socialmixr].
 * Predict to any age brackets - such as monthly ages, for example, 1, 3, 6, month year old infants
-* Add ability to fit multiple contact surveys at once, e.g., POLYMOD and another dataset
-* Add ability to include known household age distributions as offsets in the 'home' setting model, in place of the whole population distribution.
-So compute household age matrices (like age-structured contact matrices, but for household members instead of contacts) from POLYMOD data.
-If we compute a different one for each household size, in the POLYMOD data (probably estimated with another GAM, to make best use of the limited data) we might be able to extrapolate household age matrices to new countries based on the distribution of household sizes.
+* Fitting to multiple contact surveys simultaneously, e.g., POLYMOD and CoMix
+* Add uncertainty to estimates
 * Add methods for including household size distributions
-* Add uncertainty to estimates
-* Move Australian centric data into its own package
-* Add documentation on specifying your own GAM model and using this workflow
+* Include known household age distributions as offsets in the 'home' setting model, in place of the whole population distribution.
 
@@
 In time we hope it can become more widely used and be useful for more applications in epidemiology and public health.
+
+NOTE: It is also worth noting that there is an updated analysis pipeline that uses conmat, [`syncomat`](https://github.com/idem-lab/syncomat), to generate synthetic contact matrices for 200 countries.
 
@@
 
-# Cutting Room Floor
-
-`conmat` also provides flexibility, in that it allows users to specify the area in which they would like the contact matrices to be generated; it allows users to specify their own age groups and population structures; it allows users to upload their own contact surveys to fit the model on; and it allows users to generate the contact matrices at different settings.
+Identifying vulnerable groups and predicting how diseases spread are essential for informed public health decision-making.
+Infectious diseases such as influenza and coronavirus spread through human-to-human interactions, or in other words, "social contact".
+Quantifying social contact and its patterns can provide critical insights into how these diseases spread.
+[ Is this circular?
+] / and how best to mitigate the spread of these diseases.

### 2024-08-14 paper/paper.Rmd
Fit more word cleanup

@@
 
-There are currently only a few options for a user to access synthetic contact matrices [@socialmixr; @prem].
-Existing methods describing how to generate synthetic contact matrices from @prem are not designed for replicability, and are restricted to only selected countries with no sub-national demographic estimates available.
+There are currently few options for a user to access synthetic contact matrices [@socialmixr; @prem2017].
+Existing code to generate synthetic contact matrices from @prem2017 are not designed for replicability, and are restricted to only selected countries with no sub-national demographic estimates available.
 
 The software exposes model fitting and prediction separately to the user.
-Users can fit a model based on a contact survey such as POLYMOD, then predict from this model to their own data.
+Users can fit a model based on a contact survey such as POLYMOD [@mossong2008], then predict from this model to their own data.
 This means users can generate synthetic contact matrices for any region, with any contact survey, provided they have the relevant data.
@@
 
-One of the issues with the contact matrices generated by @prem2017 is that some countries are missing.
-To remedy this we generated synthetic contact matrices for 200 countries, based on a list of country names by the UN, fitted on the POLYMOD contact surveys.
-We also ensured that the analysis pipeline is reproducible and transparent by utilising a targets workflow, which allows ease of editing for users.
-The resulting synthetic contact matrices, and a replicable / extensible (?) analysis pipeline, can be found in the syncomat analysis pipeline ([GitHub](https://github.com/idem-lab/syncomat), [Zenodo](https://zenodo.org/records/11365943)).
+For users who do not wish to run the entire `conmat` pipeline, we have pre-generated synthetic contact matrices for 200 countries, based on a list of country names by the UN, using a model fit to the POLYMOD contact survey.
+These resulting synthetic contact matrices, and the associated code, can be found in the syncomat analysis pipeline ([GitHub](https://github.com/idem-lab/syncomat), [Zenodo](https://zenodo.org/records/11365943)).
 
@@
 
-Empirical estimates of social contact are provided by social contact surveys. These provide the frequency and type of social contact across different settings (home, work, school, other).
+Empirical estimates of social contact are provided by social contact surveys. These provide samples of the frequency and type of social contact across different settings (home, work, school, other).
 
@@
 These are known as contact matrices or synthetic contact matrices.
-A widely used approach by @prem2017 [@prem2021] produced contact matrices for 177 countries at "urban" and "rural" levels for each country.
+A widely used approach by @prem2021 [@prem2021] produced contact matrices for 177 countries at "urban" and "rural" levels for each country.
 
@@
 The `conmat` package was developed to fill the specific need of creating contact matrices for arbitrary demographic structures.
-We developed the method primarily to output contact matrices.
+We developed the method primarily to output synthetic contact matrices.
 We also provided methods to create next generation matrices.
@@
 
-We will generate a contact matrix for Tasmania area within Australia, using a model fitted from the POLYMOD contact survey.
+We will generate a contact matrix for Tasmania, a state in Australia, using a model fitted from the POLYMOD contact survey.
 We can get the age-stratified population data for Tasmania from the helper function `abs_age_state()`:
@@
 
-Each cell in the resulting contact matrix, indexed *i*, *j*, is the predicted number of people in age group *j* that a single individual in age group *i* will have contact with per day.
-If you sum across all the *j* age groups for each *i* age group, you get the predicted total number of contacts per day for each individual of age group *i*.
-[ #TODO expected, predicted, or average?
-Does it matter?
-note: currently going with predicted]
+Each cell in the resulting contact matrix, indexed $i$, $j$, is the predicted number of people in age group $j$ that a single individual in age group $i$ will have contact with per day.
+The sum over all of the $j$ age groups for a particular age group $i$ is the predicted total number of contacts per day for each individual of age group $i$.
 
@@
 The six key features of the relationship between the age groups, represented by the six covariates, are displayed in the figure below.
-
-[ #TODO notes-to-self: the model structure wasn't generated through any particularly robust process, it was just coming up with structures that looked mildly appropriate for our use case. ]
+These covariates capture typical features of inter-person contact, where individuals primarily interact with people of similar age (the diagonals of the matrix), and with grandparents and/or children (the so-called 'wings' of the matrix).
 
@@
 The model structure (covariates?) provided in conmat was designed to represent the key features that are typically present in a contact matrix for different settings (work, school, home, other).
-Including other sources of information that may better describe these contact patterns, such as ..., may improve model performance.
+Including other sources of information that may better describe these contact patterns, such as inter-generational mixing, or differences in school ages of a local demographic, may improve model performance.
 
@@
 
-NOTE: It is also worth noting that there is an updated analysis pipeline that uses conmat, [`syncomat`](https://github.com/idem-lab/syncomat), to generate synthetic contact matrices for 200 countries.
-
 # References

### 2024-08-16 paper/paper.Rmd
pushing partial prediction helpers

@@
 
+```{r}
+#| label: libraries
+library(purrr)
+library(patchwork)
+library(conmat)
+library(ggplot2)
+```
+
 # Summary
@@
 ```{r}
-#| label: load-conmat
-library(conmat)
+#| label: abs-age
 tasmania <- abs_age_state("TAS")
@@
 ```{r}
-# Show partial dep plot of the six main covariates
+#| label: partial-plots
+#| echo: FALSE
+fit_home <- polymod_setting_models$home
+age_grid <- create_age_grid(ages = 1:99)
+term_names <- extract_term_names(fit_home)
+term_var_names <- clean_term_names(term_names)
+age_predictions <- predict_individual_terms(
+  age_grid = age_grid,
+  fit = fit_home,
+  term_names = term_names,
+  term_var_names = term_var_names
+)
+
+age_predictions_all_settings <- map_dfr(
+  .x = polymod_setting_models,
+  .f = function(x) {
+    predict_individual_terms(
+      age_grid = age_grid,
+      fit = x,
+      term_names = term_names,
+      term_var_names = term_var_names
+    )
+  },
+  .id = "setting"
+)
+
+plot_age_term_settings <- gg_age_terms_settings(age_predictions_all_settings)
+age_predictions_long <- pivot_longer_age_preds(age_predictions)
+# this is a figure we want
+plot_age_predictions_long <- gg_age_partial_pred_long(age_predictions_long) +
+  coord_equal() +
+  labs(x = "Age from",
+       y = "Age to")
+
+age_predictions_long_sum <- add_age_partial_sum(age_predictions_long)
+# this is a figure we want
+plot_age_predictions_sum <- gg_age_partial_sum(age_predictions_long_sum) + coord_equal() +
+  labs(x = "Age from",
+       y = "Age to")
+# this is a figure we want
+```
+
+```{r}
+#| echo: FALSE
+#| fig.height: 8
+plot_all_terms_sum <- plot_age_predictions_long +
+  plot_age_predictions_sum + 
+  plot_layout(design = "
+            A
+            A
+            A
+            A
+            A
+            A
+            A
+            B
+            ") + 
+  plot_annotation(
+    tag_levels = "A"
+  )
+
+plot_all_terms_sum
 ```
@@
 
-When the six covariates are added up together for each setting (in other words, each model) and exponentiated, they show the following patterns:
+When the six covariates are added up together for each setting (in other words, each model), then exponentiated, they show the following patterns:
 

### 2024-08-19 paper/paper.qmd
use quarto

--- 2024-08-14 paper/paper.Rmd
@@
   orcid: 0000-0002-8159-0414
-date: "03 May 2024"
-output:
-  pdf_document: default
-  html_document:
-    keep_md: yes
+date: today
 bibliography: references.bib
@@
   name: Monash University
+execute: 
+  echo: true
+  cache: true
+format: 
+  pdf: 
+    keep-md: true
+    fig-height: 4
+    fig-align: center
+    fig-format: png
+    dpi: 300
+  html: 
+    keep-md: true
+    fig-height: 4
+    fig-align: center
+    fig-format: png
+    dpi: 300
 ---
 
-```{r setup}
+```{r}
 #| label: setup
@@
 #| warning: false
-#| comment: false
-knitr::opts_chunk$set(comment = "#>",
-                      echo = TRUE,
-                      out.width = "95%",
-                      retina = 3,
-                      fig.height = 4,
-                      fig.align = "center",
-                      dpi = 300,
-                      dev = "png")
 options(tinytex.clean = FALSE)
+```
+
+```{r}
+#| label: libraries
+#| echo: false
+#| output: false
+
+library(purrr)
+library(patchwork)
+library(conmat)
+library(ggplot2)
 ```
@@
 
-This article introduces `conmat`, an R package which generates synthetic contact matrices.
 Contact matrices describe the number of contacts between individuals, typically age groups.
 They are used to create models of infectious disease spread.
+`conmat` is an R package which generates synthetic contact matrices for arbitrary input demography, ready for use in infectious diseases modelling.
 
 There are currently few options for a user to access synthetic contact matrices [@socialmixr; @prem2017].
-Existing code to generate synthetic contact matrices from @prem2017 are not designed for replicability, and are restricted to only selected countries with no sub-national demographic estimates available.
+Existing code to generate synthetic contact matrices from @prem2017 are not designed for replicability, are restricted to only selected countries, and provide no sub-national demographic estimates.
 
-The software exposes model fitting and prediction separately to the user.
-Users can fit a model based on a contact survey such as POLYMOD [@mossong2008], then predict from this model to their own data.
-This means users can generate synthetic contact matrices for any region, with any contact survey, provided they have the relevant data.
+The `conmat` package exposes model fitting and prediction separately to the user.
+Users can fit a model based on a contact survey such as POLYMOD [@mossong2008], then predict from this model to their own demographic data.
+This means users can generate synthetic contact matrices for any region, with any contact survey.
 
-We demonstrate a use-case for `conmat` by creating contact matrices for a state (i.e. at the sub-national level) in Australia.
+We demonstrate a use-case for `conmat` by creating contact matrices for sub-national level (in this case, a state) in Australia.
 
-For users who do not wish to run the entire `conmat` pipeline, we have pre-generated synthetic contact matrices for 200 countries, based on a list of country names by the UN, using a model fit to the POLYMOD contact survey.
-These resulting synthetic contact matrices, and the associated code, can be found in the syncomat analysis pipeline ([GitHub](https://github.com/idem-lab/syncomat), [Zenodo](https://zenodo.org/records/11365943)).
+For users who do not wish to run the entire `conmat` pipeline, we have pre-generated synthetic contact matrices for 200 countries, based on a list of countries from the United Nations, using a model fit to the POLYMOD contact survey.
+These resulting synthetic contact matrices, and the associated code, can be found in the syncomat analysis pipeline ([GitHub](https://github.com/idem-lab/syncomat), [Zenodo](https://zenodo.org/records/11365943)) [@syncomat].
 
@@
 
-An prominent contact survey is the "POLYMOD" study by @mossong2008, which covered 8 European countries: Belgium, Germany, Finland, Great Britain, Italy, Luxembourg, The Netherlands, and Poland [@mossong2008].
+An prominent contact survey is the "POLYMOD" study by @mossong2008, which surveyed 8 European countries: Belgium, Germany, Finland, Great Britain, Italy, Luxembourg, The Netherlands, and Poland [@mossong2008].
 
 These social contact surveys can be projected on to a given demographic structure to produce estimated daily contact rates between age groups.
-These are known as contact matrices or synthetic contact matrices.
+These are known as "contact matrices" or "synthetic contact matrices".
 A widely used approach by @prem2021 [@prem2021] produced contact matrices for 177 countries at "urban" and "rural" levels for each country.
@@
 We will generate a contact matrix for Tasmania, a state in Australia, using a model fitted from the POLYMOD contact survey.
-We can get the age-stratified population data for Tasmania from the helper function `abs_age_state()`:
+We can get the age-stratified population data for Tasmania from the Australian Bureau of Statistics (ABS) with the helper function, `abs_age_state()`:
 
 ```{r}
-#| label: load-conmat
-library(conmat)
+#| label: abs-age
 tasmania <- abs_age_state("TAS")
-tasmania
+head(tasmania)
 ```
 
-We can then generate a contact matrix for Tasmania using `extrapolate_polymod()`.
+We can then generate a contact matrix for Tasmania, from the POLYMOD study with `extrapolate_polymod()`.
 
@@
 #| label: autoplot-contacts
-#| fig.width: 8
-#| fig.height: 8
+#| fig-width: 8
+#| fig-height: 8
 autoplot(tasmania_contact)
@@
 1) Fit a model to predict individual contact rate, using an existing contact survey
-2) Predict a contact matrix using age population data
+2) Predict a synthetic contact matrix using age population data
 
@@
 
-Each cell in the resulting contact matrix, indexed $i$, $j$, is the predicted number of people in age group $j$ that a single individual in age group $i$ will have contact with per day.
+[njt: should we mention the link/family?]
+
+Each cell in the resulting contact matrix, indexed ($i$, $j$), is the predicted number of people in age group $j$ that a single individual in age group $i$ will have contact with per day.
 The sum over all of the $j$ age groups for a particular age group $i$ is the predicted total number of contacts per day for each individual of age group $i$.
 
-The six covariates are 
-$|i-j|$, 
-${|i-j|}^{2}$, 
-$i + j$, 
-$i \times j$, 
-$\text{max}(i, j)$ and 
-$\text{min}(i, j)$.
+[njt: do we need to mention that we need to do the exponentiated sum, since these are on the log scale?]
 
-The six key features of the relationship between the age groups, represented by the six covariates, are displayed in the figure below.
-These covariates capture typical features of inter-person contact, where individuals primarily interact with people of similar age (the diagonals of the matrix), and with grandparents and/or children (the so-called 'wings' of the matrix).
+The six covariates are:
+
+- $|i-j|$, 
+- ${|i-j|}^{2}$, 
+- $i + j$, 
+- $i \times j$, 
+- $\text{max}(i, j)$ and 
+- $\text{min}(i, j)$.
+
+[njt: OK with putting these as dot points?]
+
+These covariates capture typical features of inter-person contact, where individuals primarily interact with people of similar age (the diagonals of the matrix), and with grandparents and/or children (the so-called 'wings' of the matrix).The key features of the relationship between the age groups, represented by the six covariates, are displayed in \@ref(fig:partial-plots) for the home setting.
+The $|i-j|$ term gives the strong diagonal, modelling people generally living with similar age people, and the $\max(i,j)$ and $\min(i,j)$ terms give the intergenerational effect of parents and grandparents with children.
 
 ```{r}
-# Show partial dep plot of the six main covariates
+#| label: partial-plots-create
+#| echo: false
+
+fit_home <- polymod_setting_models$home
+age_grid <- create_age_grid(ages = 1:99)
+term_names <- extract_term_names(fit_home)
+term_var_names <- clean_term_names(term_names)
+age_predictions <- predict_individual_terms(
+  age_grid = age_grid,
+  fit = fit_home,
+  term_names = term_names,
+  term_var_names = term_var_names
+)
+
+age_predictions_all_settings <- map_dfr(
+  .x = polymod_setting_models,
+  .f = function(x) {
+    predict_individual_terms(
+      age_grid = age_grid,
+      fit = x,
+      term_names = term_names,
+      term_var_names = term_var_names
+    )
+  },
+  .id = "setting"
+)
+
+plot_age_term_settings <- gg_age_terms_settings(age_predictions_all_settings)
+age_predictions_long <- pivot_longer_age_preds(age_predictions)
+plot_age_predictions_long <- gg_age_partial_pred_long(age_predictions_long) +
+  coord_equal() +
+  labs(x = "Age from",
+       y = "Age to") + 
+  theme(
+    legend.position = "bottom"
+  ) +
+  scale_x_continuous(expand = c(0,0)) +
+  scale_y_continuous(expand = c(0,0)) +
+  expand_limits(x = c(0, 100), y = c(0, 100))
+
+age_predictions_long_sum <- add_age_partial_sum(age_predictions_long)
+plot_age_predictions_sum <- gg_age_partial_sum(age_predictions_long_sum) + coord_equal() +
+  labs(x = "Age from",
+       y = "Age to") +
+  theme(
+    legend.position = "bottom"
+  ) +
+  scale_x_continuous(expand = c(0,0)) +
+  scale_y_continuous(expand = c(0,0)) +
+  expand_limits(x = c(0, 100), y = c(0, 100))
 ```
 
-Note that these partial dependency plots are on the log scale.
+```{r}
+#| label: show-partial-plots
+#| echo: false
+#| fig-height: 8
+#| fig-cap: "Partial predictive plot (A) and overall synthetic contact matrix (B) for the Poisson GAM fitted to the POLYMOD contact survey in the home setting.
+The strong diagonal elements, and parents/grandparents interacting with children result in the classic 'diagonal with wings' shape."
+plot_all_terms_sum <- plot_age_predictions_long +
+  plot_age_predictions_sum + 
+  plot_layout(design = "
+            AAAABBBB
+            AAAABBBB
+            AAAABBBB
+            AAAABBBB
+            ") + 
+  plot_annotation(
+    tag_levels = "A"
+  )
 
-When the six covariates are added up together for each setting (in other words, each model) and exponentiated, they show the following patterns:
-
-```{r}
-# Show combined partial dep plot (i.e. sum of the partial dependencies for all six covariates) in each setting: home, school, work and other
+plot_all_terms_sum
 ```
 
-In other words, the six covariates above provide patterns that are useful in modelling the different settings,
-and correspond with real-life situations of how contact would look like. 
-In the home setting for example, [ #TODO describe how children interact with parents and elderly generation, grandparents ].
-When the covariates for school and work are added, these covariates also provide patterns that correspond with real-life situations.
-https://idem-lab.github.io/conmat/dev/articles/visualising-conmat.html
-In the school setting, children tend to contact other children in the same age groups as them.
-In the work setting, there are no contacts with children under the age of ten and minimal contact with adults beyond retirement age.
+Visualising the partial predictive plots for other settings (school, work and other), shows patterns that correspond with real-life situations are observed.
+A full visualisation pipeline is available at https://idem-lab.github.io/conmat/dev/articles/visualising-conmat.html
 
@@
 These contact matrices can then be used in infectious disease modelling and surveillance.
-
-## Strengths + Weaknesses
 
@@
 
-The model structure (covariates?) provided in conmat was designed to represent the key features that are typically present in a contact matrix for different settings (work, school, home, other).
+The covariates used by conmat were designed to represent the key features that are typically present in a contact matrix for different settings (work, school, home, other).
 Including other sources of information that may better describe these contact patterns, such as inter-generational mixing, or differences in school ages of a local demographic, may improve model performance.
@@
 
-## Meaning of the work
-
 Public health decisions are often based on age specific information, which means the more accurate your age specific models are, the better those decisions are likely to be.
@@
 
-This work was used as a key input into several models for COVID19 in Australia and contributed directly to decisions around vaccination policy.
-
-## Unanswered questions / Future Directions
+This work was used as a key input into several models for COVID-19 transmission and control in Australia and contributed to decisions around vaccination policy [@DohertyModelling].
 
@@
 # References
-
-https://www.doherty.edu.au/our-work/institute-themes/viral-infectious-diseases/covid-19/covid-19-modelling/modelling
-
-Identifying vulnerable groups and predicting how diseases spread are essential for informed public health decision-making.
-Infectious diseases such as influenza and coronavirus spread through human-to-human interactions, or in other words, "social contact".
-Quantifying social contact and its patterns can provide critical insights into how these diseases spread.
-[ Is this circular?
-] / and how best to mitigate the spread of these diseases.

### 2024-08-19 paper/paper.qmd
added a couple of small TODO notes and some small wording changes

@@
 
+[njt: should we reference that contact patterns are known to differ?]
+
 The covariates used by conmat were designed to represent the key features that are typically present in a contact matrix for different settings (work, school, home, other).
@@
 The interface to the model formula in conmat is fixed; users cannot change the covariates of the model.
-This means that if there is an unusual structure in their contact data it might not be accurately captured by conmat.
-It was a design decision that was made to focus on the key feature of conmat: using just age population data to predict a contact matrix.
+This means if there is an unusual structure in their contact data it might not be accurately captured by conmat.
+This fixed formula was a design decision made to focus on the key feature of conmat: using just age population data to predict a contact matrix.
+
+[njt: should we have conmat as `conmat`]
 

### 2024-08-19 paper/paper.qmd

--- 2024-08-19 paper/paper.qmd
@@
 ---
-title: 'conmat: generate synthetic contact matrices for a given age-stratified population'
+title: '`conmat`: generate synthetic contact matrices for a given age-stratified population'
 authors:
@@
 bibliography: references.bib
+cite-method: biblatex
 tags:
@@
   echo: true
-  cache: true
+  cache: false
 format: 
@@
 These are known as "contact matrices" or "synthetic contact matrices".
-A widely used approach by @prem2021 [@prem2021] produced contact matrices for 177 countries at "urban" and "rural" levels for each country.
+A widely used approach by @prem2017 [@prem2021] produced contact matrices for 177 countries at "urban" and "rural" levels for each country.
 
@@
 One model is fitted for each setting. 
-Each model fitted is a Poisson generalised additive model (GAM) which predicts the count of contacts, with an offset for the log of participants. 
+Each model fitted is a Poisson generalised additive model (GAM) with a log link function, which predicts the count of contacts, with an offset for the log of participants. 
 The model has six covariates to explain six key features of the relationship between ages, 
@@
 
-[njt: should we mention the link/family?]
-
-Each cell in the resulting contact matrix, indexed ($i$, $j$), is the predicted number of people in age group $j$ that a single individual in age group $i$ will have contact with per day.
+Each cell in the resulting contact matrix (after back-transformation of the link function), indexed ($i$, $j$), is the predicted number of people in age group $j$ that a single individual in age group $i$ will have contact with per day.
 The sum over all of the $j$ age groups for a particular age group $i$ is the predicted total number of contacts per day for each individual of age group $i$.
-
-[njt: do we need to mention that we need to do the exponentiated sum, since these are on the log scale?]
 
@@
 - $\text{min}(i, j)$.
-
-[njt: OK with putting these as dot points?]
 
@@
   coord_equal() +
-  labs(x = "Age from",
-       y = "Age to") + 
+  labs(
+    x = "Age from",
+    y = "Age to"
+    ) + 
   theme(
-    legend.position = "bottom"
+    legend.position = "bottom",
+    axis.text = element_text(size = 6),
+    panel.spacing = unit(x = 1, units = "lines")
   ) +
@@
 #| echo: false
-#| fig-height: 8
 #| fig-cap: "Partial predictive plot (A) and overall synthetic contact matrix (B) for the Poisson GAM fitted to the POLYMOD contact survey in the home setting.
@@
   plot_layout(design = "
-            AAAABBBB
-            AAAABBBB
-            AAAABBBB
-            AAAABBBB
+            AAAAABBBB
+            AAAAABBBB
+            AAAAABBBB
+            AAAAABBBB
             ") + 
@@
 
-The covariates used by conmat were designed to represent the key features that are typically present in a contact matrix for different settings (work, school, home, other).
+The covariates used by `conmat` were designed to represent the key features that are typically present in a contact matrix for different settings (work, school, home, other).
 Including other sources of information that may better describe these contact patterns, such as inter-generational mixing, or differences in school ages of a local demographic, may improve model performance.
 
-The interface to the model formula in conmat is fixed; users cannot change the covariates of the model.
-This means that if there is an unusual structure in their contact data it might not be accurately captured by conmat.
-It was a design decision that was made to focus on the key feature of conmat: using just age population data to predict a contact matrix.
+The interface to the model formula in `conmat` is fixed; users cannot change the covariates of the model.
+This means if there is an unusual structure in their contact data it might not be accurately captured by `conmat`.
+This fixed formula was a design decision made to focus on the key feature of `conmat`: using just age population data to predict a contact matrix.
 

### 2024-08-19 paper/paper.Rmd

--- 2024-08-14 paper/paper.Rmd
@@
 
+```{r}
+#| label: libraries
+#| echo: FALSE
+
+library(purrr)
+library(patchwork)
+library(conmat)
+library(ggplot2)
+```
+
 # Summary
 
-This article introduces `conmat`, an R package which generates synthetic contact matrices.
 Contact matrices describe the number of contacts between individuals, typically age groups.
 They are used to create models of infectious disease spread.
+`conmat` is an R package which generates synthetic contact matrices for arbitrary input demography, ready for use in infectious diseases modelling.
 
@@
 The software exposes model fitting and prediction separately to the user.
-Users can fit a model based on a contact survey such as POLYMOD [@mossong2008], then predict from this model to their own data.
-This means users can generate synthetic contact matrices for any region, with any contact survey, provided they have the relevant data.
+Users can fit a model based on a contact survey such as POLYMOD [@mossong2008], then predict from this model to their own demographic data.
+This means users can generate synthetic contact matrices for any region, with any contact survey.
 
-We demonstrate a use-case for `conmat` by creating contact matrices for a state (i.e. at the sub-national level) in Australia.
+We demonstrate a use-case for `conmat` by creating contact matrices for sub-national level (in this case, a state) in Australia.
 
-For users who do not wish to run the entire `conmat` pipeline, we have pre-generated synthetic contact matrices for 200 countries, based on a list of country names by the UN, using a model fit to the POLYMOD contact survey.
+For users who do not wish to run the entire `conmat` pipeline, we have pre-generated synthetic contact matrices for 200 countries, based on a list of countries from the United Nations, using a model fit to the POLYMOD contact survey.
 These resulting synthetic contact matrices, and the associated code, can be found in the syncomat analysis pipeline ([GitHub](https://github.com/idem-lab/syncomat), [Zenodo](https://zenodo.org/records/11365943)).
@@
 
-An prominent contact survey is the "POLYMOD" study by @mossong2008, which covered 8 European countries: Belgium, Germany, Finland, Great Britain, Italy, Luxembourg, The Netherlands, and Poland [@mossong2008].
+An prominent contact survey is the "POLYMOD" study by @mossong2008, which surveyed 8 European countries: Belgium, Germany, Finland, Great Britain, Italy, Luxembourg, The Netherlands, and Poland [@mossong2008].
 
@@
 
-Each cell in the resulting contact matrix, indexed $i$, $j$, is the predicted number of people in age group $j$ that a single individual in age group $i$ will have contact with per day.
+Each cell in the resulting contact matrix, indexed ($i$, $j$), is the predicted number of people in age group $j$ that a single individual in age group $i$ will have contact with per day.
 The sum over all of the $j$ age groups for a particular age group $i$ is the predicted total number of contacts per day for each individual of age group $i$.
@@
 
-The six key features of the relationship between the age groups, represented by the six covariates, are displayed in the figure below.
-These covariates capture typical features of inter-person contact, where individuals primarily interact with people of similar age (the diagonals of the matrix), and with grandparents and/or children (the so-called 'wings' of the matrix).
+These covariates capture typical features of inter-person contact, where individuals primarily interact with people of similar age (the diagonals of the matrix), and with grandparents and/or children (the so-called 'wings' of the matrix).The key features of the relationship between the age groups, represented by the six covariates, are displayed in \@ref(fig:partial-plots) for the home setting.
+The $|i-j|$ term gives the strong diagonal, modelling people generally living with similar age people, and the $\max(i,j)$ and $\min(i,j)$ terms give the intergenerational effect of parents and grandparents with children.
 
 ```{r}
-# Show partial dep plot of the six main covariates
+#| label: partial-plots
+#| echo: FALSE
+#| fig.cap: "Partial predictive plot (A) and overall synthetic contact matrix (B) for the Poisson GAM fitted to the POLYMOD contact survey in the home setting.
+The strong diagonal elements, and parents/grandparents interacting with children result in the classic 'diagonal with wings' shape."
+
+fit_home <- polymod_setting_models$home
+age_grid <- create_age_grid(ages = 1:99)
+term_names <- extract_term_names(fit_home)
+term_var_names <- clean_term_names(term_names)
+age_predictions <- predict_individual_terms(
+  age_grid = age_grid,
+  fit = fit_home,
+  term_names = term_names,
+  term_var_names = term_var_names
+)
+
+age_predictions_all_settings <- map_dfr(
+  .x = polymod_setting_models,
+  .f = function(x) {
+    predict_individual_terms(
+      age_grid = age_grid,
+      fit = x,
+      term_names = term_names,
+      term_var_names = term_var_names
+    )
+  },
+  .id = "setting"
+)
+
+plot_age_term_settings <- gg_age_terms_settings(age_predictions_all_settings)
+age_predictions_long <- pivot_longer_age_preds(age_predictions)
+plot_age_predictions_long <- gg_age_partial_pred_long(age_predictions_long) +
+  coord_equal() +
+  labs(x = "Age from",
+       y = "Age to") + 
+  theme(
+    legend.position = "bottom"
+  ) +
+  scale_x_continuous(expand = c(0,0)) +
+  scale_y_continuous(expand = c(0,0)) +
+  expand_limits(x = c(0, 100), y = c(0, 100))
+
+age_predictions_long_sum <- add_age_partial_sum(age_predictions_long)
+plot_age_predictions_sum <- gg_age_partial_sum(age_predictions_long_sum) + coord_equal() +
+  labs(x = "Age from",
+       y = "Age to") +
+  theme(
+    legend.position = "bottom"
+  ) +
+  scale_x_continuous(expand = c(0,0)) +
+  scale_y_continuous(expand = c(0,0)) +
+  expand_limits(x = c(0, 100), y = c(0, 100))
 ```
 
-Note that these partial dependency plots are on the log scale.
+```{r}
+#| echo: FALSE
 
-When the six covariates are added up together for each setting (in other words, each model) and exponentiated, they show the following patterns:
+plot_all_terms_sum <- plot_age_predictions_long +
+  plot_age_predictions_sum + 
+  plot_layout(design = "
+            AAAABBBB
+            AAAABBBB
+            AAAABBBB
+            AAAABBBB
+            ") + 
+  plot_annotation(
+    tag_levels = "A"
+  )
 
-```{r}
-# Show combined partial dep plot (i.e. sum of the partial dependencies for all six covariates) in each setting: home, school, work and other
+plot_all_terms_sum
 ```
 
-In other words, the six covariates above provide patterns that are useful in modelling the different settings,
-and correspond with real-life situations of how contact would look like. 
-In the home setting for example, [ #TODO describe how children interact with parents and elderly generation, grandparents ].
-When the covariates for school and work are added, these covariates also provide patterns that correspond with real-life situations.
-https://idem-lab.github.io/conmat/dev/articles/visualising-conmat.html
-In the school setting, children tend to contact other children in the same age groups as them.
-In the work setting, there are no contacts with children under the age of ten and minimal contact with adults beyond retirement age.
+Visualising the partial predictive plots for other settings (school, work and other), shows patterns that correspond with real-life situations are observed.
+A full visualisation pipeline is available at https://idem-lab.github.io/conmat/dev/articles/visualising-conmat.html
 

### 2024-08-26 paper/paper.qmd
update qmd, remove rmd

@@
 
-Contact matrices describe the number of contacts between individuals, typically age groups.
+Contact matrices describe the number of contacts between individuals.
 They are used to create models of infectious disease spread.
@@
 There are currently few options for a user to access synthetic contact matrices [@socialmixr; @prem2017].
-Existing code to generate synthetic contact matrices from @prem2017 are not designed for replicability, are restricted to only selected countries, and provide no sub-national demographic estimates.
+Existing code to generate synthetic contact matrices from @prem2017 are not designed for replicability, are restricted to select countries, and provide no sub-national demographic estimates.
 
@@
 Infectious diseases like influenza and COVID19 spread via social contact.
-If we can understand patterns of contact - which people are more likely be in contact with each other - then we will be able to create models of how disease spreads.
+If we can understand patterns of contact---which individuals are more likely be in contact with each other---then we will be able to create models of how disease spreads.
 Epidemiologists and public policy makers can use these models to make decisions to keep a population safe and healthy.
@@
 
-An prominent contact survey is the "POLYMOD" study by @mossong2008, which surveyed 8 European countries: Belgium, Germany, Finland, Great Britain, Italy, Luxembourg, The Netherlands, and Poland [@mossong2008].
+A prominent contact survey is the "POLYMOD" study by @mossong2008, which surveyed 8 European countries: Belgium, Germany, Finland, Great Britain, Italy, Luxembourg, The Netherlands, and Poland [@mossong2008].
 
@@
 This presents challenges for decision makers who are often working at a sub-national geographical scale.
-Third, the code provided by Prem et al., was not designed for replicability and easy modification with user-defined inputs.
+Third, the code provided by Prem et al.
+was not designed for replicability and easy modification with user-defined inputs.
 
-The `conmat` package was developed to fill the specific need of creating contact matrices for arbitrary demographic structures.
+The `conmat` package was developed to fill the specific need of creating contact matrices for arbitrary age categories and populations (as shown in the below example).
 We developed the method primarily to output synthetic contact matrices.
@@
 
-We can plot the resulting contact matrix for Tasmania with `autoplot`:
+We can plot the resulting contact matrix for Tasmania with `autoplot`, shown in @fig-autoplot-contacts.
 
 ```{r}
-#| label: autoplot-contacts
+#| label: fig-autoplot-contacts
+#| fig-cap: "Contact patterns between individuals for different age groups across four settings: home, work, school, and other.
+The x axis shows the age group from, and the y axis shows the age group to, coloured by the average number of contacts between individuals in two age groups.
+We see different contact patterns in different settings, for example, diagonal with wings for the home setting."
 #| fig-width: 8
@@
 
-1) Fit a model to predict individual contact rate, using an existing contact survey
-2) Predict a synthetic contact matrix using age population data
+1) fit a model to predict individual contact rate, using an existing contact survey;
+2) predict a synthetic contact matrix using age population data.
 
@@
 Each cell in the resulting contact matrix (after back-transformation of the link function), indexed ($i$, $j$), is the predicted number of people in age group $j$ that a single individual in age group $i$ will have contact with per day.
-The sum over all of the $j$ age groups for a particular age group $i$ is the predicted total number of contacts per day for each individual of age group $i$.
+The sum over all age groups $j$ for a particular age group $i$ is the predicted total number of contacts per day for each individual of age group $i$.
 
@@
 - $|i-j|$, 
-- ${|i-j|}^{2}$, 
+- $|i-j|^{2}$, 
 - $i + j$, 
@@
 
-These covariates capture typical features of inter-person contact, where individuals primarily interact with people of similar age (the diagonals of the matrix), and with grandparents and/or children (the so-called 'wings' of the matrix).The key features of the relationship between the age groups, represented by the six covariates, are displayed in \@ref(fig:partial-plots) for the home setting.
-The $|i-j|$ term gives the strong diagonal, modelling people generally living with similar age people, and the $\max(i,j)$ and $\min(i,j)$ terms give the intergenerational effect of parents and grandparents with children.
+These covariates capture typical features of inter-person contact, where individuals primarily interact with people of similar age (the diagonals of the matrix), and with grandparents and/or children (the so-called 'wings' of the matrix).
+The key features of the relationship between the age groups, represented by the six covariates, are displayed in @fig-show-partial-plots for the home setting.
+The $|i-j|$ term gives the strong diagonal, modelling people generally living with those of similar age, and the $\max(i,j)$ and $\min(i,j)$ terms give the intergenerational effect of parents and grandparents with children.
 
@@
 ```{r}
-#| label: show-partial-plots
+#| label: fig-show-partial-plots
 #| echo: false
@@
 
-Visualising the partial predictive plots for other settings (school, work and other), shows patterns that correspond with real-life situations are observed.
+Visualising the partial predictive plots for other settings (school, work and other) show patterns that correspond with real-life situations.
 A full visualisation pipeline is available at https://idem-lab.github.io/conmat/dev/articles/visualising-conmat.html
@@
 Current approaches provide only a selection of country level contact matrices.
-This software can predict to arbitrary demography, such as sub-national, or simulated populations.
+This software can predict to arbitrary demography, such as sub-national or simulated populations.
 
@@
 This means if there is an unusual structure in their contact data it might not be accurately captured by `conmat`.
-This fixed formula was a design decision made to focus on the key feature of `conmat`: using just age population data to predict a contact matrix.
+This fixed formula was a design decision made to focus on the key feature of `conmat`: using only age population data to predict a contact matrix.
 
@@
 
-* Demonstrate fitting a model to other contact surveys from sources such as the `socialmixr` R package [@socialmixr].
-* Predict to any age brackets - such as monthly ages, for example, 1, 3, 6, month year old infants
-* Fitting to multiple contact surveys simultaneously, e.g., POLYMOD and CoMix
-* Add uncertainty to estimates
-* Add methods for including household size distributions
-* Include known household age distributions as offsets in the 'home' setting model, in place of the whole population distribution.
+* demonstrate fitting a model to other contact surveys from sources such as the `socialmixr` R package [@socialmixr];
+* predict to any age brackets - such as monthly ages, for example, 1, 3, 6, month year old infants;
+* fitting to multiple contact surveys simultaneously, e.g., POLYMOD and CoMix;
+* add uncertainty to estimates;
+* add methods for including household size distributions;
+* include known household age distributions as offsets in the 'home' setting model, in place of the whole population distribution.
 

### 2025-01-20 paper/paper.qmd
suggested paper edits

@@
 They are used to create models of infectious disease spread.
-`conmat` is an R package which generates synthetic contact matrices for arbitrary input demography, ready for use in infectious diseases modelling.
+`conmat` is an R package which generates synthetic contact matrices for arbitrary input demography, ready for use in infectious disease modelling.
 
@@
 
-Infectious diseases like influenza and COVID19 spread via social contact.
+Infectious diseases like influenza and COVID-19 spread via social contact.
 If we can understand patterns of contact---which individuals are more likely be in contact with each other---then we will be able to create models of how disease spreads.
@@
 
-A prominent contact survey is the "POLYMOD" study by @mossong2008, which surveyed 8 European countries: Belgium, Germany, Finland, Great Britain, Italy, Luxembourg, The Netherlands, and Poland [@mossong2008].
+A prominent contact survey is the POLYMOD study by @mossong2008, which surveyed 8 European countries: Belgium, Germany, Finland, Great Britain, Italy, Luxembourg, The Netherlands, and Poland [@mossong2008].
 
 These social contact surveys can be projected on to a given demographic structure to produce estimated daily contact rates between age groups.
-These are known as "contact matrices" or "synthetic contact matrices".
-A widely used approach by @prem2017 [@prem2021] produced contact matrices for 177 countries at "urban" and "rural" levels for each country.
+These are known as 'synthetic' contact matrices.
+A widely used approach by @prem2017 [@prem2021] produced synthetic contact matrices for 177 countries at 'urban' and 'rural' levels for each country.
 
@@
 First, not all countries were included in their analyses.
-Second, the contact matrices only covered broad scale areas.
-This presents challenges for decision makers who are often working at a sub-national geographical scale.
+Second, the contact matrices only covered broad population groups within entire countries.
+This presents challenges for decision makers who are often working at a sub-national geographical scale, with differing demographic structure in different sub-populations.
 Third, the code provided by Prem et al.
@@
 
-The `conmat` package was developed to fill the specific need of creating contact matrices for arbitrary age categories and populations (as shown in the below example).
+The `conmat` package was developed to fill the specific need of creating contact matrices for arbitrary age categories and populations (as shown in the below example) to inform infectious diease models.
 We developed the method primarily to output synthetic contact matrices.
-We also provided methods to create next generation matrices.
+We also provided methods to create next generation matrices for modelling.
 
@@
 
-We can then generate a contact matrix for Tasmania, from the POLYMOD study with `extrapolate_polymod()`.
+We can then generate a synthetic contact matrix for Tasmania, by extrapolating the contact patterns between age groups learned from the POLYMOD study, using `extrapolate_polymod()`.
 
@@
 #| fig-cap: "Contact patterns between individuals for different age groups across four settings: home, work, school, and other.
-The x axis shows the age group from, and the y axis shows the age group to, coloured by the average number of contacts between individuals in two age groups.
-We see different contact patterns in different settings, for example, diagonal with wings for the home setting."
+The x axis shows the age groups for focal individuals ('from'), and the y axis shows the age groups for people those individuals have contact with ('to'), coloured by the average number of contacts the individual has in that age group.
+We see different contact patterns in different settings, for example, diagonal with 'wings' for the home setting."
 #| fig-width: 8
@@
 
-1) fit a model to predict individual contact rate, using an existing contact survey;
+1) fit a model to predict individual contact rates, using an existing contact survey;
 2) predict a synthetic contact matrix using age population data.
@@
 These covariates capture typical features of inter-person contact, where individuals primarily interact with people of similar age (the diagonals of the matrix), and with grandparents and/or children (the so-called 'wings' of the matrix).
-The key features of the relationship between the age groups, represented by the six covariates, are displayed in @fig-show-partial-plots for the home setting.
-The $|i-j|$ term gives the strong diagonal, modelling people generally living with those of similar age, and the $\max(i,j)$ and $\min(i,j)$ terms give the intergenerational effect of parents and grandparents with children.
+The key features of the relationship between the age groups, represented by spline transformations of the six covariates, are displayed in @fig-show-partial-plots for the home setting.
+The spline-transformed $|i-j|$ and $|i-j|^{2}$ terms give the strong diagonal lines modelling people generally living with those of similar age and the intergenerational effect of parents and (faintly) grandparents with children.
+The spline-transformed $\text{max}(i, j)$ and $\text{min}(i, j)$ terms give the higher rates of at-home contact among younger people of similar ages and with their parents.
 
@@
 We provide a trained model of contact rate that is fit to the POLYMOD survey for ease of use.
-The software also has an interface to use other contact surveys, such as @comix.
+The software also has an interface to train models to other contact surveys, such as @comix.
 This is important as POLYMOD represents contact patterns in 8 countries in Europe, and contact patterns are known to differ across nations and cultures.
@@
 
-This work was used as a key input into several models for COVID-19 transmission and control in Australia and contributed to decisions around vaccination policy [@DohertyModelling].
+This code underlying this software was used as a key input into several models for COVID-19 transmission and control in Australia and contributed to decisions around vaccination policy [@DohertyModelling].
 
@@
 
-* demonstrate fitting a model to other contact surveys from sources such as the `socialmixr` R package [@socialmixr];
-* predict to any age brackets - such as monthly ages, for example, 1, 3, 6, month year old infants;
+* integrating model fitting methods with contact survey prepared using the `socialmixr` R package [@socialmixr];
+* enabling prediction to arbitrary age brackets, e.g. monthly age bins for infants;
 * fitting to multiple contact surveys simultaneously, e.g., POLYMOD and CoMix;
-* add uncertainty to estimates;
-* add methods for including household size distributions;
-* include known household age distributions as offsets in the 'home' setting model, in place of the whole population distribution.
+* providing estimates of uncertainty in contact matrices;
+* adding methods to include household size distributions in predictions of contacts in the 'home' setting;
 

### 2025-01-23 paper/paper.qmd
Change author order

@@
   orcid: 0000-0003-1460-8722
-- affiliation: 1,2
-  name: Nick Golding
-  orcid: 0000-0001-8916-5570
+- affiliation: 1,3
+  name: Chitra Saraswati
+  orcid: 0000-0002-8159-0414
 - affiliation: 1,3
@@
   orcid: 0000-0001-6515-827X
-- affiliation: 1,3
-  name: Chitra Saraswati
-  orcid: 0000-0002-8159-0414
+- affiliation: 1,2
+  name: Nick Golding
+  orcid: 0000-0001-8916-5570
 date: today

### 2025-01-28 README.Rmd

--- 2024-07-26 README.Rmd
@@
 [![R-CMD-check](https://github.com/idem-lab/conmat/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/idem-lab/conmat/actions/workflows/R-CMD-check.yaml)
-[![Codecov test coverage](https://codecov.io/gh/idem-lab/conmat/branch/master/graph/badge.svg)](https://codecov.io/gh/idem-lab/conmat?branch=master)
+[![Codecov test coverage](https://codecov.io/gh/idem-lab/conmat/graph/badge.svg)](https://app.codecov.io/gh/idem-lab/conmat)
 <!-- badges: end -->
@@
 
-You can install the stable version from cran with:
+You can install the stable version from CRAN with:
 

### 2025-02-06 paper/paper.qmd
fixes to get PDF to render by JOSS

@@
 format: 
-  pdf: 
-    keep-md: true
-    fig-height: 4
-    fig-align: center
-    fig-format: png
-    dpi: 300
   html: 

### 2025-02-28 paper/paper.qmd
tidy up to use partial_effects and autoplot

@@
 
-fit_home <- polymod_setting_models$home
-age_grid <- create_age_grid(ages = 1:99)
-term_names <- extract_term_names(fit_home)
-term_var_names <- clean_term_names(term_names)
-age_predictions <- predict_individual_terms(
-  age_grid = age_grid,
-  fit = fit_home,
-  term_names = term_names,
-  term_var_names = term_var_names
+partial_home <- partial_effects(
+  model = polymod_setting_models$home,
+  ages = 1:99
 )
 
-age_predictions_all_settings <- map_dfr(
-  .x = polymod_setting_models,
-  .f = function(x) {
-    predict_individual_terms(
-      age_grid = age_grid,
-      fit = x,
-      term_names = term_names,
-      term_var_names = term_var_names
-    )
-  },
-  .id = "setting"
+gg_partial_home <- autoplot(partial_home)
+
+partial_home_sum <- partial_effects_sum(
+  model = polymod_setting_models$home,
+  ages = 1:99
 )
 
-plot_age_term_settings <- gg_age_terms_settings(age_predictions_all_settings)
-age_predictions_long <- pivot_longer_age_preds(age_predictions)
-plot_age_predictions_long <- gg_age_partial_pred_long(age_predictions_long) +
-  coord_equal() +
-  labs(
-    x = "Age from",
-    y = "Age to"
-    ) + 
+gg_partial_home_sum <- autoplot(partial_home_sum)
+
+gg_partial_home_tidy <- gg_partial_home + 
   theme(
@@
 
-age_predictions_long_sum <- add_age_partial_sum(age_predictions_long)
-plot_age_predictions_sum <- gg_age_partial_sum(age_predictions_long_sum) + coord_equal() +
-  labs(x = "Age from",
-       y = "Age to") +
+gg_partial_home_sum_tidy <- gg_partial_home_sum +
   theme(
@@
 The strong diagonal elements, and parents/grandparents interacting with children result in the classic 'diagonal with wings' shape."
-plot_all_terms_sum <- plot_age_predictions_long +
-  plot_age_predictions_sum + 
+plot_all_terms_sum <- gg_partial_home_tidy +
+  gg_partial_home_sum_tidy + 
   plot_layout(design = "

### 2025-03-04 paper/paper.qmd
some minor tweaks to get GH actions to build PDF appropriately for JOSS submission

@@
 date: today
-bibliography: references.bib
+bibliography: paper.bib
 cite-method: biblatex
@@
 - index: 1
-  name: Telethon Kids Institute
+  name: The Kids Research Institute Australia, WA, Australia
 - index: 2
-  name: Curtin University
+  name:  University of Western Australia, WA, Australia
 - index: 3
-  name: 
-- index: 4
-  name: Monash University
+  name: Monash University, VIC, Australia
 execute: 
@@
 
-We can plot the resulting contact matrix for Tasmania with `autoplot`, shown in @fig-autoplot-contacts.
+We can plot the resulting contact matrix for Tasmania with `autoplot`, shown in (Figure \ref{fig-autoplot-contacts}).
 
@@
 These covariates capture typical features of inter-person contact, where individuals primarily interact with people of similar age (the diagonals of the matrix), and with grandparents and/or children (the so-called 'wings' of the matrix).
-The key features of the relationship between the age groups, represented by spline transformations of the six covariates, are displayed in @fig-show-partial-plots for the home setting.
+The key features of the relationship between the age groups, represented by spline transformations of the six covariates, are displayed in Figure \ref{fig-show-partial-plots} for the home setting.
 The spline-transformed $|i-j|$ and $|i-j|^{2}$ terms give the strong diagonal lines modelling people generally living with those of similar age and the intergenerational effect of parents and (faintly) grandparents with children.

### 2025-03-04 paper/paper.qmd
don't use cite-method: biblatex

@@
 bibliography: paper.bib
-cite-method: biblatex
 tags:

### 2025-03-05 paper/paper.qmd
try to mimic the traveltime quarto file structure

@@
 title: '`conmat`: generate synthetic contact matrices for a given age-stratified population'
+format: 
+  html: 
+    keep-md: true
+    fig-height: 4
+    fig-align: center
+    fig-format: png
+    dpi: 300
+tags:
+  - epidemiology
+  - R
+  - infectious disease
 authors:
@@
     orcid: 0000-0001-8916-5570
-date: today
-bibliography: paper.bib
-tags:
-- epidemiology
-- R
-- infectious disease
 affiliations:
@@
   name: Monash University, VIC, Australia
-execute: 
-  echo: true
-  cache: false
-format: 
-  html: 
-    keep-md: true
-    fig-height: 4
-    fig-align: center
-    fig-format: png
-    dpi: 300
+date: today
+bibliography: paper.bib
 ---
@@
 options(tinytex.clean = FALSE)
+knitr::opts_chunk$set(warning = FALSE, message = FALSE, echo = TRUE, cache = FALSE) 
 ```

### 2025-03-05 paper/paper.qmd
make sure to track figures

@@
     orcid: 0000-0003-1460-8722
-  - affiliation: 1,3
+  - affiliation: 1
     name: Chitra Saraswati
@@
     orcid: 
-  - affiliation: 4
+  - affiliation: 1
     name: Michael Lydeamore

### 2025-03-05 paper/paper.qmd
add a couple more references, and fix affiliations to render

@@
 authors:
-  - affiliation: 1
-    name: Nicholas Tierney
+  - name: Nicholas Tierney
     orcid: 0000-0003-1460-8722
-  - affiliation: 1
-    name: Chitra Saraswati
+    corresponding: true
+    affiliation: "1"
+  - name: Chitra Saraswati
     orcid: 0000-0002-8159-0414
-  - affiliation: 1,3
-    name: Aarathy Babu
-    orcid: 
-  - affiliation: 1
-    name: Michael Lydeamore
+    affiliation: "1"
+  - name: Aarathy Babu
+    orcid: 0000-0002-6982-5989
+    affiliation: "1,3"
+  - name: Michael Lydeamore
     orcid: 0000-0001-6515-827X
-  - affiliation: 1,2
-    name: Nick Golding
+    affiliation: "1"
+  - name: Nick Golding
     orcid: 0000-0001-8916-5570
+    affiliation: "1,2"
 affiliations:
@@
 
-This code underlying this software was used as a key input into several models for COVID-19 transmission and control in Australia and contributed to decisions around vaccination policy [@DohertyModelling].
+This code underlying this software was used as a key input into several models for COVID-19 transmission and control in Australia and contributed to decisions around vaccination policy [@DohertyModelling; @conway2023; @ryan2024].
 

### 2025-03-10 paper/paper.qmd
Fix Michael and Aarathy's affiliation

@@
     orcid: 0000-0002-6982-5989
-    affiliation: "1,3"
+    affiliation: "1"
   - name: Michael Lydeamore
     orcid: 0000-0001-6515-827X
-    affiliation: "1"
+    affiliation: "3"
   - name: Nick Golding
@@
   - index: 3
-    name: Monash University, VIC, Australia
+    name: Department of Econometrics and Business Statistics, Monash University, VIC, Australia
 date: today

### 2025-04-08 paper/paper.qmd
Quote affiliation names

--- 2025-03-05 paper/paper.qmd
@@
   - index: 1
-    name: The Kids Research Institute Australia, WA, Australia
+    name: "The Kids Research Institute Australia, WA, Australia"
   - index: 2
-    name:  University of Western Australia, WA, Australia
+    name:  "University of Western Australia, WA, Australia"
   - index: 3
-    name: Monash University, VIC, Australia
+    name: "Department of Econometrics and Business Statistics, Monash University, VIC, Australia"
 date: today

### 2025-08-06 paper/paper.qmd
add acknowledgements

@@
 
+# Acknowledgements
+
+The authors would like to thank Gerry Ryan for his contributions to conmat, as well as the authors of "Projecting social contact matrices in 152 countries using contact surveys and demographic data", Kiesha Prem, Alex Cook, and Mark Jit, for making their original data public.
+We would also like to thank reviewers Hugo Gruson and Anthony Baptista for their contributions.
+
 # References

### 2025-11-13 paper/paper.qmd
Shorten paper

@@
 
-The six covariates are:
-
-- $|i-j|$, 
-- $|i-j|^{2}$, 
-- $i + j$, 
-- $i \times j$, 
-- $\text{max}(i, j)$ and 
-- $\text{min}(i, j)$.
-
-These covariates capture typical features of inter-person contact, where individuals primarily interact with people of similar age (the diagonals of the matrix), and with grandparents and/or children (the so-called 'wings' of the matrix).
+The covariate capture typical features of inter-person contact, where individuals primarily interact with people of similar age (the diagonals of the matrix), and with grandparents and/or children (the so-called 'wings' of the matrix).
 The key features of the relationship between the age groups, represented by spline transformations of the six covariates, are displayed in Figure \ref{fig-show-partial-plots} for the home setting.
-The spline-transformed $|i-j|$ and $|i-j|^{2}$ terms give the strong diagonal lines modelling people generally living with those of similar age and the intergenerational effect of parents and (faintly) grandparents with children.
-The spline-transformed $\text{max}(i, j)$ and $\text{min}(i, j)$ terms give the higher rates of at-home contact among younger people of similar ages and with their parents.
-
 ```{r}
@@
 
-Some future directions for this software include:
-
-* integrating model fitting methods with contact survey prepared using the `socialmixr` R package [@socialmixr];
-* enabling prediction to arbitrary age brackets, e.g. monthly age bins for infants;
-* fitting to multiple contact surveys simultaneously, e.g., POLYMOD and CoMix;
-* providing estimates of uncertainty in contact matrices;
-* adding methods to include household size distributions in predictions of contacts in the 'home' setting;
-
 Software is never finished, and the software in its current format has proven useful for infectious disease modelling.

### 2025-11-28 R/partial-prediction-helpers.R
misc changes to improve documentation

@@ -269,14 +269,14 @@ clean_term_names <- function(term_names) {
 }
 
 #'
-#' @param age_grid grid of ages from [create_age_grid()]
+#' @param age_grid grid of ages from `create_age_grid()`
 #' @param model model fitted object from conmat, e.g.,
 #'   `polymod_setting_models$home`.
-#' @param term_names terms from model extracted with [extract_term_names()].
+#' @param term_names terms from model extracted with `extract_term_names()`.
 #' @param term_var_names Cleaned up term names from model used with
-#'   [clean_term_names()].
+#'   `clean_term_names()`.
 #' @return Data frame containing predicted values added to output of
-#'   [create_age_grid()].
+#'   `create_age_grid()`.
 #' @noRd
 predict_individual_terms <- function(
   age_grid,

### 2025-11-28 R/plot_setting_matrices.R

@@ -1,6 +1,6 @@
 #' Visualise predicted contact matrix for each setting
 #'
-#' This is an extension of [plot_matrix()], which visualises the contact
+#' This is an extension of [autoplot.conmat_age_matrix()], which visualises the contact
 #'   matrix for each setting. It uses `patchwork` to combine all the matrices
 #'   together
 #'

### 2025-12-18 paper/paper.qmd

@@
 format: 
-  html: 
+  wordcount-html: 
+    wordcounter-banner: true
     keep-md: true
@@
     dpi: 300
+params:
+  wordcount: |
+    <strong>{{< words-sum body-note-ref >}} total words</strong>: {{< words-body >}} in the body • {{< words-ref >}} in the references • {{< words-note >}} in the notes
 tags:
@@
 
-There are currently few options for a user to access synthetic contact matrices [@socialmixr; @prem2017].
+<!-- There are currently few options for a user to access synthetic contact matrices [@socialmixr; @prem2017].
 Existing code to generate synthetic contact matrices from @prem2017 are not designed for replicability, are restricted to select countries, and provide no sub-national demographic estimates.
+-->
 
 The `conmat` package exposes model fitting and prediction separately to the user.
-Users can fit a model based on a contact survey such as POLYMOD [@mossong2008], then predict from this model to their own demographic data.
+Users can fit a model based on a contact survey, then predict from this model to their own demographic data.
 This means users can generate synthetic contact matrices for any region, with any contact survey.
@@
 Infectious diseases like influenza and COVID-19 spread via social contact.
-If we can understand patterns of contact---which individuals are more likely be in contact with each other---then we will be able to create models of how disease spreads.
+If we can understand patterns of contact---which individuals are more likely be in contact with each other---then we will be able to create accurate models of how disease spreads.
 Epidemiologists and public policy makers can use these models to make decisions to keep a population safe and healthy.
 
-Empirical estimates of social contact are provided by social contact surveys. These provide samples of the frequency and type of social contact across different settings (home, work, school, other).
-
-A prominent contact survey is the POLYMOD study by @mossong2008, which surveyed 8 European countries: Belgium, Germany, Finland, Great Britain, Italy, Luxembourg, The Netherlands, and Poland [@mossong2008].
-
-These social contact surveys can be projected on to a given demographic structure to produce estimated daily contact rates between age groups.
-These are known as 'synthetic' contact matrices.
-A widely used approach by @prem2017 [@prem2021] produced synthetic contact matrices for 177 countries at 'urban' and 'rural' levels for each country.
+Empirical estimates of social contact are provided by social contact surveys, which provide samples of the frequency and type of social contact across different settings (home, work, school, other).
+These surveys can be projected onto a given demographic structure, resulting in what is known as 'synthetic' contact matrices.
+A widely used approach by @prem2017 [@prem2021] produced such matrices for 177 countries at 'urban' and 'rural' levels for each country using data from 8 European Countries by @mossong2008.
 
@@
 Second, the contact matrices only covered broad population groups within entire countries.
-This presents challenges for decision makers who are often working at a sub-national geographical scale, with differing demographic structure in different sub-populations.
 Third, the code provided by Prem et al.
@@
 
-The `conmat` package was developed to fill the specific need of creating contact matrices for arbitrary age categories and populations (as shown in the below example) to inform infectious diease models.
-We developed the method primarily to output synthetic contact matrices.
-We also provided methods to create next generation matrices for modelling.
+The `conmat` package was developed to fill the specific need of creating contact matrices for arbitrary age categories and populations to inform infectious diease models.
+We developed the method to output synthetic contact matrices.
+We also provided methods to create next generation matrices.
 
@@
 Each model fitted is a Poisson generalised additive model (GAM) with a log link function, which predicts the count of contacts, with an offset for the log of participants. 
-The model has six covariates to explain six key features of the relationship between ages, 
+The model has six covariates to explain key features of the relationship between ages, 
 and two optional covariates for attendance at school or work.
-The two optional covariates are included depending on which setting the model is fitted for.
 
@@
 
-The covariate capture typical features of inter-person contact, where individuals primarily interact with people of similar age (the diagonals of the matrix), and with grandparents and/or children (the so-called 'wings' of the matrix).
-The key features of the relationship between the age groups, represented by spline transformations of the six covariates, are displayed in Figure \ref{fig-show-partial-plots} for the home setting.
+The model captures typical features of inter-person contact, where individuals primarily interact with people of similar age (the diagonals of the matrix), and with grandparents and/or children (the so-called 'wings' of the matrix).
+The key features of the relationship between the age groups are displayed in Figure \ref{fig-show-partial-plots} for the home setting.
 ```{r}
@@
 These contact matrices can then be used in infectious disease modelling and surveillance.
+Public health decisions are based on models using these matrices as input data.
+This is the first piece of software that can provide context-appropriate contact matrices for a population, which means more accurate models of disease.
 
@@
 
-The interface to the model formula in `conmat` is fixed; users cannot change the covariates of the model.
+<!-- The interface to the model formula in `conmat` is fixed; users cannot change the covariates of the model.
 This means if there is an unusual structure in their contact data it might not be accurately captured by `conmat`.
 This fixed formula was a design decision made to focus on the key feature of `conmat`: using only age population data to predict a contact matrix.
-
-Public health decisions are often based on age specific information, which means the more accurate your age specific models are, the better those decisions are likely to be.
-This is the first piece of software that will provide appropriate contact matrices for a population, which means more accurate models of disease.
+-->
 

### 2025-12-20 paper/paper.qmd
Fix a few formatting issues

@@
 
-We can plot the resulting contact matrix for Tasmania with `autoplot`, shown in (Figure \ref{fig-autoplot-contacts}).
+We can plot the resulting contact matrix for Tasmania with `autoplot`, shown in Figure \ref{fig-autoplot-contacts}.
 
@@
 One model is fitted for each setting. 
-Each model fitted is a Poisson generalised additive model (GAM) with a log link function, which predicts the count of contacts, with an offset for the log of participants. 
+Each model fitted is a Poisson generalised additive model (GAM) with a log link function, which predicts the count of contacts, with an offset for the log of the number of participants. 
 The model has six covariates to explain key features of the relationship between ages, 
@@
 
-This code underlying this software was used as a key input into several models for COVID-19 transmission and control in Australia and contributed to decisions around vaccination policy [@DohertyModelling; @conway2023; @ryan2024].
+The code underlying this software was used as a key input into several models for COVID-19 transmission and control in Australia and contributed to decisions around vaccination policy [@DohertyModelling; @conway2023; @ryan2024].
 
